---
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
    keep_tex: false
  bookdown::word_document2: default
  bookdown::html_document2: default
documentclass: book
editor_options: 
  chunk_output_type: inline
  
bibliography: 
  - bibliography/references.bib
bibliography-heading-in-pdf: Works Cited
params:
  corrections: true 
---

```{r setup 01-03, echo = F, include = F}
```

# Psychology of source selection {#chapter-advisor-choice}
\adjustmtc 

Advice is relied upon to a different extent depending upon a variety of markers for its trustworthiness, including its plausibility and the reputation of its source.
The question at the core of this chapter is whether people preferentially seek out advice from advisors they believe to be more trustworthy.
At first glance, it may seem a foregone conclusion that people will seek out advice from more trustworthy advisors: who after all wants to be advised by fools or liars?
Nevertheless, empirical evidence for this kind of source selection behaviour has been somewhat mixed.
The evidence that people do tend to seek out information from sources likely to agree with them is moderate ['selective exposure', @hartFeelingValidatedBeing2009]. 
The evidence that people avoid information likely to disagree is poor ['selective avoidance', @jangChallengesSelectiveExposure2014a; @weeksPartisanEnclavesShared2016], with evidence becoming less persuasive as tasks become more ecologically valid [@searsSelectiveExposureInformation1967; @nelsonMythPartisanSelective2017]. 

There are also intuitive arguments for a range of potential findings.
It would make sense that people seek out information they are more likely to use, because all information acquisition comes with some kind of cost, even if only attentional and opportunity costs, and rational actors should maximise their benefit-cost trade-off.
It may make sense for people to seek out information they are likely to agree with, regardless of usefulness, because they may be exercising critical vigilance over their own side in a debate, ensuring that bad arguments are not used to support their ideological position.
It would also make sense, however, for people to seek out information from sources they disagree with: perhaps those we disagree with have access to evidence or reasons we had not considered; or perhaps learning about others' views will allow us to better counter them and convert their adherents [@freedmanConfidenceUtilitySelective1965].
People may even prefer a balanced or random diet of information because they feel unable to judge relative quality, or because all the reasons above are pulling them in different directions. 

The vast majority of the source selection literature uses surveys or browsing tasks with stimuli being realistic politically-charged media items.
Measurements are either active interest ratings or passive activity monitoring [usually on links clicked or reading time, but eye tracking is a recent innovation: @marquartSelectiveExposureContext2016; @schmuckAvoidingOtherSide2020].
The experiments here are more traditional cognitive psychology experiments: the complex contextual factors suspected of driving selectivity are removed [@festingerTheoryCognitiveDissonance1957; @knobloch-westerwickSelectiveExposureSelf2015] and only the informational motive remains.
While it is not impossible that a preference for agreement which makes sense from a self-image preservation perspective bleeds into a context where accuracy is key, the experiments here at least provide a context where a correct answer exists.^[It is arguable that people may seek out politically-concordant information because they believe it to be more accurate rather than because they do not want their self-image to be challenged.]

### Similar work

The source selection literature is largely from the domains of social and personality, in which the constructs that produce the phenomena are attitudes and self-concepts. 
This work is grounded in the cognitive psychology domain, and consequently uses a model of advisor evaluation (Advisor Evaluation without Feedback§\@ref(advisor-evaluation-without-feedback)) that posits measurable variables and mathematically-describable processes.
This model is based on a similar model from @pescetelliRoleDecisionConfidence2021.
It takes as a starting point the observation that, given objective feedback, people can use that feedback to learn about the trustworthiness of advisors [@yanivAdviceTakingDecision2000; @pescetelliRoleDecisionConfidence2021; @behrensAssociativeLearningSocial2008].
The extent to which advice is taken (§\@ref(m-analysis-dv-woa)) is commonly used as a measure of a participant's trust in an advisor, on the argument that the participant seeks to maximise task performance and task performance is maximised by taking more advice from more trustworthy advisors.
As expected, people make greater use of advice they believe will be more accurate compared to less accurate [@ginoAnxietyAdviceAbility2012; @rakoczyYoungChildrenHeed2015; @sniezekImprovingJudgementPrepaid2004; @sollStrategiesRevisingJudgment2009; @tostPowerCompetitivenessAdvice2012; @schultzeInabilityIgnoreUseless2017; @wangWhyDoesAdvice2018; @onkalEvaluatingExpertAdvice2017].

When objective feedback is unavailable, it is still possible for people to demonstrate a greater dependence upon advice from more as opposed to less accurate advisors.
This is a consequence of agreement: where the base probability of being correct is greater than chance, the independent estimates of people who are more accurate will agree more often (leading to 100% agreement on the correct answer for two independent decision-makers of perfect accuracy).
In the absence of feedback, therefore, agreement can be used as a proxy for accuracy, as formalised in the model.

@pescetelliRoleDecisionConfidence2021 demonstrated that advice is more influential from (equally accurate) advisors who tend to agree with a participant more frequently when objective feedback is not provided.
This is despite the fact that advice is generally more influential when it disagrees with the participant's initial estimate.
^[This is partly due to the nature of the judge-advisor system: there is always room for disagreement to be more extreme than agreement, because agreement is lower-bounded by the participant's initial estimate.] 
Their data suggest that people may be using agreement as a proxy for accuracy, although they may also simply prefer agreement over disagreement when there is no accuracy cost to be paid.
In this chapter, we partially replicate the findings of @pescetelliRoleDecisionConfidence2021, and explore the consequences of pitting accurate advisors against agreeing advisors.

### Overview of Experiments

We conducted a series of experiments to explore whether the advice-taking behaviour observed previously [@pescetelliRoleDecisionConfidence2021] would translate into preferential source selection behaviour.
In these experiments participants were familiarised with different pairs of advisors, and then given the opportunity to select which advisor they would like to get advice from (General Method§\@ref(gm)).

Each experiment was repeated using two different tasks: a perceptual decision-making "Dots task", extended from @pescetelliRoleDecisionConfidence2021; and a historical date estimation "Dates task" newly built for this project.
To reduce expenditure, all participants in the Dots task experiments received no feedback on their answers while learning about advisors, because contrasting the presence and absence of feedback was done by @pescetelliRoleDecisionConfidence2021.
In the Dates task, due to its novelty, participants were split into conditions based on whether or not they received feedback while learning about the advisors.

The first of the advisor pairs was a high accuracy advisor and a low accuracy advisor (Experiment 1A§\@ref(ac-acc-dots) and Experiment 1B§\@ref(ac-acc-dates)). 
We predicted that the high accuracy advisor would be selected more often, even where feedback was not available. 
This experiment would demonstrate the minimum phenomenon of interest -- sensitivity to advisor accuracy in the absence of feedback translating into preferential advisor selection.

The second advisor pair was a high agreement and a low agreement advisor (Experiment 2A§\@ref(ac-agr-dots) and Experiment 2B§\@ref(ac-agr-dates)). 
We predicted that the high agreement advisor would be selected more frequently, because we expect agreement to be the method by which the accurate advisors were detected in the previous task.
This experiment would constitute a test of the purported mechanism.

The third advisor pair was a high agreement advisor and a high accuracy advisor (Experiment 3A§\@ref(ac-ava-dots) and Experiment 3B§\@ref(ac-ava-dates)).
We predicted that the high agreement advisor would be selected more frequently than the high accuracy advisor, but only where feedback was withheld.
Where feedback was provided, we expected the high accuracy advisor to be picked more often.
This experiment would test whether the absence of feedback invites using agreement as a substitute for accuracy.

The final advisor pair were confident contingent advisors like those used in @pescetelliRoleDecisionConfidence2021 (Experiment 4A§\@ref(ac-cca-dots) and the Lab Study§\@ref(ac-cca-lab)). 
These advisors agree at the same rate and are similarly accurate, but one agrees more when the participant expresses high initial confidence and less when the participant expresses low initial confidence, and the other vice-versa. 
We predicted that the former 'bias-sharing' advisor would be selected more often because participants would use their own sense of confidence to weight the value of agreement. 
This experiment would explore whether metacognitive processes are able to finesse the basic agreement-for-accuracy substitution.


<!-- Presentation of the experiments (may want different subsections for each experiment and an extra one for the general discussion).
-->

<!-- The results for each experiment are included in their own files because they're just too damn long for hackMD.io to handle -->
```{r, child=c('_acc.Rmd', '_agr.Rmd',  '_ava.Rmd', '_cca.Rmd'), results='asis'}
```

## General discussion

Previous work in our lab indicated that people are able to evaluate advice in the absence of feedback using agreement as a proxy [@pescetelliRoleDecisionConfidence2021].
We performed a series of experiments investigating whether the patterns observed for advice taking are also evident in advisor selection.
Our experiments exercised tight control over the advisors' answers in the domains of agreement and accuracy, and allowed us to explore their relative contributions.

Modelling and theoretical work indicates that biased source selection can dramatically reshape communication networks and create echo chamber effects where accurate but unpalatable information is ignored [@sunsteinRepublicCom2002; @madsenLargeNetworksRational2018].
Empirical research on source selection behaviour has found relatively little indication that people behave this way in the real world [@marquartSelectiveExposureContext2016; @searsSelectiveExposureInformation1967; @nelsonMythPartisanSelective2017], particularly in terms of avoiding exposure to unpalatable information [@weeksPartisanEnclavesShared2016; @jangChallengesSelectiveExposure2014].
If the effects seen by @pescetelliRoleDecisionConfidence2021 in the domain of advisor choice also occur in the domain of advisor selection, they may demonstrate in principle a psychological mechanism which could drive biased source selection that are rational and appropriate given the information available.

#### Advisor choice results

The preferences for advisors were broadly consistent with the pattern expected from previous work on advisor influence [@pescetelliRoleDecisionConfidence2021].
Experiments 1B and 3B showed that, where objective feedback could be used to calculate advisor performance, participants showed a systematic preference for picking the advisor who would provide the most accurate advice.
Experiments 1A showed that this preference endured even when feedback was removed, although the result was not replicated in Experiment 1B.

Experiments 2A and 2B showed that participants who did not receive feedback systematically preferred High agreement advisors over Low agreement advisors.
Experiments 3A and 3B indicated that this preference for agreement in the absence of feedback did not extend to a preference for agreement over accuracy.
These results are consistent with an account of advisor trust updating which uses agreement as a proxy for advisor accuracy when more reliable information is not available, although some additional mechanism is required to explain how accuracy can with agreement in the absence of feedback.
@pescetelliRoleDecisionConfidence2021 offer confidence as an additional mechanism, but attempts to replicate their advisor influence experiment in the domain of advisor choice (Experiments 4A and the Lab experiment) did not provide empirical support for this.

\mccorrect{NICK: Highlight key themes as they relate to your results specifically. The themes seem to be: 1. preference for accurate advice when this can be inferred from feedback, but not otherwise. 2. Preference for agreeing advice when feedback is absent, but not when it's present. Relate back to previous literature -> mixed evidence on how people seek info. May depend on domain? (Cf. our conversation all those years ago with Jonathan Bright about different knowledge/info domains.) + the more detailed points you make below (e.g., about similarities and differences between the tasks)}

#### Accuracy of advice

Our experiments showed that people will prefer to seek advice from an advisor who is more accurate, provided that they can identify that advisor.
This coheres well with results from Experiment 0§\@ref(ai-ava-r-h) and other literature in the advice-taking domain where greater task accuracy is referred to as 'expertise' [@pescetelliRoleDecisionConfidence2021; @yanivAdviceTakingDecision2000; @ginoAnxietyAdviceAbility2012; @rakoczyYoungChildrenHeed2015; @sniezekImprovingJudgementPrepaid2004; @sollStrategiesRevisingJudgment2009; @tostPowerCompetitivenessAdvice2012; @schultzeInabilityIgnoreUseless2017; @wangWhyDoesAdvice2018; @onkalEvaluatingExpertAdvice2017]. 
A review of this advice-taking literature can be found in another chapter§\@ref(context-expertise).

Like @pescetelliRoleDecisionConfidence2021, we were interested in whether people are sensitive to accuracy for decisions they make where feedback is not provided.
The majority of decisions on which we seek advice in everyday life do not come with feedback, or come with only infrequent and often delayed feedback.
Although the perceptual decision-making task and the date estimation task used here are highly stylized, they can mimic this feedback regime.
When feedback was denied to participants, leaving them unable to use the feedback to determine the accuracy of the advisors, their preferences only favoured the more accurate advisor in the Dots task (Experiment 1A§\@ref(ac-acc-dots-r-h)), with no systematic preference in the Dates task (Experiment 1B§\@ref(ac-acc-dates-r-h)).
This difference might be explained by the relative difficulty of the tasks.

#### Confidence-weighted agreement as a proxy for accuracy

Where people cannot use objective feedback to determine the quality of advice, they use whether or not the advice agrees with them as a proxy for accuracy.
This is shown by Experiments 2A§\@ref(ac-agr-dots-r-h) and 2B§\@ref(ac-agr-dates-r-h), and is consistent with Experiment 1A§\@ref(ac-acc-dots-r-h) (although not with Experiment 1B§\@ref(ac-acc-dates-r-h) given Experiment 3B§\@ref(ac-ava-dates-r-h)).
It also reflects, in the advisor choice domain, the findings of @pescetelliRoleDecisionConfidence2021 in the advice-taking domain.

@pescetelliRoleDecisionConfidence2021 theorised, on the basis of their experiments, that people assess advice on the basis of confidence-weighted agreement.
This means that, where a judge is confident in their own opinion, offering agreement or disagreement results in a large increase or decrease in trust in the advisor, respectively.
Where a judge is very unsure of the accuracy of their own opinion, however, neither agreement nor disagreement affect trust in the advisor very much -- it is as if the judge has no frame of reference by which to assess the advice they have been given.

Assuming that trust in an advisor translates directly into a preference for hearing advice from that advisor, this theory accounts for some, but not all of our experimental results.
It provides a straightforward account of the results of Experiment 2A§\@ref(ac-agr-dots-r-h) and 2B§\@ref(ac-agr-dates-r-h), where participants who did not receive feedback preferred to hear advice from the advisor more likely to agree with them (while overall advisor accuracy was held constant).
It can also explain of the results of Experiment 1A§\@ref(ac-acc-dots-r-h), because the probability that two independent binary judgements agree is related to the probabilities that they are greater than chance [@sollStrategiesRevisingJudgment2009].
Given participants were above chance in their perceptual decisions, the more accurate advisor would agree more, as indicated in Table \@ref(tab:ac-acc-dots-m-profiles).
Furthermore, if agreement is weighted by confidence, this discrepancy would be greater where the weighting is higher to the extent that participants were well calibrated in their confidence: where they were most confident they were most likely to be correct, and so they were proportionally more likely to be agreed with by the more accurate advisor.

Experiment 1B§\@ref(ac-agr-dates-r-h) is harder to explain under the @pescetelliRoleDecisionConfidence2021 theory. 
Participants should be sensitive to differential agreement rates as in Experiment 1A§\@ref(ac-agr-dots-r-h), and this should be enhanced to the extent that participants' confidence is well calibrated.
The results were doubtful that participants with greater accuracy or confidence calibration expressed a greater preference for the more accurate advisor.
It could have been the case that individual high-impact trials where a participant was extremely confident of the correct answer happened to systematically coincide with the less accurate advisor agreeing with the participant, but this seems very unlikely indeed.
All in all, the results from Experiment 1B do not cohere well with the theory.

Experiments 3A§\@ref(ac-ava-dots-r-h) and 3B§\@ref(ac-ava-dates-r-h) are also consistent with the theory.
Participants denied feedback did not prefer to see advice from the agreeing advisor over the accurate one.
This result would make sense if participants were able to detect the accuracy advantage of the accurate advisor: they might well have noticed that that advisor tended to agree with them where they were confident of the correct answer, and to disagree otherwise.
The data did not support that conclusion.
In the continuous Dates task used for Experiment 3B, the difference between agreement and accuracy is much clearer to participants because the advisors place markers on a timeline that also shows the participant's initial estimate. 
Participants in Experiment 3B may have been able to detect the redundancy of the agreeing advisor's advice and preferred the accurate advisor for that reason.
We included a debrief questionnaire asking what participants though was the difference between the advisors, and several participants indicated in their responses that they had identified that the agreeing advisor tended to reflect their own answer.

The most clear failure of the theory in accounting for the present results is in the experiments using confidence-contingent advice, the Lab experiment and Experiment 4A§\@ref(ac-cca-dots-r-h).
In these experiments, the advisors were specifically constructed such that they would be balanced for overall agreement and accuracy, but differentiated at the extremes of participants' subjective confidence.
One specific test indicated that there may be an effect -- a frequentist test on the moderate-confidence Lab experiment trials where advisors' agreement rates were balanced.
This test, and this experiment, are the closest to those reported by @pescetelliRoleDecisionConfidence2021. 
The effect, if there is one, does not seem to generalise to advisor choice behaviour in shorter versions of the task performed by participants outside of a laboratory setting.

Overall, the results of this suite of experiments suggest that trust in advisors, as evaluated by advisor choice preference, is determined by a variety of factors, even in highly constrained perceptual and general knowledge estimation tasks. 
One of these factors may be confidence-contingent agreement, or agreement more generally.
We have offered some speculation as to properties of the task and context that might alter the extent to which confidence-contingent agreement determines trust in advisors.
Whether there is any dominant mechanism in play that accounts for a sizeable amount of the variation in trust remains unknown, but it appears unlikely that confidence-contingent agreement is that mechanism.

\mccorrect{NICK: Highlight how results relate to the modelling to come: preference for agreeing advice when feedback is absent, but also wide variation in this preference. When preferences are not strong at the population level, we see almost all selection behaviours from always choosing A to always choosing B.}

#### Variability between participants

The experiments produced a range of results, from clear evidence of systematic preferences to clear evidence of the lack of any such systematicity in preferences.
Interestingly, participants displayed a range of preference patterns. 
Most participants in most conditions in most studies demonstrated fairly balanced picking behaviour; perhaps motivated by a sense of fairness or novelty, or perhaps as a result of random selection or attention to other factors such as the position of the advisor on the screen. 
Where effects appear in the data, they show up as a fat tail on a skewed distribution: a sizeable minority select a given advisor on most trials, and almost no one selects the other advisor on most of the trials.

The advisor preference distributions differ somewhat between tasks.
Although advisor choice distributions in both tasks are roughly normally distributed, those in the Dots task results are sharper.
This sharpness may be a result of many participants selecting advisors at approximately equal rates.
If participants become bored or fatigued by the experiment they may disengage and select advisors in a random manner.

Where manipulations are effective in the Dots task (e.g. Experiment 3B§\@ref(ac-ava-dots)) they change the direction of preferences: a good many participants continue to pick advisors at approximately equal rates, but preferences in those who do express a preference systematically favour one particular advisor.
Systematic differences in the Dates task are signified by distributions in which the modal preference moves to an extreme preference for the relevant advisor while the tails of the distribution continue to cover the whole range.
These differences are likely a consequence of the difference in the number of Choice trials in each Task.
The Dates task only has around 10 Choice trials, and it is relatively common for participants to select a single preferred advisor repeatedly. 
The Dots task, however, has 30-60 Choice trials, meaning participants may become tired of seeing advice from the same advisor, increasing the novelty value of advice from the non-preferred advisor and thus reducing the apparent strength of preference.
In support of this idea, the distribution of preferences in Experiment 3A§\@ref(ac-ava-dots-r-h)), which had 30 Choice trials, was much more similar to those from the Dates task than the other Dots task experiments, which had 60 Choice trials.
The similarity may have reflected the absence of any effect rather than the number of Choice trials, but it also more closely resembles the distributions of the Dates task where effects are see (1B§\@ref(ac-acc-dates-r-h), 2B§\@ref(ac-agr-dates-r-h), 3B§\@ref(ac-ava-dates-r-h)) than the other Dots task distribution where they are not (4A§\@ref(ac-cca-dots-r-h)).

The kind of heterogeneity revealed in the experiments' results is seldom included in population models of influence dynamics. 
In the following chapter§\@ref(chapter-network-effects), we explore the effects of including this kind of heterogeneity in agent-based models of advice giving.

#### Social and Personality perspectives

Source selection, most robustly selective exposure, is argued in the Social and Personality Psychology domains to be a product of a drive for cognitive consonance [@festingerTheoryCognitiveDissonance1957] or protecting a positive self-concept [@knobloch-westerwickSelectiveExposureSelf2015] rather than an heuristic which is expected to improve the accuracy of decision-making under common real-world conditions.
While these experiments do not directly contradict that literature, they do indicate that source selection can occur in the absence of any clear implications of the choice for a person's view of themselves.
It may be argued that the effects in the absence of meaningful moral or political contexts reflects a bleed over from processes that perform useful work in vigilantly guarding a person's self-image, and that are always active when choices over information sources are made.
Conversely, however, it could be argued that much of the selective exposure evidence represents a drive for accurate information: if I strongly believe in a liberal world-view I may judge the reporting of a liberal media outlet to be more objectively accurate, and be more willing to view its content on that basis.

#### Limitations

As noted above, there were several issues with the experiments that were only noticed after data had been collected.
The most serious of these was that the Dates task did not counterbalance the advisors' positions, and post hoc analysis of the Dots task data suggested that advisor position may have an unexpectedly important role in advisor choice behaviour.
Another concern is that the difficulty of the Dates task was high, and also highly variable between participants.
In some ways this is a strength, because it could theoretically allow us to detect variations in advisor choice behaviour as a function of participants' ability, but in practice we did not find these.
We were left only with the drawbacks, therefore, of higher noise in the data and the possibility of strong effects of choice being driven by difficult-to-identify high-impact individual trials.

A related concern is the frequently large and significant effects of advisor position in the Dots task. 
Participants frequently picked the advisor at the top of the screen, regardless of that advisor's identity. 
This suggests disengagement with the task.
Interestingly, the advisor at the top of the screen was further away from the answer bar (where participants input their initial estimates and final decisions) than the advisor at the bottom. 
We would expect lazy participants using a mouse to predominantly select the closer advisor.
For participants using mobile phones, it would be equally easy to select either advisor.

Ecological validity is a concern more generally, too.
While these studies were appropriate for capturing the behaviour of interest, they are also highly stylized in both their decision-making tasks and in the relationship between the participant and the advisor.
The tasks are somewhat unusual in that people are seldom required to compare barely-seen visual scenes or estimate historical dates in their everyday lives.
When they do, they are unlikely to seek advice on them.
This is a limitation general to most psychology experiments in one way or another, but no less important for that.

The relationship between the participants and the advisors was also unusual. 
While some researchers have suggested that social influence phenomena can be explained by reinforcement learning from repeated interactions [@behrensAssociativeLearningSocial2008; @feldmanhallViewingAdaptiveSocial2019; @heyesKnowingOurselvesTogether2020], the kind of repetition presented in these tasks is not a typical feature of human relationships.
In some particular cases, for example working with a colleague at a job that requires rapid and repeated joint decision-making, behaviour might approximate that of our tasks, although for our domain of advisor choice to be of particular interest these people would also have to have the power to select their partner.

#### Conclusion

These experiments paint a rather equivocal picture, without being able to offer the kind of strong evidence we would like concerning the validity of the @pescetelliRoleDecisionConfidence2021 theory of confidence-weighted advice evaluation.
One major observation revealed in the experiments was the extent to which participants exhibited a wide range of preference strengths and directions, particularly where systematic effects of advisor preference were absent.
In the following chapter§\@ref(chapter-network-effects) we use agent-based computational modelling to investigate the role of this kind of heterogeneity in the formation of echo chambers in information exchange networks.
