---
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: default
  bookdown::html_document2: default
documentclass: book
---

```{r setup 02-02, echo = F, include = F}
```

# Behavioural responses to advice contexts {#chapter-context-benevolence}
\adjustmtc 

<!-- 
Present behavioural experiments in which we show sensitivity to both the advisor and the advice, and discuss the relatively high levels of advice-taking (hard task!), and how the results support the impressions gleaned from the evolutionary models: context matters in advice-taking, and discounting may be a feature of vigilant conservatism (hyperprior for deceit).
-->

<!-- Include directBenevolenceContexts stuff! -->

We suggest that the long-standing view that egocentric discounting reflects sub-optimal information processing is a consequence of taking a narrow view of the problem being solved.
While it is indeed demonstrable that people in Judge-Advisor System experiments would perform better and earn more reward if they took more advice \mccorrect{CITE}, the people who participate in those experiments also have to function in the real world where being too trusting can produce very negative outcomes.
Furthermore, advice-taking and decision-making are, like the behaviour of other organisms, ultimately mechanisms for the more efficient propagation of genes.
The task being solved by the genes in the cells of the participant in a Judge-Advisor System experiment is to effectively exploit a complex, often-unreliable, and frequently-changing world.
We suggest that egocentric discounting may result from genetic and cultural evolution favouring the default assumption that an individual's own information is a more reliable basis for decision-making for that individual than another individual's information.

The evolutionary models offered a proof-of-concept illustration that hyperpriors may evolve under a variety of contextual features that are almost always at least partially true of advice-taking situations.
In this chapter, we explore the flexibility of egocentric discounting in these contexts.
We present three experiments that examine how advice-taking changes according to the benevolence and the identifiability of advisors.
We also include a brief discussion of the literature on advisor expertise.

## Experiment 5: Benevolence of the advisor population {#be-db}

```{r be-db-load, include = F}
```

The evolutionary models discussed in the last chapter§\@ref(chapter-advice-taking-context) demonstrated that optimal advice-taking strategies depend in part upon the advice one receives being a genuine effort to help.
Difference in benevolence, or the extent to which the interests of the advisor and the judge overlap, is one of the three pillars of the @mayerIntegrativeModelOrganizational1995 model of advice-taking.
Despite this, relatively little investigation has been made into the role of benevolence in trust, as discussed previously§\@ref(context-familiarity).

Advice-taking can be contingent on the properties of the advice, or on the properties of the advisor.
In order to maximise the value of advice while minimising the potential exposure to exploitation, advice-taking should be contingent on a combination of these factors.
Where advice is plausible it should be weighted relatively equally, whether it comes from an advisor who is sometimes misleading or not, but where advice is more implausible it should only be trusted when it comes from an advisor who is never misleading.
To explore whether people's behaviour matches this pattern, participants were recruited for a series of behavioural experiments in which they were given advice on a date estimation task from advisors who were described as either always helpful or occasionally misleading.

We expected that advisor influence would be higher for advice that participants rated as 'honest' versus advice rated as 'deceptive'.
Likewise, we expected that influence would be higher for advisors who were described as 'always honest', even for advice rated as 'honest'.
In other words, we expect that participants' advice-taking depends upon both the plausibility of the advice and the benevolence of the advisor.

#### Open scholarship practices

This experiment was preregistered at `r unique(datequiz$preregistration)`.
The experiment data are available in the `esmData::` package for R from \mccorrect{!TODO[Zenodo esmData]}, and also directly from \mccorrect{!TODO[OSFify Dates task data]}.
A snapshot of the state of the code for running the experiment at the time the experiment was run can be obtained from https://github.com/oxacclab/ExploringSocialMetacognition/blob/b4289fea196f71ccf0ba0b2ae8fde12139a16301/ACv2/db.html.

This is a replication of a study of identical design that produced the same results. 
The data for the original study can be obtained from the `esmData::` R package or from \mccorrect{!TODO[OSFify]}.

There were a number of deviations from the preregistered analysis in this Experiment.
Several participants used translation software to translate the experiment website. 
We could not guarantee that the questions were accurately translated and so these participants were excluded.
Some participants never rated the Sometimes deceptive advisor's advice as 'honest', and so they were excluded in the t-test comparing advisors.

### Method {#be-db-m}

```{r be-db-m-structure}
```

#### Procedure

`r length(unique(AdvisedTrial$pid))` participants each completed `r round(sum(ceiling(tmp$n)))` trials over `r max(tmp$block)` blocks of the continuous version of the Dates task§\@ref(m-p-dates-c).
On each trial, participants were presented with an historical event that occurred on a specific year between 1900 and 2000.
They were asked to drag a marker onto a timeline to indicate the date range within which they thought the event occurred.
The markers covered `r AdvisedTrial %>% filter(!is.na(responseMarkerWidth)) %>% pull(responseMarkerWidth) %>% unique()` years, meaning that it would cover an entire decade inclusively, e.g. 1965-1975.
Participants then received advice indicating a region of the timeline in which the advisor suggested the event occurred, and rated the honesty of the advice on a three-point scale (Figure \@ref(fig:be-db-m-performance)).
Participants could then mark a final response in the same manner as their original response, and could choose a different marker width if they wished.

```{r be-db-m-performance, fig.align='center', fig.caption="Advice honesty rating.  Participants rated advice on a three-point scale according to whether they thought the advice was deceptive or honest.", out.width="80%", echo=F}
```

Participants started with `r sum(tmp$type == "practice")` block of `r tmp %>% filter(type == "practice") %>% pull(n) %>% ceiling()` trials that contained no advice to allow them to familiarise themselves with the task.
All trials in this section included feedback for all participants indicating whether or not the participant's response was correct.

Participants then did `r tmp %>% filter(type == "advice_practice") %>% pull(n) %>% round()` trials with a practice advisor to get used to receiving advice.
They also received feedback on these trials.
They were informed that they would "get advice on the answers you give" and that the feedback they received would "tell you about how well the advisor does, as well as how well you do".
Before starting the main experiment they were told that they would receive advice from multiple advisors and that "advisors might behave in different ways, and it's up to you to decide how useful you think each advisor is, and to use their advice accordingly".

Participants then performed `r sum(tmp$type == "core")` blocks of trials that constituted the main experiment.
In each of these blocks participants had a single advisor for `r tmp %>% filter(block == 2, type == "core") %>% pull(n) %>% round()` trials, plus `r tmp %>% filter(block == 2, type == "atn_check") %>% pull(n) %>% round()` attention check.
No feedback was given on answers in the main experiment blocks.

The two advisors were identical in how they generated advice, but they were labelled differently.
The advisors had different colours, and participants were told that the advisor who matched the participant's colour "will give you the **best advice that they can**", while the advisor who did not match the participant's colour "might sometimes try to direct you **away from the correct answer**".
Colours and the order in which the advisors were encountered were counterbalanced.

#### Advice profiles

Despite differences in labelling, the advisors were identical in terms of how they actually produced advice.
The advisors offered advice by placing an `r AdvisedTrial %>% filter(!is.na(advisor0confidence)) %>% pull(advisor0confidence) %>% unique()`-year wide marker on the timeline.
The marker was placed with its centre on a point sampled from a roughly normal distribution around the correct answer with a standard deviation of `r AdvisedTrial %>% filter(!is.na(advisor0confidenceVariation)) %>% pull(advisor0confidenceVariation) %>% unique()` years.

### Results

##### Exclusions

```{r be-db-exclusions}
```

Participants (total *n* = `r nrow(exclusions)`) could be excluded for a number of reasons: failing attention checks, having fewer than `r nMaxTrials - nMaxOutliers` trials which took less than `r maxTrialRT / 1000`s to complete, providing final decisions which were the same as the initial estimate on more than `r round((1 - minChangeRate) * 100)`% of trials, or using non-English labels for the honesty questionnaire.
The latter exclusion was added after data were collected because it was not anticipated that participants would use translation software in the task.
The numbers of participants who failed the various checks are detailed in Table \@ref(tab:be-db-exclusions).

The final participant list consists of `r length(unique(AdvisedTrial$pid))` participants who completed an average of `r num2str(mean(aggregate(advisor0 ~ pid, AdvisedTrial, length)$advisor0))` trials each.

```{r be-db-r-exclusion-table}
```

##### Task performance

```{r be-db-r-split}
```

```{r be-db-r-performance, fig.caption="Task performance for Experiment 5.  A: Response error. Faint lines show individual participant mean error (the absolute difference between the participant's response and the correct answer), for which the violin and box plots show the distributions. The dashed line indicates chance performance. Dotted violin outlines show the distribution of participant means on the original study which this is a replication. The dependent variable here is error, the distance between the correct answer and the participant's answer, and consequently lower values represent better performance. The theoretical limit for error is around 100."}
```

```{r be-db-r-aov}
```

Participants performed as expected, decreasing the error between the midpoint of their answer and the true answer from the initial estimate to the final decision (`r s_acc$s[1]`), which suggests that they incorporated the advice, which was indicative of the correct answer (Figure \@ref(fig:be-db-r-performance)).
The participants had less error on decisions made with the Always honest advisor than the Sometimes deceptive advisor (`r s_acc$s[2]`), although surprisingly there was no evidence that this was due to greater reduction in error scores over time for that advisor (`r s_acc$s[3]`).

Participants only had one marker they could place, and separate confidence judgements were not asked for, so we cannot directly assess confidence in these data.

##### Advisor performance

```{r be-db-r-advisor-performance}
```

The advice given by the advisors was generated stochastically from the same distribution.
Any differences will be random.
This was demonstrably the case in the domain of advice error (absolute distance between the centre of the advice marker and the correct year; `r tt$s[1]`).
The Bayes' Factor for the domain of agreement -- the absolute distance between the centre of the advice marker and the centre of the participant's initial estimate marker -- was essentially on the threshold (`r tt$s[2]`).

##### Advice ratings

```{r be-db-r-advice-ratings, fig.caption="Advice rating in Experiment 5.  The polar plots show the number of times each participant gave the given rating to the advice of each advisor. The colour density illustrates the number of participants who gave at least that many ratings to the advice of an advisor."}
```

The advisors' advice was rated differently by the participants, as shown in Figure \@ref(fig:be-db-r-advice-ratings) ($\chi^2$`r s`).
This indicates that participants understood the task and that the manipulation worked as intended, with more suspicion applied to the advice from the Sometimes deceptive advisor.

##### \OpenScience{prereg} Effect of advice

```{r be-db-r-advice, results='asis'}
```

Participants chose their own ratings for the advice, and it was common for participants not to use all ratings for all advisors (e.g. many participants never rated advice from the Always honest advisor as Deceptive).
This meant that the statistical tests preregistered for this hypothesis were broken down into separate contrasts of advice and advisor. 
Using a more complete test, such as 2x3 ANOVA, would have suffered greatly from missing values.

To explore the effect of advice, a 1x3 ANOVA was run on weight on advice across ratings. 
In all, `r length(unique(x$pid))`/`r length(unique(Familiarization$pid))` (`r num2str(length(unique(x$pid)) / length(unique(Familiarization$pid)) * 100)`%) participants had at least one trial rated with each of the three ratings.
The weight on advice differed according to the rating assigned the advice (`r s_advice$s[1]`; Mauchly's test for Sphericity W=`r prop2str(aov_advice[["Mauchly's Test for Sphericity"]][2][[1]])`, p=`r prop2str(aov_advice[["Mauchly's Test for Sphericity"]][3][[1]])`).
As expected, participants were more influenced by advice they rated as Honest compared to advice they rated as Deceptive.

##### \OpenScience{prereg} Effect of advisor

```{r be-db-r-advisor, fig.caption="Weight on Advice in Experiment 5.  Shows the weight of the advice of the advisors. Only trials where the participant rated the advice as Honest are included. The shaded area and boxplots indicate the distribution of the individual participants' mean weight on advice. Individual means for each participant are shown with lines in the centre of the graph. The dashed outline shows the distribution of participant means in the original study of which this is a replication."}
```

To distinguish the effects of the advisor from the effects of the advice, we compared weight on advice for only those trials where the participant rated the advice as Honest. 
This approach has the limitation that `r lost` (`r num2str(lost / length(unique(Familiarization$pid)) * 100)`%) participants had to be dropped due to never rating advice from the Sometimes deceptive advisor as Honest.

Comparing the two (Figure \@ref(fig:be-db-r-advisor)) showed that participants placed more weight on the Honest advice from the Always honest advisor (`r .T`).

#### Exploration

```{r be-db-r-overall, fig.caption="Advice response in Experiment 5.  Scatter plot of advice distance and advice influence. The dashed line shows x = y. Colours represent different advice ratings. Dots represent individual trials, and lines show the pattern within each rating."}
```

Figure \@ref(fig:be-db-r-overall) shows the overall pattern of advice-taking in the experiment. 
The difference in the number of dots of each colour reflects the difference in participants' ratings of advice between advisors. 

The lines illustrate the relationship between the distance of the advice from the participant's initial estimate and the amount the participant moved the marker towards the advisor's advice for their final decision.
The dashed line indicates complete acceptance of the advice, while the bottom triangle below the dashed line indicates incomplete acceptance.

A linear mixed model was used to better understand the significance of the relationships in the figure, predicting influence on a trial from the advisor, the distance of the advice, and rating (dummy-coded). 
Random intercepts were included for participant.
A similar Bayesian model was included to produce Bayes factors.

Overall, the distance between the initial estimate and the advice was hugely influential, with an increase in distance leading to an approximately equal increase in influence ($\beta$=`r coefs$s[3]`).
This indicates that the advice rated Honest from the Always honest advisor was generally followed, as is shown clearly in Figure \@ref(fig:be-db-r-overall).
This pattern indicates that the participants see the difference between their own estimates and the advisor's as indicating that they themselves are mistaken.

Advice rated as Deceptive from the Sometimes deceptive advisor was substantially less influential ($\beta$=`r coefs$s[8]`), and this was complemented by the relationship between distance and influence being substantially reduced in this case ($\beta$=`r coefs$s[12]`).

There are other patterns in Figure \@ref(fig:be-db-r-overall) that do not come out in the statistics, possibly due to the very low trial and participant numbers, but are suggestive of a pattern we might expect.
The relationship of advice rated Honest is similar between the advisors: as the advice gets further away it retains its level of influence and the participants are willing to go further to match it.
This is not tested directly in the stats, but there is no significant effect of advisor alone ($\beta$=`r coefs$s[2]`), the presence of which would indicate that Honest-rated advice differed between advisors.
The Bayesian analogue of the test indicated that there was not enough evidence to decide whether Advisor alone was an important factor.

Similarly, there may be a difference in the way the Possibly Deceptive advice was received from the Sometimes deceptive advisor as compared to the Always honest advisor (`r coefs$s[7]`), or in how the influence of this advice related to the distance between the advice and initial estimate markers (`r coefs$s[11]`).
The statistics did not support this, and the Bayesian statistics suggested that there was sufficient evidence against either effect being present.

### Discussion

Both the source and the plausibility of the advice matter, and in this task they interacted such that discounting primarily occurred where advice was offered that differed substantially from the participant's initial estimate and came from the advisor the participants were told might mislead them.
Participants adapted to the context of the advice, both in terms of how readily they were to categorise the advice as dishonest and in terms of how much they were influenced by the advice.
As advice got more distant from the initial estimate, i.e. decreased on our measure of plausibility, participants had to decide whether the discrepancy was due to their own error or their advisor's.
Where they were in a context that suggested the advisor was trustworthy, they were more likely to ascribe the error to themselves, rating the advice as honest and adopting it for their final decision. 
Where they were in a context that suggested the advisor was not trustworthy, they were more likely to label the advice as misleading and to retain their initial estimate as their final decision.

These observations complement the evolutionary simulations and the benevolence component of the three-factor model of trust described by @mayerIntegrativeModelOrganizational1995.
Nevertheless, we have demonstrated sensitivity to context, but not universal discounting due to hyperpriors.
It remains a matter of speculation that people exercise epistemic hygiene by ensuring that information comes from trusted sources before integrating it, and that no source is as trusted as one's own mind.
This result is in keeping with evidence from experiments where initial estimates are labelled as advice (and vice-versa), in which participants frequently show an unusual level of acceptance of the advice suggestive of their performing egocentric discounting of their own initial estimate because they have accepted the labels and adopted the advice as their own initial estimate [@sollJudgmentalAggregationStrategies2011]. 

#### Limitations

Even compared to the other experiments in this thesis, these experiments had a low participant count. 
As with other Dates task studies, data collection stopped when the Bayes Factor for the main experimental hypothesis reached one of the two thresholds (1/3 > BF > 3).
This, combined with the low trial count for each participant, meant that there were interesting follow-up questions that the data were unable to address.
In keeping with the open science approach, we suggest that future investigations exploring those questions take them as preregistered hypotheses.

The Dates task is one that participants find challenging, leading to generally high levels of advice taking in the absence of other effects [@ginoEffectsTaskDifficulty2007; @yonahTheyDonKnow2021].
This means that the Honest advisor seemed to be entirely trusted.
As discussed in the introduction to this section§\@ref(chapter-context), however, even greatly trusted advisors' advice is usually subject to some egocentric discounting.

## Noise in the advice

The second scenario§\@ref(models-scenario-2) explored in the evolutionary models added noise to the advice agents received and demonstrated that this provided an evolutionary pressure towards egocentric discounting.
The addition of noise in a point-value estimation task lowers the relative performance, and thus this scenario was essentially a manipulation of advisor expertise. 
This scenario is not explored in behavioural experiments because its conclusions are well supported by existing literature.
Specifically, the literature demonstrates the normativity of discounting where the judge outperforms the advisor, that advice-taking is sensitive to advisor expertise, and that people are likely to consider themselves superior to the average advisor.
This demonstration is supplemented with a more comprehensive model of the utility of advice according to the ability to identify the more expert opinion, the relative accuracy of the advisor and judge, and the independence of the opinions [@sollStrategiesRevisingJudgment2009].
A more complete account of the effects of advisor expertise was provided earlier§\@ref(context-expertise).

Views of relative expertise may also be affected by self-enhancement bias [@brownEvaluationsSelfOthers1986].
We expect that this is somewhat dependent upon the difficulty of the task presented; people faced with a difficult task will under- rather than overestimate their ability relative to others [@ginoEffectsTaskDifficulty2007].
Taken together, then people are likely to consider themselves more able on a given task than an arbitrary advisor, and consequently that they are likely to downweight advice relative to their own initial estimate.
This behaviour is supported by normative models which show biasing towards the better estimator (in this case the judge) is the optimal strategy [@sollStrategiesRevisingJudgment2009; @mahmoodiEqualityBiasImpairs2015].
As discussed in the scenario, the belief that one is better at a task than the average advisor may not be misguided: advisors may not dedicate the same amount of time, concentration, or thought to producing advice as judges do for initial estimates.
Judges have to live with the consequences of their decisions, while advisors do not.

## Confidence mapping

The third scenario§\@ref(models-scenario-3) explored in the evolutionary models assigned each agent a confidence mapping, and demonstrated that discounting emerged as an appropriate response where the advisor's confidence mapping was unknown.
The key difficulty in conducting behavioural experiments to test the effects of known vs unknown confidence mapping is finding a manipulation of confidence mapping knowledge which is not confounded by familiarity with an advisor or the amount of information provided by an advisor.

We attempted to investigate this in two ways. 
Firstly, we performed an experiment where participants received advice over blocks of trials from either the same advisor on each trial or a different advisor on each trial.
Secondly, we familiarised participants with two advisors who differed in their use of the confidence scale, and then tested whether participants responded differently based on whether they could identify which of those two advisors was providing advice.

Neither experiment provided evidence consistent with the hypothesis that familiarity with an advisor's confidence calibration leads to greater trust in that advisor's advice.
We suggest that this may be a failure in experimental design rather than reliable evidence of the absence of this feature of advice-taking behaviour.

### Experiment 6: Individuality as a cue to confidence {#be-ce}

The expression of confidence is highly idiosyncratic [@aisIndividualConsistencyAccuracy2016; @navajasIdiosyncraticNatureConfidence2017].
Given this, we hypothesised that the same advice may be treated differently depending upon whether or not it was labelled as coming from repeated interactions with a single individual or from a series of one-off interactions with different individuals.
Where the advice comes from the same individual over and over again, participants should become more aware of that individual's confidence calibration (the relationship between their confidence and the probability they are correct), and should thus be able to better discriminate higher-quality (more confident) advice.

In this experiment the effect of individuality is confounded with familiarity, a feature that we expect will increase the palatability of advice. 
While participants are learning about the advisors, and learning more about the confidence calibration of the individual advisor than that of the group members, they are also becoming more familiar with the individual advisor.
Nevertheless, this is a useful experiment because it is capable of indicating the absence of an effect: if the manipulation proves unable to produce greater influence from the individual advisor it will do so without a confound. 
If the experiment demonstrates higher influence for the individual advisor then further experiments can be run to attempt to isolate confidence calibration knowledge from mere exposure.

```{r be-ce-load, include = F}
```

#### Open scholarship practices

This experiment was not preregistered because it was highly exploratory, and we were doubtful that the manipulation would work.
The experiment data are available in the `esmData::` package for R from \mccorrect{!TODO[Zenodo esmData]}, and also directly from \mccorrect{!TODO[OSFify Dates task data]}.
A snapshot of the state of the code for running the experiment at the time the experiment was run can be obtained from https://github.com/oxacclab/ExploringSocialMetacognition/blob/4d8aace6b864c4465cacd8579ec1abd870dd65d2/ACBin/ce.html.

#### Method

```{r be-ce-m-structure}
```

##### Procedure

`r length(unique(AdvisedTrial$pid))` participants each completed `r round(sum(ceiling(tmp$n)))` trials over `r max(tmp$block)` blocks of the binary version of the Dates task§\@ref(m-p-dates-b).
On each trial, participants were presented with an historical event that occurred on a specific year between 1900 and 2000.
They were then given an anchor year within the 1900-2000 range. 
The task for the participant was to indicate whether the event occurred before or after the anchor year. 
To answer 'before' they selected a point on the lefthand column, and to answer 'after' they selected a point on the righthand column.
They indicated their confidence by the point they selected on the chosen column: the higher up the column they chose the greater confidence the signalled in their answer.

Participants then received advice from an advisor indicating which of the columns the advisor considered the correct answer.
The advisor also indicated a confidence in their response, indicated by the height of the advisor's avatar on the indicated bar (Figure \@ref(fig:be-ce-m-advice)).

```{r be-ce-m-advice, fig.align='center', fig.caption="Advice confidence.  Advisors' markers shifted position vertically to indicate the confidence with which the advice was give. As with the participants' own responses, higher placement on the column indicated higher confidence.", out.width="80%", echo=F}
```

Participants started with `r sum(tmp$type == "practice")` block of `r tmp %>% filter(type == "practice") %>% pull(n) %>% ceiling()` trials that contained no advice to allow them to familiarise themselves with the task.
All trials in this section included feedback for all participants indicating whether or not the participant's response was correct.

Participants then did `r tmp %>% filter(type == "advice_practice") %>% pull(n) %>% round()` trials with a practice advisor to get used to receiving advice.
They also received feedback on these trials.
They were informed that they would "get advice about the correct answer" and that the "advisors indicate their confidence in a similar way to you, by placing their marker higher on the scale if they are more sure".

Participants then performed `r sum(tmp$type == "core")` blocks of trials that constituted the main experiment.
These blocks came in pairs, with each pair containing one block of `r tmp %>% filter(block == 2) %>% pull(n) %>% sum()` trials that included feedback followed by one block of `r tmp %>% filter(block == 3) %>% pull(n) %>% sum()` trials that did not include feedback.
`r tmp %>% filter(block == 2, type == "atn_check") %>% pull(n)` trial in the first block in each pair was an attention check trial.
Each pair of blocks had a different advisor presentation.

In one of the pairs of blocks, the advice was always labelled as coming from the same advisor. 
In the other pair of blocks, the advice on each trial was labelled as coming from a different advisor.
The order that the participants encountered these presentations in was counterbalanced.

##### Advice profiles {#be-ce-m-advice-profiles}

Despite differences in labelling, the advisors were identical in terms of how they actually produced advice.
The advice was determined on each trial by selecting a point drawn from a normal distribution around the correct answer with standard deviation of `r AdvisedTrial %>% filter(!is.na(advisor0confidenceVariation)) %>% pull(advisor0confidenceVariation) %>% unique()` years.
This point served as the advisor's internal estimate of the correct answer. 
The advisor then gave the appropriate answer according to whether or not the internal estimate was before or after the anchor year, and scaled their confidence based on the distance between those two years.
The advisor was maximally confident where the difference between the internal estimate and the anchor year was at least `r AdvisedTrial %>% filter(!is.na(advisor0confidence)) %>% pull(advisor0confidence) %>% unique()` years.

#### Results

##### Exclusions

```{r be-ce-exclusions}
```

Participants (total *n* = `r nrow(exclusions)`) were excluded for a number of reasons: having fewer than `r nMaxTrials - nMaxOutliers` no-feedback trials which took less than `r maxTrialRT / 1000`s to complete, or providing final decisions which were the same as the initial estimate on more than `r round((1 - minChangeRate) * 100)`% of trials.
Table \@ref(tab:be-ce-exclusions) shows the number of participants excluded and the reasons why.
Participants who failed attention checks would have been immediately dropped, but no participants did so.

The final participant list consists of `r length(unique(AdvisedTrial$pid))` participants who completed an average of `r num2str(mean(aggregate(advisor0 ~ pid, AdvisedTrial, length)$advisor0))` trials each.

```{r be-ce-r-exclusion-table}
```

##### Task performance

```{r be-ce-r-split}
```

```{r be-ce-r-performance, fig.caption="Task performance for Experiment 6.  A: Response accuracy. Faint lines show individual participant means, for which the violin and box plots show the distributions. The dashed line indicates chance performance. Dotted violin outlines show the distribution of actual advisor accuracy.  Because there were relatively few trials, the proportion of correct trials for a participant generally falls on one of a few specific values. This produces the lattice-like effect seen in the graph. Some participants had individual trials excluded for over-long response times, meaning that the denominator in the accuracy calculations is different, and thus producing accuracy values which are slightly offset from others'.  B: Confidence. Faint lines show individual participant means, for which the violin and box plots show the distributions.  C: Influence. Participants' weight on the advice for advisors in the Familiarization and Test stages of the experiment. The shaded area and boxplots indicate the distribution of the individual participants' mean influence of advice. Individual means for each participant are shown with lines in the centre of the graph. The theoretical range for influence values is [-2, 2]."}
```

```{r be-ce-r-performance-aov}
```

Accuracy during the Familiarization trials (Figure \@ref(fig:be-ce-r-performance)A) was higher for final decisions than for initial estimates (`r s_acc$s[2]`), and higher for the Consistent individual advisor than for the group (`r s_acc$s[1]`).
There was no significant effect of advisor presentation on improvement (`r s_acc$s[3]`).

There were no significant effects for the ANOVA on confidence (Figure \@ref(fig:be-ce-r-performance)B).
Neither the correctness of the initial estimate (`r s_conf$s[1]`), nor whether the response was the initial estimate or final decision (`r s_conf$s[2]`) appeared to systematically affect confidence.
There was also no significant interaction to indicate that confidence changed over time differently for correct versus incorrect initial estimates (`r s_conf$s[3]`).

Likewise, no significant effects were found for the ANOVA on influence (Figure \@ref(fig:be-ce-r-performance)C).
Neither the advisor presentation (`r s_inf$s[1]`), nor whether the trial was in the Familiarization stage (with feedback) or the test stage (without feedback) appeared to be systematically linked to the influence of the advice (`r s_inf$s[2]`). 
There was also no indication that the influence of the advisors' advice changed differently between stages (`r s_inf$s[3]`).

##### Advisor performance

```{r be-ce-r-advice}
```

The advice is generated probabilistically using the same rules for both advisor presentations.
The advisors' advice is not dependent on the participants' initial estimates, but it is useful nevertheless to compare the advisors' agreement and accuracy rates.
The advisors were demonstrably similar in their agreement rates (`r .T.agr`), but not so in their accuracy rates (`r .T.acc`), driven by a difference in the likelihood of agreeing with incorrect initial estimates.
It is unlikely, but plausible, that the Consistent individual advisor may have been slightly more influential because of their higher agreement rate, a systematic effect that would go in the same direction as our hypothesis and that would therefore require a caveat during interpretation. 
We note here, however, that participants received feedback during this Familiarization phase, and that Experiment 3B§\@ref(ac-ava-dates-r-h) demonstrated that accuracy is an important feature, and agreement an unimportant feature, in the Dates task where feedback is available.

##### Effect of advisor presentation

```{r be-ce-r-h}
```

The hypothesis for this study was that, in the key Test trials where participants did not receive feedback, the advisor presented as a consistent individual would be more influential than the advisor presented as different members of a group on each trial.
As illustrated in the righthand panel of Figure \@ref(fig:be-ce-r-performance)C, influence was not systematically different between the advisor presentations on the Test trials (`r .T`).

From this we can conclude that the manipulation was not effective in differentiating the advisors or that such differences as were produced do not affect the influence of advice.

#### Simulation

```{r be-ce-r-sim, fig.caption="Simulated data for Experiment 6.  Simulated participants' weight on the advice for advisors in the Test stage of the experiment. The shaded area and boxplots indicate the distribution of the individual participants' mean influence of advice. Individual means for each participant are shown with lines in the centre of the graph. The theoretical range for influence values is [-2, 2]."}
```

We conducted a simulation in which we modified participants' actual data by substituting the final confidence values for values calculated by a model that reduces egocentric discounting for the Consistent individual advisor by a set effect size. 
The simulations indicated that, even where we directly simulated differences in egocentric discounting for each advisor, we were unable to detect the effects we were looking for (Figure \@ref(fig:be-ce-r-sim); `r .T.sim`).

#### Discussion

The manipulation at the centre of this experiment did not work. 
We presented participants with the same advice, labelled either as always coming from the same advisor or as coming from a different advisor on each trial. 
We had expected that presenting participants with a single advisor would allow them to learn about that advisor's ability to perform the task, and how well their confidence was calibrated (i.e. how strong the relationship between increased confidence and increased probability of being correct was).
We did not observe differences in the influence of advice as a function of the presentation of the advisor. 
Furthermore, in a simulation that altered the participants' final decisions to implement a difference in the extent to which advice was discounted between advisors. 
The simulation also failed to detect the effects we were looking for.

The two reasons why we failed to detect the effects, even in simulation, are that the manipulation was not powerful enough or that there is no systematic relationship between calibration knowledge (and familiarity more generally) and advice influence.
The manipulation may not have been strong enough because participants may have paid relatively little attention to the identity of the advisor and focused more on the content of the advice.
Participants may also have learned about the calibration distributions just the same for individual and group advisors: statistically the experience is the same and some research has suggested that statistical mechanisms such as associative learning may be sufficient to explain social learning phenomena [@behrensAssociativeLearningSocial2008; @feldmanhallViewingAdaptiveSocial2019].
It is also possible, though we suspect less likely given prior evidence of sensitivity to calibration [@pescetelliRoleDecisionConfidence2021], that the participants were simply unable to distinguish the advisors even in principle, or that any distinction they did make failed to translate into differential influence.

### Experiment 7: Identifiability of advice {#be-ck}

The results of Experiment 6 were not promising.
Consequently, we entirely redesigned the manipulation in an attempt to place the calibration of the advice in the forefront of participants' experience.
To this end, we familiarised participants with two advisors whose accuracy, probability of agreement, and confidence calibration were identical, but whose use of the confidence scale differed. 
A Low confidence advisor used the bottom two-thirds of the confidence scale, while a High confidence advisor used the top two-thirds. 

On the test trials, participants frequently saw advice where the confidence lay in the middle third of the scale.
On some of these trials, the advice was labelled as coming from a specific advisor.
If the advice came from the Low confidence advisor it would represent high confidence advice, and imply a high probability that it was correct.
If the advice came from the High confidence advisor, it would represent low confidence advice, and imply a low probability that it was correct.
On the remainder of these trials, the advice was labelled as coming from an unknown one of those two advisors.
We expected that advice that was labelled in this way would be treated differently relative to advice that was identifiable because it was impossible for participants to appropriately interpret the confidence (and therefore probability of correctness) of the advice.

```{r be-ck-load, include = F}
```

#### Open scholarship practices

This experiment was not preregistered because it was highly exploratory.
The experiment data are available in the `esmData::` package for R from \mccorrect{!TODO[Zenodo esmData]}, and also directly from \mccorrect{!TODO[OSFify Dates task data]}.
A snapshot of the state of the code for running the experiment at the time the experiment was run can be obtained from https://github.com/oxacclab/ExploringSocialMetacognition/blob/9ac26116e348f8c4ff5617a8e68710b889bc7e08/ACBin/ck.html.

#### Method

```{r be-ck-m-structure}
```

##### Procedure

`r length(unique(AdvisedTrial$pid))` participants each completed `r round(sum(ceiling(tmp$n)))` trials over `r max(tmp$block) + 1` blocks of the binary version of the Dates task§\@ref(m-p-dates-b).
The procedure for filling in responses and the way the advice was represented was the same as described for Experiment 6§\@ref(be-ce).

Participants started with `r sum(tmp$type == "practice")` block of `r tmp %>% filter(type == "practice") %>% pull(n) %>% ceiling()` trials that contained no advice to allow them to familiarise themselves with the task.
All trials in this section included feedback for all participants indicating whether or not the participant's response was correct.

Participants then did `r tmp %>% filter(type == "advice_practice") %>% pull(n) %>% round()` trials with a practice advisor to get used to receiving advice.
They also received feedback on these trials.
They were informed that they would "get advice about the correct answer" and that the "advisors indicate their confidence in a similar way to you, by placing their marker higher on the scale if they are more sure".

Before performing trials with an advisor, participants saw the advisor's avatar alongside a speech bubble in which the advisor introduced themself.
On the same screen, participants saw a scorecard for that advisor (Figure \@ref(fig:be-ck-m-scorecard)).
Scorecards were introduced to the participant after the initial practice (without advice).

```{r be-ck-m-scorecard, fig.align="center", fig.caption="Advice scorecard for Experiment 7.  The scorecards indicated the relationship between confidence and accuracy, allowing participants to see how well calibrated they or an advisor was.", out.width="80%", echo=F}
```

Participants then performed `r sum(tmp$type == "core")` blocks of trials that constituted the main experiment.
In the first `r tmp %>% filter(feedback == 1) %>% pull(block) %>% unique() %>% length()` blocks participants were familiarised with their advisors over `r tmp %>% filter(feedback == 1) %>% filter(block == min(block)) %>% pull(n) %>% ceiling() %>% sum()` trials each (`r tmp %>% filter(feedback == 1) %>% filter(block == min(block), type == "atn_check") %>% pull(n) %>% ceiling()` of which was an attention check).
The order in which participants encountered the advisors was counterbalanced, and participants received feedback during these Familiarization trials.

Finally, participants performed `r tmp %>% filter(feedback == 0) %>% pull(block) %>% unique() %>% length()` block of `r tmp %>% filter(feedback == 0) %>% pull(n) %>% ceiling()` Test trials that did not include feedback about the correct answer.
Before this block, participants were reminded again about their advisors, and shown the introduction screen with the scorecards for each advisor again.
The scorecards were shown individually, and then displayed on the same screen next to one another, and the participants invited to "compare them with one another".
During these Test trials, advice was sometimes labelled as coming from a specific one of the advisors encountered during the Familiarization trials, and sometimes the advice was labelled as coming from an unspecified one of those advisors (Figure \@ref(fig:be-ck-m-hybrid)).

```{r be-ck-m-hybrid, fig.align='center', fig.caption="Hybrid advisor presentation.  The Hybrid advisor presentation was designed to indicate that one or other of the previously-encountered advisors would be giving advice, but that the participant did not know which. This was done by dividing the image diagonally and drawing half of one avatar in the top-left area and half of the other avatar in the bottom-right area.", out.width="80%", echo=F}
```

##### Advice profiles

```{r be-ck-advice-profiles, fig.caption="Advice distribution map for advisors in Experiment 7.  The High confidence equates to 100\\% correct, Medium to 66\\%, and Low to 33\\%. The dashed lines show the overlap area between the minimum confidence for the High confidence advisor and the maximum confidence for the Low confidence advisor. Note that the advisors are not equally correct on average in this zone: the Low confidence advisor is substantially more accurate because they are idiosyncratically more confidence."}
```

There are two advisors in this experiment, a High confidence advisor and a Low confidence advisor.
Before the Familiarization block with each advisor, the advisors introduced themselves with a statement about their advice-giving style. 
The High confidence advisor stated "I'm confident and outgoing. I tend to make up my mind and stick to it."
The Low confidence advisor stated "I'm cautious and careful. I try to keep an open mind even when I've made my choice."

The Advice profiles (Figure \@ref(fig:be-ck-advice-profiles)) for the two advisors were balanced in terms of the information provided by each advisor: both advisors had a subjectively high confidence at which they were 100% accurate, a medium confidence range within which they were 66% accurate, and a low accuracy range in which they were 33% accurate. 
Crucially, these ranges span different parts of the confidence scale; the Low confidence advisor never expressed confidence above 66%, and the High confidence advisor never expressed confidence below 33%.

The advisor's advice during the Familiarization phase was choreographed to provide all participants with an exact insight into the underlying calibration.
Each advisor offered three estimates in each of their three confidence zones.
All of the high-confidence advice was correct, two of the medium-confidence, and one of the low-confidence.

During the Test phase, advisors provided advice while either labelled unambiguously, as they had been during the Familiarization phase, with their avatar and advisor number, or ambiguously, with a hybrid avatar and question marks instead of the advisor number (Figure \@ref(fig:be-ck-m-hybrid)).
Each advisor offered 7 pieces of advice while labelled unambiguously, and 7 while labelled ambiguously. 
Each of these sets of 7 advice had the following structure: three trials in the third of the confidence scale unique to the advisor that were correct, two trials in the ambiguous third of the confidence scale where the advisor agreed with the participant's initial estimate, and two trials in the ambiguous third where the advisor disagreed with the participant's initial estimate. 

The decision to include advice outside the ambiguous third of the confidence scale (between the dashed lines in Figure \@ref(fig:be-ck-advice-profiles))) was taken with the aim of ensuring participants' experience of the advice during the Test phase felt natural.
Unfortunately, this meant that the advisors either had to degrade their calibration or they had to have different accuracy rates (either overall or within the ambiguous third of the confidence scale). 
Between these two lemmas we opted for the former, meaning that during the Test phase the Low confidence advisor's calibration changed such that all low-confidence advice was accurate.

The most important feature of this complex advice profile construction is that there are an equal number of trials that have advice with confidence in the ambiguous range for each advisor and for each presentation (ambiguous or identifiable).
Within these trials, agreement is also tightly controlled meaning that each advisor-presentation combination agrees on half the trials and disagrees on half the trials.
These `r 4 * 2 * 2` Key trials are central to testing our hypothesis that participants will be less influenced by advice when the source is ambiguous, so it is important that they are as balanced as possible for agreement and number.

#### Results

##### Exclusions

```{r be-ck-exclusions}
```

Participants (total *n* = `r nrow(exclusions)`) were excluded for a number of reasons: having fewer than `r nMinKeyTrials` Key trials which took less than `r maxTrialRT / 1000`s to complete, or providing final decisions which were the same as the initial estimate on more than `r round((1 - minChangeRate) * 100)`% of trials.
Table \@ref(tab:be-ck-exclusions) shows the number of participants excluded and the reasons why.^[Note that no participants were excluded only for failing to finish the study.]
Participants who failed attention checks do not reach this stage of the experiment.

The final participant list consists of `r length(unique(AdvisedTrial$pid))` participants who completed an average of `r num2str(mean(aggregate(advisor0 ~ pid, AdvisedTrial, length)$advisor0))` trials each.
Many participants were excluded using our typical exclusion criteria, but the results of the main statistical tests are the same when participants who seldom altered their responses are left in the sample, even where they did not complete the entire study. 

```{r be-ck-r-exclusion-table}
```

##### Task performance


```{r be-ck-r-split}
```

```{r be-ck-r-performance, fig.caption="Task performance for Experiment 7.  A: Response accuracy. Faint lines show individual participant means, for which the violin and box plots show the distributions. The full width dashed line indicates chance performance, and the half width dashed lines indicate advisor accuracy. Because there were relatively few trials, the proportion of correct trials for a participant generally falls on one of a few specific values. This produces the lattice-like effect seen in the graph. Some participants had individual trials excluded for over-long response times, meaning that the denominator in the accuracy calculations is different, and thus producing accuracy values which are slightly offset from others'.  B: Confidence. Faint lines show individual participant means, for which the violin and box plots show the distributions."}
```

```{r be-ck-r-performance-aov}
```

Participants increased their accuracy (Figure \@ref(fig:be-ck-r-performance)A) from initial estimate to final decision (`r s_acc$s[2]`). There was no evidence of a difference between the advisors in either overall accuracy (`r s_acc$s[1]`) or in the increase in accuracy following advice (`r s_acc$s[3]`).

Participants were more confident (Figure \@ref(fig:be-ck-r-performance)B) in their responses when their initial estimate was correct (`r s_conf$s[1]`).
There was no evidence that they were systematically more confident on final decisions compared to initial estimates (`r s_conf$s[2]`), or that confidence change between decisions differed as a function of whether or not the initial estimate was correct (`r s_conf$s[3]`). 
This pattern of participants' accuracy improving while their confidence does not may indicate a lack of metacognitive awareness of their own performance.
This is a little strange given the number of trials in this experiment that included feedback, and the frequent inclusion of scorecards that indicated to participants how well they had been performing on recent trials.

##### Effect of advisor presentation

```{r be-ck-r-key-trials, fig.caption="Key trials in Experiment 7.  Trials were matched for agreement and confidence across advisor presentation and advisor identity. The Flavour trials were included to avoid the feeling of the task changing dramatically from the Familiarization blocks to the Test block. The Key trials occur where advice could potentially come from either advisor. If the advice came from the High confidence advisor it represented a low confidence response; it if came from the Low confidence advisor it represented a high confidence response. If the advisor came from an ambigous (hybrid) source, the participant would not know whether it represented a high or low confidence response."}
```

```{r be-ck-r-h, fig.caption="Advice influence in Experiment 7.  Participants' weight on the advice for advisors in the Test stage of the experiment. The shaded area and boxplots indicate the distribution of the individual participants' mean influence of advice. Individual means for each participant are shown with lines in the centre of the graph. The theoretical range for influence values is [-2, 2]."}
```

The main hypothesis in this experiment is that advice will be treated differently if it comes from an identifiable as opposed to an ambiguous source.
Key trials occur in that band of the 
We thus expect that the High confidence advisor's advice will be more influential when the source is ambiguous, because participants who know that the advice comes from the High confidence advisor will know that the confidence score represents that advisor's low confidence advice.
The opposite prediction is made for the Low confidence advisor.

These predictions were not borne out in the data. 
A 2x2 ANOVA of Advisor by presentation indicated no significant effects.
Furthermore, the numerical direction of effects was against our prediction.
As expected, there was no main effect to indicate that Hybrid presentation would be more or less influential than Unambiguous presentation (`r s_inf$s[1]`), and no main effect of advisor to indicate that, absent Unambiguous presentation, one advisor was more influential than the other (`r s_inf$s[2]`).
The interaction is not significant (`r s_inf$s[3]`), and it goes in the opposite direction numerically to the one we would expect.
The Unambiguous presentation of the Low confidence advisor is _less_ influential, and the Unambiguous presentation of the High confidence advisor _more_ influential than their Hybrid presentation counterparts.

##### Predictors of advice influence

```{r be-ck-r-lmm}
```

It is quite possible that participants failed to adequately grasp the calibration of the advisors, despite the lengths that we went to in order to highlight the importance of this feature.
Indeed, a paired T-test of the influence of the advisors in Key trials where they were presented Unambiguously indicated that the High confidence advisor was numerically _more_ influential than the Low confidence advisor, despite that advisor offering less useful advice. 
Statistically, there was not enough evidence to conclude whether or not the effect was present or absent.

This suggested that participants were forming a simple attachment to the more confident advisor, perhaps following a heuristic that the more confident advisor would give better advice.
Indeed, linear mixed modelling indicated that, when predicting the influence on Key trials from the advisor, presentation, advisor-by-presentation interaction, and advice confidence (with random intercepts for participant), only advice confidence was a significant predictor ($\beta$=`r coefs$s[4]`).
The other main predictors were both demonstrably absent ($\beta_{\text{High confidence advisor}}$=`r coefs$s[2]`; $\beta_{\text{Unambiguous presentation}}$=`r coefs$s[3]`), and there was not sufficient evidence to adjudicate on the presence of an interaction ($\beta_{\text{High confidence advisor, Unambiguous presentation}}$=`r coefs$s[5]`).

#### Discussion

We attempted to manipulate participants' ability to use their knowledge of advisors' idiosyncratic confidence expression to perform our Dates estimation task.
We were unable to demonstrate that participants did so, and it seemed as though participants paid more attention to the advice than its source.
While the effects were not statistically significant, they did trend in the opposite direction to that hypothesised, and it appeared as if participants had developed a mild positive association between the more confident advisor and more confident advice, treating that advisor as more influential even when they expressed a moderate level of confidence.

There are several features of this experiment that may have led to the underwhelming conclusion. 
First, the advisors' gravatar images may be harder for participants to differentiate than human faces.
Second, without offering an incentive beyond the innate appeal of the task, participants may not have been motivated to absorb the complex confidence calibration information presented to them, especially where the time cost to do so is not offset by performance-based payment.
Third, the somewhat artificial nature of the task may limit participants' interest in the character of the advisors.
Adding additional information beyond the simple introductory speech bubble may have helped to alleviate this issue.

Whether or not additional appeal and character for the advisors would improve participants' sensitivity to the advisors' use of the confidence scale, these results cast doubt on a simple mechanistic implementation of our model of advice-taking.

## General discussion

The results of the direct benevolence manipulation in Experiment 5 show that people are sensitive to the motivations of their advisors, and exercise appropriate caution where those motivations may mean the advice is misleading.
They also demonstrate that, even where advice is considered trustworthy, it is discounted when coming from a less trusted advisor.
Together with existing literature on the effects of advisor expertise, this supports the idea from the models that advice-taking can be flexibly adjusted according to the context.

The results of the confidence mapping experiments were less conclusive.
We were unable to produce a manipulation which was sufficiently clear and strong to produce observable effects.
It is plausible that people are sensitive to their knowledge of an advisor's confidence mapping, but it is also plausible that this degree of flexibility is beyond most people, and that simple heuristics such as relying on cultural norms about the meanings of metacognitive terms [@roseanoCommunicatingEpistemicStance2016; @dhamiInterpersonalComparisonSubjective2005; but see @wallstenMeasuringVagueMeanings1986] are used instead of complex calculations.
The lack of flexibility on the timescale of a behavioural experiment does not, of course, negate the possibility of flexibility on the timescale of a human interpersonal relationship (perhaps there are a certain number of people whose confidence mappings we can track, as suggested by Robin Dunbar's Social Brain Hypothesis [@dunbarHowManyFriends2010]^[Note that this hypothesis has been viewed increasingly sceptically in recent years, as neatly covered by @lindenforsDunbarNumberDeconstructed2021]).
Nor does it negate the possibility of a genetic or cultural evolutionary mechanism baking in advice discounting as a protection against unknown confidence mapping, although it is questionable whether advice has been occurring in human societies for long enough to allow the former to take place.
We have a plausible explanation of egocentric which only relies on rational responses to environmental effects.
These effects are ubiquitous, and thus a ubiquitous egocentric bias prior to engaging with the specifics of a situation makes sense.
It is entirely plausible that experiments showing egocentric discounting behaviour fail to overcome the hyperpriors held by participants that taking advice is risky for various reasons.

We saw in the previous section that people are sensitive to the quality of advice and advisors, and will curate their information environments based on that sensitivity.
We have seen in this section how the properties of the information environment can change people's sensitivity to advice.

There is one major feature of advice-taking that has received relatively little investigation, yet that would, if real, be entirely inexplicable in terms of evolutionarily optimal hyperpriors.
This is the finding that people tend to consider all advisory estimates they receive as a single, multifaceted opinion, which is then integrated with their own individual opinion§\@ref(context-number).
Crucially, this seems to happen no matter how many advisory estimates are supplied [@hutterSeekingAdviceSampling2016; @yonahTheyDonKnow2021].
A rational approach to egocentric discounting might attempt, as we have above, to explain how it is sensible to afford less weight to another's opinion compared to one's own, but it cannot explain how it is sensible to afford the same weight to one's opinion whether integrating it with the opinions of one advisor or of several advisors.
