---
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
    keep_tex: false
  bookdown::word_document2: default
  bookdown::html_document2: default
documentclass: book
editor_options: 
  chunk_output_type: inline
  
bibliography: 
  - bibliography/references.bib
bibliography-heading-in-pdf: Works Cited
params:
  corrections: true 
---

```{r setup 01-05, echo = F, include = F}
```

```{r functions from model chapter}
```

# Constructing advice-taking models {#chapter-models-parameter-recovery}
\adjustmtc 

## Overview

We are attempting to ascertain whether our model of participant behaviour is robust enough to recover meaningful values from participants and use those to generate new information. 
To do this, we are using parameter recovery of simulated data. 
This means we use the model itself to generate data according to parameters we specify, and then apply our model-fitting processes to that data. 
If the fitting process works effectively we should see that the parameters the model-fitting processes suggests are the 'best' parameters are very close to the parameters we used to create the data.

## Simple test case

```{r demo case}
```

To demonstrate the components and visualisations, we'll use a simple example.
In this case, it's `demo$n` trials with the trustUpdateRate set to `demo$tu` and the weightedSelection set to `demo$ws`.
Remember that our model generates new trust values by using **trustUpdateRate** to weight the average of the current trust value and 1 (for agree trials) or 0 (for disagree trials).
**weightedSelection** is used to govern the steepness of the sigmoid curve giving the pick probability of each advisor based on the current trust values. 
In our model, trust is updated _after_ advisor choice but _before_ influence.

For simplicity's sake, at this stage, our confidence measure is unconstrained, so we don't have to worry about issues to do with the asymmetrical second decision confidence scale.

### Visualisation

We can see a plot of our example data and trace the model's behaviour. 

```{r demo run plot}
```

The two lines show the model's trust in each advisor at each trial. 
The arrow markers show whether the advisor agreed or disagreed on the trial.
Only one advisor gives advice on each trial.
After agreement, the trust in that advisor increases, and after disagreement it decreases.
The wider the gap between advisors on a trial, the more likely the more trusted advisor will be to be selected.
The column plot at the bottom shows the influence of the advice on the trial.
The magnitude of this column is proportional to the current trust in the advisor giving advice.

### Model fitting

We perform model fitting using two different approaches: gradient descent and grid search.

#### Gradient descent

The gradient descent algorithm takes a random starting point, and steps towards lower error in each dimension. 
When it cannot lower the error, it reduces its step size and tries again.
When the step size meets a minimum, or it stalls, it stops.

A single run of the gradient descent can be visualised as a path over a 2d surface defined by the parameters we are trying to recover.

```{r demo gradient descent path}
```

The gradient descent algorithm gets stuck in local minima quite easily, so we initialise it in a range of starting positions to increase the chances that one of the local minima it finds is the global minimum.

When we plot the end positions of all these descents we get a plot that looks like this:

```{r demo gradient descent summary}
```

The points show endpoints of individual runs, coloured according to the combined error.
The open black circle is the best run value, while the red star shows the target.
It looks surprisingly close, although this is partly an artefact of scale caused by the massively negative weightedSelection values identified by some runs.
The cause of this slow slope downwards when weightedSelection values get highly negative is not yet known.

#### Grid search

The second approach to parameter estimation is grid search. 
A grid search simply divides up the plane defined by the two parameters using a grid, and at each of the intersections calculates the model fit for the parameters at that intersection.

The error for the grid search has been been scaled so that the two dimensions' errors are equivalent, and the log taken to maximise discrimination at the lower error areas (where discrimination is most important).

```{r demo grid search}
```

The region with the best values does not include the target value.
This is largely a function of the number of trials we chose, which was low (to make for easy visualisation). 
Using a higher number of trials makes the weightedSelection estimation better.
The estimation of the trustUpdateRate is exact when considering that dimension alone (vertical dashed line).

## Test case with more trials

```{r long demo case}
```

Below are the same figures for the same coefficients, but with `demo$n` trials.

```{r long demo plots}
```

#### Outstanding puzzles

* Why do gradient descent and grid search show different minima?
  * Maybe different fitness function (simple addition vs scaledError)?
    * How could that be, given gradient descent never combines values?
* Why do neither identify the correct parameters?
  * Both do well for trustUpdateRate, not so much for weightedSelection

### Define simple model data

```{r simple model data}
```

```{r simple model grid search}
```

## Parameter recovery

We generate data from the model itself, then see if we can recover the parameters we used to generate that data.
For this we use a realistic number of trials, around 30.

```{r parameter recovery setup}
```

```{r visualise simulants data}
```

```{r visualise simulant grid example}
```

```{r parameter recovery demo}
```

```{r parameter recovery demo evaluation}
```

## Parameter recovery systematic investigation

We set up a grid to investigate parameter recovery systematically.

```{r simulant grid}
```

```{r visualise simulant grid}
```

```{r parameter recovery sim demo}
```

## Noisy simulations

We systematically vary noise to explore how it affect parameter recovery.

```{r simulant noise}
```

```{r visualise simulant noise grid}
```

```{r noise parameter recovery demo}
```


## Fixed trustUpdateRate

The weighted selection is our primary variable of interest. 
It is possible (reading from the model fitting results to participant data) that we are estimating a population parameter rather than discovering individual differences. 
To minimise the variability in weighted selection which is accounted for by measurement error rather than genuine inter-individual variation, we can fix the estimate of trust update rate (upon which weighted selection depends). 

In the simulations below, we explore the accuracy of weighted selection parameter recovery when trust update rate is fixed across all simulants. 

```{r fixed TUR}
```

