
## Effects of confidence-contingent advice {#ac-cca}

The results of the experiments described previously (1A§\@ref(ac-acc-dots), 1B§\@ref(ac-acc-dates), 2A§\@ref(ac-agr-dots), 2B§\@ref(ac-agr-dates), 3A§\@ref(ac-ava-dots), 3B§\@ref(ac-ava-dates)) were mixed, but indicated overall [and in combination with @pescetelliRoleDecisionConfidence2021] that people prefer accurate over inaccuate advisors when they can assess the advisors based on feedback, but prefer agreeing over disagreeing advisors when feedback is absent. 
Here we test whether advice selection can depend on a more sophisticated mechanism when feedback is absent.

This mechanism, proposed by @pescetelliRoleDecisionConfidence2021, weights the updating of trust in an agreeing advisor using the confidence of the judge's initial estimate.
Where the initial estimate is made with high confidence, agreement is taken to indicate that the advisor has a high probability of being correct, while disagreement is taken to indicate that the advisor has a low probability of being correct.
Where the initial estimate is low confidence, however, neither agreement nor disagreement is a good indicator of correctness. 
This intuition accords neatly with a Bayesian approach: the greater the uncertainty around whether or not the advice is correct, the lower the strength of the updating of trust in the advisor.

This mechanism can be directly tested by using advisors who have different agreement rates contingent upon the judge's confidence in their initial estimate, and @pescetelliRoleDecisionConfidence2021 used just such an approach to provided evidence for the mechanism in the domain of advisor influence.
Here, a very similar design is used to explore this effect in the domain of advisor choice.

Unlike the previous experiments, in which the same approach was implemented in both the Dots and the Dates tasks, this experiment uses only the Dots task. 
To balance the advisors' accuracy and agreement rates (such that only their _confidence-contingent agreement_ is varied), precise control is required over the participants' initial estimate accuracy. 
Such control is achieved using a staircasing procedure in the Dots task, and cannot be done in the Dates task (because there are too few questions to choose from, the questions have too wide a range of difficulty, and a question's difficulty varies dramatically and unpredictably between participants).

Instead of a Dots and a Dates task, this experiment is repeated in two versions of the Dots task.
The first version, directly adapted from @pescetelliRoleDecisionConfidence2021, was performed in the lab with a correspondingly low sample size and high number of trials per participant. 
The second version was a replication run online and with a larger sample size and lower number of trials per participant.
For ease of reference, the lab study is referred to as 'Lab study', while the online study retains the numbering and lettering used previously, meaning it is designated Experiment 4A.
There is no Experiment 4B, because it was not possible to use the Dates task with this design of advisors.^[The lab version of this study was the first one performed in chronological order. The results were not as anticipated, so a replication was run online (Experiment 4A). These results were also odd, so other experiments were run to investigate the stability of the basic effects (Experiments 1A, 2A, and 3A).] 

### Lab study of confidence-contingent advice {#ac-cca-lab}

@pescetelliRoleDecisionConfidence2021 used a judge-advisor system to demonstrate that judges are influenced to a greater extent by advisers who share their biases.
Participants played the role of judge in a judge-advisor system, while the advisers were virtual agents whose advice-giving was dependent upon the confidence and correctness of the judges' initial estimates.
The advisers were balanced for both overall agreement with the judge and objective correctness of advice.
This was achieved by varying the agreement rates for the advisors contingent on the confidence of the judge's initial estimate. 
The Bias-sharing advisor would agree more frequently when the participant expressed high confidence in their initial estimate and less frequently when the participant expressed low confidence in their initial estimate.
The Anti-bias advisor did the opposite.
Crucially, the advisors were matched in agreement when participants were moderately confident in their initial estimates, allowing the advisors to be compared directly on these trials [@pescetelliRoleDecisionConfidence2021].
We place participants in a similar paradigm in which they are given a choice between advisers, and hypothesise that they will more frequently seek advice from the _Bias Sharing_ advisor than from the _Anti Bias_ advisor.
We predict that, given a choice, judges will prefer to receive advice from a _Bias Sharing_ advisor over receiving advice from an advisor who does not share the judge’s bias.

#### Open scholarship practices

This experiment was preregistered at https://aspredicted.org/ze3tn.pdf.
One analysis in the preregistration is not reported here because the results are non-significant and they represented a branch of analysis that we sidelined in other experiments. 
This analysis explored participants' subjective assessments of advisors.
The experiment data are available in the `esmData::` package for R from \mccorrect{!TODO[Zenodo esmData]}, and also directly from https://osf.io/vgcnb/.
The code for running the experiment can be obtained from https://github.com/mjaquiery/nofeedback_trust.

#### Method {#ac-cca-lab-m}

```{r ac-ex1-load, include = F}
```

```{r ac-ex1-exclusions}
```

The method for the lab study was different in many small ways from the general method used for the Dots task online.
The basic trial experience was the same: participants saw two boxes of dots flashed breifly on the screen, and were asked to indicate which box had more dots, along with how confident they were in this initial estimate. 
Participants then received advice and provided a final decision.
On some trials participants were able to choose which of their advisors would provide the advice (Figure \@ref(fig:ac-ex1-paradigm)).

```{r ac-ex1-paradigm, fig.align='center', fig.caption="Experiment 1 procedure.  The task began with a blank screen containing only a fixation cross and progress bar. Momentarily prior to the onset of the stimuli the fixation cross flickered. The stimuli, two rectangles containing approximately 200 dots each, appeared for 0.16s, one on either side of the fixation cross. Once the stimuli disappeared, a response-collection screen appeared and prompted the participant to indicate their initial estimate and its confidence by selecting a point within one of two regions. Next, the participant was presented with a choice screen. The choice screen displayed two images, one at the top of the screen and one at the bottom. The images were one of the following: an advisor portrait, a silhouette, or a red cross. The red cross was not selectable, forcing participants to choose the other option. The silhouette offered no advice, and was only ever offered as a forced choice. Selecting an advisor image provided the participant with the opinion of that advisor on the trial.  Having heard the advice, the participant was again presented with the response-collection screen, with a yellow indicator marking their original response. A second (final) judgement was collected using this screen (except on catch trials), and the trial concluded.", out.width="100%"}
```

Overall, `r nrow(exclusions) + 1` participants were recruited from the University of Oxford participant recruitment platforms took part in the experiment and attended experimental sessions.
`r nrow(exclusions) - nrow(participants)` participant was excluded because the preregistered sample size had already been met when their data were collected, and one participant's data was lost due to technical issues.
The remaining participants had an average age of `r num2str(mean(participants$age))` (±SD `r num2str(sd(participants$age), 1)`).
Their self-identified genders were give as `r sum(tolower(participants$gender) == 'm')` male, `r sum(tolower(participants$gender) == 'f')` female, `r sum(tolower(participants$gender) != 'm' & tolower(participants$gender) != 'f')` other.
Participants were compensated for their time with either course credit for a psychology degree, or 10GBP.

Each participant completed 363 trials (51 practice trials over 2 blocks + 12 x 26-trial experimental blocks).
Prior to the first experimental block, after the final experimental block, and after the 4th and 8th experimental blocks, participants were presented with a questionnaire (Figure \@ref(fig:ac-ex1-questionnaire)).
The questionnaire contained 4 questions for each advisor.
The questions asked for the judge’s assessment of the advisor’s likeability, trustworthiness, influence, and ability to do the task.
The questions presented before the first experimental block were worded prospectively (e.g.
‘How much are you going to like this person?’ as opposed to ‘How much do you like this person?’).
Answers were provided by moving a sliding scale below the advisor’s portrait towards the right for more favourable responses (marked ‘extremely’) or towards the left for less favourable responses (marked ‘not at all’).

The blocks contained a mixture of choice, forced, and catch trials.
On choice trials, participants had a choice between the two advisors giving advice on that block, and were able to select whichever they preferred by clicking the advisor's portrait. 
The relative frequency of selection on these trials provided our dependent variable of advisor choice.
On forced trials, participants were faced with the advisor selection screen, but only one option was available. 
Participants could only continue when they selected the available portrait. 
These trials were included to allow measuring of the influence of advice without the confound of having just chosen the advisor over another advisor.
Catch trials were included to encourage participants to respond accurately in their initial estimates: on these trials they were forced to select a blank advisor portrait and received no advice; their initial estimate became their final decision automatically.

```{r ac-ex1-questionnaire, fig.align='center', fig.caption="Experiment 1 advisor questionnaire.  Participants rated advisors on a number of different dimensions.", out.width="100%"}
```

Each participant attended the experiment individually, was welcomed and briefed on the experimental procedure, and had their informed consent recorded, before the experiment began.
They were seated a comfortable distance in front of a 24’ (1440x900 resolution) computer screen in a small, quiet, and dimly-lit room.
The experiment took place wholly on the computer, and lasted around 45 minutes.

The experiment was programmed in MATLAB R2017b [@MATLAB2017] using the Psychtoolbox-3 package [@kleiner2007s].

##### Key differences from online version

There were several differences from the online version of the task that are worth mentioning.
First, there were more trials and the experiment took longer to complete.
Second, when the participant was forced to have advice from one or other advisor, they were presented with the advisor choice screen and one of the options was a blank advisor that they were unable to select.
This meant that advisor influence on the forced trials could be analysed as compared to choice trials.
Third, 8% of trials were catch trials on which no advice was offered.
Fourth, the questionnaires were more detailed and more numerous, and contained no free text fields.
Fifth, participants had the opportunity to discuss the experiment with the experimenter after the experiment was complete, although none made use of this opportunity.

##### Advice profiles {#ex1-m-profiles}

The two advisor profiles used in the experiment were Bias sharing and Anti-bias.
The advisors are balanced for their overall accuracy and agreement rates, but the Bias sharing advisor agrees more frequently with participants when their initial estimate is correct and made with relatively high confidence.
The Anti-bias advisor agrees more frequently with participants when their initial estimate is correct and made with relatively low confidence (Table \@ref(tab:ac-ex1-advisor-profiles)).
Note that the overall correctness and agreement rates of the advisers are equivalent.
Importantly, on a large minority of trials, the middle 40%, the advisers are exactly equivalent, meaning these trials can be compared directly without confounds arising from agreement rates and initial confidence.

```{r ac-ex1-advisor-profiles-r}
```

#### Results {#ac-ex1-r}

##### Exclusions

Participants could be excluded for having initial estimate accuracy below 60% or above 90%, or for performing the experiment after the stated sample size had been reached. 
No participants were excluded for having accuracy out of range. 
`r nrow(exclusions) - nrow(participants)` participant was excluded for being extraneous.

##### Advisor performance

```{r ac-ex1-r-advice}
```

The advisors agreed with the participants' initial estimates at close to target rates in all confidence categories, and were as accurate on average as expected (Table \@ref(tab:ac-ex1-r-advice-t)).

##### \OpenScience{prereg} Advisor selection

```{r ac-ex1-r-h}
```

We hypothesised that the participants would display different pick rates for the Bias Sharing advisor versus the Anti Bias advisor.
This hypothesis was evaluated by calculating the proportion of choice trials on which each participant picked the Bias Sharing advisor, and then testing these values as a one-sample t-test against the null hypothesis that the pick rates would be 0.5.
No support was found for this hypothesis (`r .T`; Figure \@ref(fig:ac-ex1-r-selection)), although the Bayesian test indicated that the data were not sufficient to conclude that no effect was present.
There was considerable variability across participants in the overall pick rate for the Bias Sharing advisor (range = [`r range(bs_pick$pPickBS) %>% num2str(isProportion = T) %>% paste(collapse = ", ")`]).

Unlike in other experiments, there was no systematic effect of the position of the advisors on the screen (`r .T.first`).
This placement is random, and has no relationship to the identity of the advisor (`r .T.pos`), so we expect that it would be random across participants.

```{r ac-ex1-r-selection, fig.align='center', fig.caption="Advisor selection.  Proportion of the time each participant picked the Bias Sharing advisor. Faint lines and dots indicate data from individual participants, while the large dot indicates the mean proportion across all participants. The dashed reference line indicates picking both advisors equally, as would be expected by chance. Error bars give 95\\% confidence intervals.", out.width="100%"}
```

###### \OpenScience{prereg} Advisor selection on medium-confidence trials

The advisers differed in their advice-giving as a function of the judge’s initial confidence.
In trials where the judge’s initial estimate was made with medium confidence, however, the advisers were equal on judge confidence and agreement rate.
Comparing selection rates for these trials alone revealed a clear preference for the Bias Sharing advisor (`r .T.med`; Figure \@ref(fig:ac-ex1-r-selection) "Medium" confidence category), although the Bayesian analysis again indicated an insensitive result, albeit in the hypothesised direction.

##### \OpenScience{prereg} Advisor influence {#ex1-influence}

```{r ac-ex1-r-influence-aov}
```

Previous work in our lab demonstrated that the agree-in-confidence advisor exerted greater influence on the judges’ final decisions than the agree-in-uncertainty advisor [@pescetelliRoleDecisionConfidence2021].
Influence was examined with a 2x2x2 (Bias-sharing versus Anti-bias advisor; choice versus forced trials; agreement versus disagreement trials) ANOVA (Figure \@ref(fig:ac-ex1-influence-r)).
This was chronologically the first experiment we ran, and the analysis was preregistered prior to the development of the capped influence measure designed to allow agreement and disagreement to be compared more fairly.
No main effect was found for advisor (`r aov_inf$s[1]`, `r mmAdvisor %>% filter(Advisor == "Bias-sharing") %>% pull(s)`, `r mmAdvisor %>% filter(Advisor == "Anti-bias") %>% pull(s)`), meaning that the previous finding was not replicated.
As shown in Table \@ref(tab:ac-ex1-influence-t), the only statistically significant effect was the main effect of agreement, with disagreement producing higher influence than agreement (`r aov_inf$s[4]`, `r mmAgree %>% filter(agree == "Agree") %>% pull(s)`, `r mmAgree %>% filter(agree == "Disagree") %>% pull(s)`).

When this analysis was repeated with the capped influence values (General Method - Capped influence§\@ref(m-analysis-dv-influence)) the effect of agreement was still significant, but less so (`r aov_inf_cap$s[1]`, `r mmAdvisor %>% filter(Advisor == "Bias-sharing") %>% pull(sCapped)`, `r mmAdvisor %>% filter(Advisor == "Anti-bias") %>% pull(sCapped)`), and a main effect of trial type also emerged (raw influence: `r aov_inf$s[2]`, `r mmTrialType %>% filter(trialType == "Choice") %>% pull(s)`, `r mmTrialType %>% filter(trialType == "Force") %>% pull(s)`; capped influence: `r aov_inf_cap$s[2]`, `r mmTrialType %>% filter(trialType == "Choice") %>% pull(sCapped)`, `r mmTrialType %>% filter(trialType == "Force") %>% pull(sCapped)`).

```{r ac-ex1-influence-r, fig.align='center', fig.caption="Advisor influence.  Influence of advice from each advisor by advisor, agreement, and trial type. Faint lines and indicate data from individual participants, while the dots indicate the mean proportion across all participants. Error bars give 95\\% confidence intervals.  Note: vertical axis is truncated to show group differences more clearly, the theoretical maximum influence given the scale is 110. The minimum is 0 as shown.", out.width="100%"}
```

###### \OpenScience{prereg} Advisor influence on medium confidence trials

```{r ac-ex1-r-influence-med}
```

The agree-in-confidence and agree-in-uncertainty advisers differed by design in the frequency with which they agree with the participant as a function of the participant’s confidence in their initial estimate.
To control for the effects of initial confidence on influence, the above analysis was repeated using only those trials on which the initial estimate was correct and given with medium confidence.
In a deviation from preregistration, this analysis was constrained to only forced trials because some participants had missing data for some advisor-trial type-agreement contingencies in the Medium confidence trials.

The results were qualitatively identical to those for the trials at all confidence levels: a main effect of agreement (raw influence: `r s_inf_m$s[2]`; capped influence: `r s_inf_cap_m$s[2]`); and no significant effect of advisor (raw influence: `r s_inf_m$s[1]`; capped influence: `r s_inf_cap_m$s[1]`) or interaction (raw influence: `r s_inf_m$s[3]`; capped influence: `r s_inf_cap_m$s[3]`).

##### \OpenScience{prereg} Sensitivity to the manipulation

```{r ac-ex1-r-sensitivity}
```

Finally, we planned to investigate the hypothesis that participants’ choice of advisor would be sensitive to the differential agreement strategies of the advisers, e.g. participants might preferentially select the advisor with the greater likelihood of agreement given their initial confidence.
This was investigated by testing the participants’ mean Bias-sharing advisor pick rate in high- versus low-confidence trials.
Pick rates did not differ (`r .T.byConf`).

##### Follow-up tests

```{r ex1-follow-up}
```

Given the weak effects of advisor profile differences on advisor choice, we ran two follow-up analyses on pick rates. 
A first analysis showed that the participants' experiences of advisor agreement in the first block was correlated with the pick rate in later blocks.
This suggested that initial exposure to the advisers may have overshadowed information in subsequent blocks.
A second analysis showed that participants' answers on the questionnaire measure correlated with their pick preference strength for the questions on asking about how accurate (`r eqs %>% filter(Dimension == "Accurate") %>% pull(s)`), and trustworthy (`r eqs %>% filter(Dimension == "Trustworthy") %>% pull(s)`) advisors were.
The higher a participant rated one advisor as compared to the other on the questionnaire scale, the heavier that participant's preference tended to be for picking the higher rated advisor.
The same was not true for the questions asking how likeable (`r eqs %>% filter(Dimension == "Likeable") %>% pull(s)`) and influential (`r eqs %>% filter(Dimension == "Influential") %>% pull(s)`) advisors were.

#### Discussion

The lab experiment, chronologically the first of all the experiments,^[Later experiments were conducted to investigate why the hypothesised effects were not found in this experiment.] produced equivocal results. 
While many of the expected relationships were found between participants' subjective perceptions of the advisors and their behaviour towards them, these did not reliably translate into differential picking rates for the Bias-sharing and Anti-bias advisors.
There was a significant difference in pick rates in medium confidence trials (where the advisors were equivalent to one another), but the Bayesian test indicated that the evidence in favour of differential pick rates was weak.
Furthermore, there was no convincing reason we could determine why the preference (if it were a real effect) would not show up at other confidence levels.
The early experience of advisors did appear to predict their relative pick rates, with the advisor who agreed more with the participant in the initial experimental block being more likely to be picked more frequently on subsequent blocks.

Overall, these results were underwhelming and difficult to interpret.
We conducted an online replication of this study so that we could collect data from more participants and hopefully determine more accurately whether or not participants were sensitive to the differences in the advisors.

### Experiment 4A: Confidence-contingent advice effects in the Dots Task {#ac-cca-dots}

The results of the previous studies indicated that people update their preferences for advisors using agreement in place of feedback where objective feedback is unavailable. 
Previous results from our lab [@pescetelliRoleDecisionConfidence2021] suggested that this capacity is heuristic is modified by confidence.
The results of the previous experiment, however, failed to demonstrate these effects with advisor selection as the outcome.

The previous experiment was tightly controlled but the sample size was small.
Using insights from its data, we refined the design and recruited a larger number of participants for the replication.
Refinements included shortening the experiment, making the advisor profiles more extreme, reducing the questionnaires, and changing advisor representations from real faces and names to colours and numbers.

```{r ac-cca-dots-load, include = F}
```

#### Open scholarship practices


This experiment was preregistered at `r unique(dotstask$preregistration)`.
The experiment data are available in the `esmData::` package for R from \mccorrect{!TODO[Zenodo esmData]}, and also directly from https://osf.io/xb4kh/.
A snapshot of the state of the code for running the experiment at the time the experiment was run can be obtained from https://github.com/oxacclab/ExploringSocialMetacognition/blob/90c04ff21d3a2876beaddd9ee35c577a821e5727/AdvisorChoice/index.html.

#### Method {#ac-cca-dots-m}

```{r ac-cca-dots-m-structure}
```

`r length(unique(trials$pid))` participants each completed `r sum(tmp$n)` trials over `r nrow(tmp)` blocks of the Dots task.
Participants started with `r sum(tmp$typeName == "catch")` blocks of `r tmp %>% filter(typeName == "catch") %>% mutate(n = n - (n %% 4)) %>% .$n %>% unique()` trials that contained no advice.
The first three trials were introductory trials that explained the task.
All trials in this section included feedback indicating whether or not the participant's response was correct.

Participants then did `r tmp %>% filter(typeName == "force" & practice) %>% .$n %>% sum()` trials with a practice advisor.
They were informed that they would "get **advice** from an advisor to help you make your decision [original emphasis]", and that "advice is not always correct, but it is there to help you: if you use the advice you will perform better on the task."

```{r ac-cca-dots-m-structure-main}
```

Participants then performed `r sum(tmp$typeName == "choice")` sets of `r nrow(tmp) / sum(tmp$typeName == "choice")` blocks each.
These sets consisted of `r sum(tmp$typeName == "force") / sum(tmp$typeName == "choice")` familiarisation block of `r tmp %>% filter(typeName == "force") %>% .$n %>% unique()` trials in which participants were assigned one of two advisors on each trial.
The familiarisation block was followed with a test block of `r tmp %>% filter(typeName == "choice") %>% .$n %>% unique()` trials in which participants could choose between the two advisors they encountered throughout the familiarisation block.
The participants saw different pairs of advisors in each set, with each pair consisting of one advisor with each of the advice profiles.

Compared to the lab version of this experiment§\@ref(ac-cca-lab-m), the design was somewhat simplified.
The forced and choice trials were grouped into discrete blocks, so participants had all the forced trials for a pair of advisors first, and then all the choice trials for those advisors.
Secondly, the advisors' biases were more extreme, as shown in Table \@ref(tab:ac-cca-dots-profiles).

##### Advice profiles

The two advisor profiles used in the experiment were Bias sharing and Anti-bias.
The advisors are balanced for their overall accuracy and agreement rates, but the Bias sharing advisor agrees more frequently with participants when their initial estimate is correct and made with relatively high confidence.
The Anti-bias advisor agrees more frequently with participants when their initial estimate is correct and made with relatively low confidence (Table \@ref(tab:ac-cca-dots-profiles)).

```{r ac-cca-dots-profiles-r}
```

#### Results {#ac-cca-dots-r}

##### Exclusions

```{r ac-cca-dots-r-clean}
```

In line with the pre-registration, participants' data were excluded from analysis where they had an average accuracy below `r accuracyRange[1]` or above `r accuracyRange[2]`, did not have choice trials in all confidence categories (bottom 30%, middle 40%, and top 30% of prior confidence responses), had fewer than `r minTrialsPerCategory` trials in each confidence category, or finished the experiment after `r preRegParticipants` participants had already submitted data which passed the other exclusion tests. 
Overall, `r sum(pull(exclusions, "Total excluded"))` participants were excluded, with the details shown in Table \@ref(tab:ac-cca-dots-exclusions).

##### Task performance

```{r ac-cca-dots-r-performance-acc, fig.caption="Response accuracy for the Dots task with confidence-contingent advisors.  Faint lines show individual participant means, for which the violin and box plots show the distributions. The half-width horizontal dashed lines show the level of accuracy which the staircasing procedure targeted, while the full width dashed line indicates chance performance. Dotted violin outlines show the distribution of actual advisor accuracy."}
```

```{r ac-cca-dots-r-performance-conf, fig.caption="Confidence for the Dots task with confidence-contingent advisors.  Faint lines show individual participant means, for which the violin and box plots show the distributions. Final confidence is negative where the answer side changes. Theoretical range of confidence scores is initial: [0,1]; final: [-1,1]."}
```

```{r ac-cca-dots-r-performance-aov}
```

Basic behavioural performance was similar to that observed with the same Dots task in Experiments 1A§\@ref(ac-acc-dots-r-performance) and 2A§\@ref(ac-agr-dots-r-performance). 
Initial estimate accuracy converged on the target 71%, and, as shown in Figure \@ref(fig:ac-cca-dots-r-performance-acc), participants benefited from advice in terms of their final decisions being more accurate than their initial estimates (ANOVA main effect of Time: `r s_acc$s[2]`), predominantly driven by following advice from the Anti-bias advisor (interaction of Time and Advisor: `r s_acc$s[3]`).
There was no main effect of Advisor (`r s_acc$s[1]`).

Figure \@ref(fig:ac-cca-dots-r-performance-conf) and ANOVA indicated that participants were more confident in their answers when they were correct compared to incorrect (`r s_conf$s[2]`), that participants were less confident in their final decisions than their initial estimates (`r s_conf$s[1]`), and that this decrease was larger for trials where the initial estimate was incorrect (`r s_conf$s[3]`).

##### Advisor performance

The advice is generated probabilistically from the rules described previously in Table \@ref(tab:ac-cca-dots-profiles).
It is thus important to get a sense of the actual advice experienced by the participants.

```{r ac-cca-r-advice}
```

Table \@ref(tab:ac-cca-r-advice-t) shows that advisors agreed with the participants' initial estimates at close to target rates in all confidence categories. 
There was a larger than expected difference in agreement on correct answers overall, but this was not a significant difference (`r .T.agr`).
The advisors were also further apart in terms of overall accuracy than desired, because of the different agreement rates for correct answers, although once again this difference was not significant (`r .T.acc`).

##### \OpenScience{prereg} Hypothesis test {#ac-cca-dots-r-h}

```{r ac-cca-dots-r-graph, fig.caption="Dot task advisor choice for confidence-contingent advisors.  Participants' pick rate for the advisors in the Choice phase of the experiment. The violin area shows a density plot of the individual participants' pick rates, shown by dots. The chance pick rate is shown by a dashed line.", fig.height=6, fig.width=4}
```

There was a strong tendency for participants to express no, or slight preferences between advisors (`r .T`).
Intriguingly, almost all participants who expressed a stronger preference expressed it towards the Anti-bias advisor: in the direction counter to that hypothesised (Figure \@ref(fig:ac-cca-dots-r-graph)).  

In the Medium confidence trials, where the Lab experiment showed a glimmer of a difference, there was evidence against the existence of a difference (`r .T_med`).

In this experiment we saw an extremely strong effect of picking the advisor in the first position on the screen (`r .T.first`), an effect that we would hope would be random and even out across participants. 
In this experiment, as a function of chance, the Bias-sharing advisor appeared in the favoured top position more frequently than we would expect (`r .T.pos`).
The effect of preferring to pick the advisor in the first position, therefore, would enhance the pick rate of the Bias-sharing advisor.
Despite this, we saw that the advisors were picked at equivalent rates, allowing us to be even more sure that there is no overall preference for the Bias-sharing advisor driven by that advisor's method of providing advice.

#### Discussion

While source selection and advice-taking are different domains, the previous experiments have shown strong similarities in the tendencies of participants: participants tend to be more influenced by the same kinds of advisors that they are more willing to hear from. 
On this basis, following @pescetelliRoleDecisionConfidence2021, we would expect to see a preference for picking the Bias sharing advisor. 
We do not see this preference, and, insofar as we see any preference at all, we see the opposite.

### Confidence-contingent advice effects in the Dates task

The Dates task was not used to study confidence-contingent advice because such advice requires both a precise control over the relative agreement and accuracy rates of the advisors and the ability to estimate confidence in responses. 
The advisors' agreement (and hence accuracy) profiles depend on the participant's performance, and this is unknown a priori in the Dates task whereas it is controlled in the Dots task using a staircase procedure.
Different approaches to estimating participants' confidence were trialled, including a pilot experiment in which the width of marker used by participants was used as a proxy for confidence, but none of the approaches produced any discernible effect of confidence on advisor agreement. 

We did attempt to design a version of the Dates task that would allow confidence-contingent advice, but pilot studies were largely unsuccessful and the time, cost, and effort required to refine the study were not deemed worthwhile in light of the null results from the Dots task studies.

### Discussion {#ac-cca-d}

Across two tasks investigating whether people preferentially selected advisors who shared their biases we found scant evidence in favour of the effect.
The two advisors, balanced for overall agreement and accuracy to eliminate the effects seen in previous experiments, differed in their likelihood of agreement based on the participants' initial estimate accuracy [following @pescetelliRoleDecisionConfidence2021]. 
The Bias-sharing advisor agreed more frequently with a participant when the initial estimate was made with high confidence, and less frequently when the initial estimate was made with low confidence, and the Anti-bias did the opposite. 
Overall, there was no evidence that participants picked these advisors at different rates.
Looking just at the medium confidence trials, where the advisors were exactly equivalent, there was very weak evidence that the Bias-sharing advisor was picked more frequently in the Lab experiment and reasonable evidence against any difference at all in the online replication.

The data from these studies were not conclusive against the existence of this effect, especially when integrated with the findings of @pescetelliRoleDecisionConfidence2021. 
It is plausible, for instance, that metacognitive moderation does happen in advice evaluation, but that these effects are more subtle than the broader effects of accuracy and agreement, and that the studies here were too underpowered to detect these effects.
It seems unlikely that metacognitive moderation effects would exist in the advisor evaluation domain (as shown in @pescetelliRoleDecisionConfidence2021) but not in the advisor choice domain, given the rough parity demonstrated between these domains across the dimensions of accuracy and agreement in previous experiments.

