
## Effects of Advisor Agreement on Advisor Selection {#ac-agr}

The next pair of experiments investigated how advice preferences are shaped by advisors’ likelihood of giving advice that agrees vs. disagrees with participants’ own initial estimates. 
Pescetelli and Yeung \mccorrect{NICK: Niccolo Exp 2 in the JEP:G paper. He found (in terms of influence) a big effect of agreement and a much smaller effect of accuracy when there was no feedback. When feedback was provided, accuracy had maybe a bit bigger effect than agreement, but both effects were clear.} demonstrated that advisors who agree \mccorrect{NICK: somewhere we need to talk about what we mean by agreement, how Niccolo defined it, how we define it (varies between binary/continuous tasks), etc. Remind the reader what we mean by agreement in Method} more frequently are more influential (regardless of the presence of feedback) in a lab-based perceptual decision-making task.}
\mccorrect{NICK: Here we explored the impact of agreement on participants’ choice of advisor. Experiment X looks at this effect in the Dots task, while Experiment Y does the same for the Dates task.}

Experiments 1A§\@ref(ac-acc-dots) and 1B§\@ref(ac-acc-dates) revealed differences in how participants selected the advisors between the Dots task (which has no feedback) and the No feedback condition of the Dates task for High versus Low accuracy advisors. 
We may expect more pronounced effects in the absence of feedback when contrasting High versus Low agreement advisors, because we expect that agreement is the driving force behind the accuracy differences where feedback is not provided.

### Experiment 2A: Advisor agreement effects in the Dots Task {#ac-agr-dots}

\mccorrect{NICK: In this experiment, the advice provided was no longer independent of participants’ own initial decisions. Instead, advice was provided contingent on those decisions, such that the two advisors varied in their likelihood…etc. I think it's worth making the point explicit, to begin to suggest how we can dissociate agreement and accuracy.}

```{r ac-agr-dots-load, include = F}

rm(list = ls()); source('scripts_and_filters/general_setup.R')

select_experiment(
  project = 'dotstask',
  function(x) filter(x, study == 'Agreement')
)

trials <- annotate_responses(trials)

```

#### Open scholarship practices

This experiment was preregistered at `r unique(dotstask$preregistration)`.
The experiment data are available in the `esmData::` package for R from \mccorrect{!TODO[Zenodo esmData]}, and also directly from https://osf.io/8cnpq/.
A snapshot of the state of the code for running the experiment at the time the experiment was run can be obtained from https://github.com/oxacclab/ExploringSocialMetacognition/blob/9932543c62b00bd96ef7ddb3439e6c2d5bdb99ce/AdvisorChoice/index.html.

#### Method {#ac-agr-dots-m}

```{r ac-agr-dots-m-structure}
tmp <- trials %>% 
  group_by(block, pid) %>% 
  summarise(
    n = n(), 
    typeName = paste(unique(typeName)), 
    practice = sum(practice),
    .groups = 'drop'
  ) %>% 
  select(-pid) %>% 
  unique()
```

`r length(unique(trials$pid))` participants each completed `r sum(tmp$n)` trials over `r nrow(tmp)` blocks of a perceptual decision-making task.
Each trial consisted of three phases: participants gave an initial estimate (with confidence) of which of two briefly presented boxes contained more dots; received advice on their decision from an advisor; and made a final decision (again, with confidence).

Participants started with `r sum(tmp$typeName == "catch")` blocks of `r tmp %>% filter(typeName == "catch") %>% mutate(n = n - (n %% 4)) %>% .$n %>% unique()` trials that contained no advice to allow them to familiarise themselves with the task; to allow the staircasing process to titrate the difficulty to their ability in order to maintain approximately 71% initial estimate accuracy; and to allow estimating of participants' idiosyncratic confidence reporting style.
The first three trials were introductory trials that explained the task.
All trials in this section included feedback indicating whether or not the participant's response was correct.

Participants then did `r tmp %>% filter(typeName == "force" & practice) %>% .$n %>% sum()` trials with a practice advisor to get used to receiving advice.
They were informed that they would "get **advice** from an advisor to help you make your decision", and that "advice is not always correct, but it is there to help you: if you use the advice you will perform better on the task."

```{r ac-agr-dots-m-structure-main}
tmp <- tmp %>% filter(!practice)
```

Participants then performed `r sum(tmp$typeName == "choice")` sets of `r nrow(tmp) / sum(tmp$typeName == "choice")` blocks each.
These sets consisted of `r sum(tmp$typeName == "force") / sum(tmp$typeName == "choice")` familiarisation block of `r tmp %>% filter(typeName == "force") %>% .$n %>% unique()` trials in which participants were assigned one of two advisors.
The familiarisation block was followed with a test block of `r tmp %>% filter(typeName == "choice") %>% .$n %>% unique()` trials in which participants could choose between the advisors they encountered in the familiarisation block.
The participants saw different pairs of advisors in each set, with each pair consisting of one advisor with each of the advice profiles.

##### Advice profiles

```{r ac-agr-dots-m-profiles-setup} 

pCor <- .71
agr <- matrix(c(.84, .61, .66, .17), 2, 2)

agr.table <- tribble(
  ~`Advisor`, ~`Participant correct`, ~`Participant incorrect`, ~`Overall`, ~`Overall accuracy`,
  "High agreement", agr[1, 1], agr[2, 1], sum(agr[,1] * c(pCor, 1 - pCor)), sum(agr[1,1] * pCor, (1 - agr[2,1]) * (1 - pCor)),
  "Low agreement", agr[1, 2], agr[2, 2], sum(agr[,2] * c(pCor, 1 - pCor)), sum(agr[1,2] * pCor, (1 - agr[2,2]) * (1 - pCor))
) %>% 
  prop2str()

tmp <- sapply(1:ncol(agr), function(i) sum(agr[, i] * c(pCor, 1 - pCor)))

```

\mccorrect{NICK: Maybe frame in terms of overall aims: Advisors were defined in terms of their likelihood of agreement with participants' correct vs. incorrect initial decisions, while being matched in terms of their objective accuracy. Then give the numbers. This gives a bit of context for numbers that otherwise seem a bit arbitrary.}

The two advisor profiles (Table \@ref(tab:ac-agr-dots-m-profiles)) used in the experiment were High agreement and Low agreement.
These advisors were defined in terms of their likelihood of agreement with participants' correct and incorrect initial estimates, while being matched for objective accuracy. 
The High agreement advisor gave advice that endorsed the same answer side as the participant's initial estimate `r round(tmp[1] * 100, 1)`% of the time while the Low agreement advisor agreed with the participant `r round(tmp[2] * 100, 1)`% of the time.
These overall agreement rates were split based on on the participants' initial estimate accuracy to achieve balanced overall accuracy rates between advisors.

```{r ac-agr-dots-m-profiles-r} 

kable(agr.table, caption = "\\label{tab:ac-agr-dots-m-profiles}Advisor advice profiles for Dots task Agreement experiment") %>%
  kable_styling() %>%
  column_spec(1, bold = T) %>%
  row_spec(0, bold = F) %>%
  collapse_rows(columns = 1, valign = "top") %>%
  add_header_above(c(" ", 
                     "Probability of agreement" = 3,
                     " "))

```

#### Results {#ac-agr-dots-r}

##### Exclusions

```{r ac-agr-dots-r-clean}
nMaxOutliers <- 2
zThresh <- 3
accuracyRange <- c(.6, .85)
minTrialsPerCategory <- 12
preRegParticipants <- 50

tmp <- trials %>% 
  nest(d = -pid) %>%
  mutate(d = map_dbl(d, ~ mean(.$initialAnswerCorrect)))

exclusions <- tibble(pid = unique(trials$pid)) %>%
  mutate(
    `Accuracy too low` = pid %in% filter(tmp, d < accuracyRange[1])$pid,
    `Accuracy too high` = pid %in% filter(tmp, d > accuracyRange[2])$pid
  )

tmp <- trials %>% 
  filter(!practice) %>%
  nest(d = c(-pid, -confidenceCategory)) %>%
  mutate(n = map_int(d, nrow)) %>%
  select(-d) %>%
  pivot_wider(names_from = confidenceCategory, 
              names_prefix = "cc", 
              values_from = n) %>%
  mutate(
    anyNA = is.na(cc0) | is.na(cc1) | is.na(cc2),
    lowest = pmin(cc0, cc1, cc2, na.rm = T)
  )

exclusions <- exclusions %>% 
  mutate(
    `Missing confidence categories` = pid %in% filter(tmp, anyNA)$pid,
    `Skewed confidence categories` = pid %in% filter(tmp, lowest < minTrialsPerCategory)$pid
  )
  
do_exclusions(exclusions)

tmp <- trials %>% nest(d = -pid) %>% rowid_to_column() %>% filter(rowid > preRegParticipants)

exclusions <- exclusions %>% mutate(`Too many participants` = pid %in% tmp$pid)

do_exclusions(exclusions, backup = F)


exclusions$`Total excluded` <- exclusions %>% select(-pid) %>% apply(1, any)
n <- ncol(exclusions)
exclusions %>% 
  summarise(across(where(is.logical), sum)) %>%
  mutate(`Total remaining` = length(unique(trials$pid))) %>% 
  pivot_longer(everything(), names_to = "Reason", values_to = "Participants excluded") %>%
  kable(caption = "\\label{tab:ac-agr-dots-exclusions}Participant exclusions for Dots task Agreement experiment") %>%
  row_spec((n - 1):n, bold = T)

familiarization <- trials %>%
  filter(typeName == "force", adviceType %in% c(7,8)) %>%
  mutate(Advisor = advisor_profile_name(adviceType),
         Advisor = factor(Advisor)) %>%
  order_factors()

```

In line with the pre-registration, participants' data were excluded from analysis where they have an average accuracy below `r accuracyRange[1]` or above `r accuracyRange[2]`, do not have choice trials in all confidence categories (bottom 30%, middle 40%, and top 30% of prior confidence responses), have fewer than `r minTrialsPerCategory` trials in each confidence category, or finish the experiment after `r preRegParticipants` participants have already submitted data which passed the other exclusion tests. 
Overall, `r sum(pull(exclusions, "Total excluded"))` participants were excluded, with the details shown in Table \@ref(tab:ac-agr-dots-exclusions).

##### Task performance

```{r ac-agr-dots-r-performance, fig.caption="Task performance for the Dots task with dis/agreeing advisors.  A: Response accuracy. Faint lines show individual participant means, for which the violin and box plots show the distributions. The half-width horizontal dashed lines show the level of accuracy which the staircasing procedure targeted, while the full width dashed line indicates chance performance. Dotted violin outlines show the distribution of actual advisor accuracy.  B: Confidence. Faint lines show individual participant means, for which the violin and box plots show the distributions.  C: Influence. Participants' weight on the advice for advisors in the Familiarization stage of the experiment. The shaded area and boxplots indicate the distribution of the individual participants' mean influence of advice. Individual means for each participant are shown with lines in the centre of the graph. The theoretical range for influence values is [-2, 2]."}

gg <- list()

# Task performance figure
dw <- .2

tmp <- familiarization %>%
  group_by(Advisor, pid) %>%
  summarise(
    `Initial estimate` = mean(initialAnswerCorrect),
    `Final decision` = mean(finalAnswerCorrect),
    .groups = 'drop'
  ) %>%
  pivot_longer(cols = c(`Initial estimate`, `Final decision`),
               names_to = 'Response', values_to = 'Accuracy') %>%
  mutate(Advisor = factor(paste0(Advisor, '\n')),
         Response = factor(str_replace(Response, " ", "\n")))

adv <- familiarization %>%
  group_by(Advisor, pid) %>%
  summarise(
    Response = 'Advice',
    Accuracy = mean(adviceCorrect),
    .groups = 'drop'
  ) %>%
  mutate(Advisor = factor(paste0(Advisor, '\n'))) %>%
  order_factors()

stair <- tribble(
  ~Response, ~Accuracy,
  'Initial estimate', .71
) %>%
  crossing(tibble(Advisor = unique(tmp$Advisor))) %>%
  filter(!is.na(Advisor))

# Should this be a paired t-test?
bf <- tmp %>%
  nest(d = -Advisor) %>%
  mutate(d = map(d, as.data.frame),
    bf = map(d, ~ ttestBF(x = .$Accuracy[.$Response == 'Initial\nestimate'],
                          y = .$Accuracy[.$Response == 'Final\ndecision'],
                          data = ., paired = T)),
         bf = map_chr(bf, ~ .@bayesFactor %>% .$bf %>% exp() %>% bf2str())) %>%
  select(-d)

gg$acc <- tmp %>%
  mutate(
    advisor = str_replace(Advisor, '\\n', ''),
    advisor = factor(advisor),
    Response = factor(str_replace(Response, " ", "\n"))
  ) %>%
  order_factors() %>%
  ggplot(aes(x = Response, y = Accuracy, colour = advisor)) +
  scale_y_continuous(limits = c(NA, 1), expand = c(0, 0)) +
  scale_x_discrete() +
  scale_colour_discrete(name = 'Advisor', aesthetics = c('fill', 'colour')) +
  coord_cartesian(clip = F) +
  geom_hline(yintercept = .5, linetype = 'dashed') +
  geom_segment(aes(y = Accuracy, yend = Accuracy, x = 0, xend = 1.5),
               linetype = 'dashed', colour = 'black', data = stair) +
  geom_line(aes(group = pid), alpha = .25) +
  geom_split_violin(aes(x = nudge(Response, dw),
                        group = Response, fill = advisor),
                    width = .9, colour = NA) +
  geom_split_violin(aes(x = 2 + dw),
                    group = 2, fill = NA, colour = 'black', linetype = 'dotted',
                    data = adv) +
  geom_boxplot(aes(x = nudge(Response, dw), group = Response),
               outlier.shape = NA, size = 1, width = dw/2, colour = 'black') +
  geom_segment(x = 1 - dw, xend = 2 + dw, y = 1, yend = 1, colour = 'black') +
  geom_label(x = 1.5, y = 1, aes(label = paste0('BF = ', bf)), colour = 'black',
             data = bf) +
  facet_wrap(~Advisor) +
  theme(legend.position = 'none') +
  labs(x = "") +
  broken_axis_bottom

tmp <- familiarization %>%
  mutate(`Initial estimate accuracy` =
           if_else(initialAnswerCorrect, 'Initial\ncorrect', 'Initial\nincorrect')) %>%
  group_by(`Initial estimate accuracy`, pid) %>%
  summarise(
    `Initial estimate` = mean(initialConfidenceScore),
    `Final decision` = mean(finalConfidenceScore),
    .groups = 'drop'
  ) %>%
  pivot_longer(cols = c(`Initial estimate`, `Final decision`),
               names_to = 'Response', values_to = 'Confidence') %>%
  mutate(response = factor(paste0(Response, '\n')),
         Response = factor(Response),
         `Initial estimate accuracy` = factor(`Initial estimate accuracy`))

bf <- tmp %>%
  nest(d = -response) %>%
  mutate(d = map(d, as.data.frame),
         bf = map(d, ~ ttestBF(
           x = .$Confidence[.$`Initial estimate accuracy` == 'Initial\ncorrect'],
           y = .$Confidence[.$`Initial estimate accuracy` == 'Initial\nincorrect'],
           data = ., paired = T)
         ),
         bf = map_chr(bf, ~ .@bayesFactor %>% .$bf %>% exp() %>% bf2str())) %>%
  select(-d)

gg$conf <- tmp %>%
  order_factors() %>%
  ggplot(aes(x = `Initial estimate accuracy`, y = Confidence, colour = Response)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
  scale_x_discrete() +
  coord_cartesian(clip = F) +
  geom_line(aes(group = pid), alpha = .25) +
  geom_split_violin(aes(x = nudge(`Initial estimate accuracy`, dw),
                        group = `Initial estimate accuracy`,
                        fill = Response),
                    width = .9, colour = NA) +
  geom_boxplot(aes(x = nudge(`Initial estimate accuracy`, dw),
                   group = `Initial estimate accuracy`),
               outlier.shape = NA, size = 1, width = dw/2, colour = 'black') +
  geom_segment(x = 1 - dw, xend = 2 + dw, y = 1, yend = 1,
               colour = 'black') +
  geom_label(aes(label = paste0('BF = ', bf)),
             x = 1.5, y = 1, colour = 'black', data = bf) +
  labs(x = "") +
  theme(legend.position = 'none') +
  facet_wrap(~response)

tmp <- familiarization %>%
  group_by(pid, adviceType) %>%
  select(c(matches('(adviceInfluence)'), group_vars(.))) %>%
  summarise_all(mean) %>%
  mutate(adviceTypeName = case_when(adviceType == 7 ~ 'High agreement',
                                    adviceType == 8 ~ 'Low agreement',
                                    T ~ NA_character_),
         `Feedback condition` = 'No feedback') %>%
  mutate(across(-matches('Influence'), factor)) %>%
  order_factors()

bf <- tmp %>%
  select(group_vars(.), adviceTypeName, adviceInfluence) %>%
  pivot_wider(names_from = adviceTypeName, values_from = adviceInfluence) %$%
  ttestBF(`High agreement`, `Low agreement`, paired = T) %>%
  .@bayesFactor %>%
  .$bf %>%
  exp() %>%
  bf2str()

dw <- .1

gg$inf <- ggplot(tmp, aes(x = adviceTypeName, y = adviceInfluence,
                colour = `Feedback condition`, fill = `Feedback condition`)) +
  geom_hline(yintercept = 0, colour = 'lightgrey', size = 1) +
  geom_line(aes(group = pid), alpha = .25) +
  geom_split_violin(aes(x = nudge(adviceTypeName, dw),
                        group = adviceTypeName), width = .9,
               colour = NA) +
  geom_boxplot(outlier.shape = NA, size = 1, width = dw/2,
               aes(x = nudge(adviceTypeName, dw),
                   group = adviceTypeName),
               colour = 'black') +
  geom_segment(x = 1, xend = 2, y = 1, yend = 1, colour = 'black') +
  geom_label(y = 1, x = 1.5, colour = 'black', fill = 'white',
             aes(label = paste0('BF = ', bf))) +
  scale_y_continuous(limits = c(-.5, 1),
                     breaks = seq(-.5, 1, length.out = 6),
                     expand = c(0, 0)) +
  coord_cartesian(clip = F) +
  facet_grid(~paste0(`Feedback condition`, '\n')) +
  labs(x = "", y = 'Advice influence') +
  theme(legend.position = 'none') +
  broken_axis

(gg$acc / gg$conf / gg$inf) + plot_annotation(tag_levels = 'A')

```

```{r ac-agr-dots-r-performance-aov}
out <- list()

# Accuracy
tmp <- familiarization %>% 
  transmute(
    pid = factor(pid),
    initialAnswerCorrect,
    finalAnswerCorrect,
    Advisor
  ) %>%
  group_by(pid, Advisor) %>%
  summarise(
    initial = mean(initialAnswerCorrect), 
    final = mean(finalAnswerCorrect), 
    .groups = 'drop'
  ) %>%
  pivot_longer(
    c(initial, final), 
    names_to = 'Decision', 
    values_to = 'accuracy'
  ) %>%
  mutate(Decision = factor(Decision))
  

aov_acc <- ez::ezANOVA(
  tmp, 
  dv = accuracy,
  wid = pid,
  within = c(Advisor, Decision)
)

out$acc_aov <- aov_acc$ANOVA %>%
  nest(d = -Effect) %>%
  mutate(s = map_chr(d, ~ glue(
    "F({.$DFn},{.$DFd})={num2str(.$F, 2)}, p={prop2str(.$p, minPrefix = '<')}"
  )))

tmp <- familiarization %>% 
  group_by(pid) %>%
  summarise(
    i = mean(initialAnswerCorrect),
    f = mean(finalAnswerCorrect)
  )

bf <- ttestBF(tmp$i, tmp$f, paired = T)
tt <- t.test(tmp$i, tmp$f, paired = T) %>% 
  tidy() %>%
  mutate(
    p.value = prop2str(p.value),
    across(where(is.numeric), num2str)
  )

out$acc_t <- glue(
  "T({tt$parameter})={tt$statistic}, p={tt$p.value}"
)

# Confidence
df <- familiarization %>% 
  transmute(
    pid = factor(pid),
    initialConfidence,
    finalConfidence,
    Advisor,
    initialAnswerCorrect,
    finalAnswerCorrect
  ) %>%
  pivot_longer(
    cols = c(initialConfidence, finalConfidence),
    names_to = "Decision", 
    names_pattern = "(.+)Confidence",
    values_to = "Confidence"
  ) %>%
  mutate(
    Correct = if_else(
      Decision == "initialConfidence", 
      initialAnswerCorrect,
      finalAnswerCorrect
    ),
    Correct = factor(Correct),
    Decision = factor(str_to_sentence(Decision))
  ) %>%
  select(-ends_with('AnswerCorrect')) %>%
  group_by(pid, Advisor, Decision, Correct) %>%
  summarise(
    Confidence = mean(Confidence), 
    .groups = 'drop'
  )

aov_conf <- ez::ezANOVA(
  df, 
  dv = Confidence,
  wid = pid,
  within = c(Advisor, Decision, Correct)
)

out$conf_aov <- aov_conf$ANOVA %>%
  nest(d = -Effect) %>%
  mutate(s = map_chr(d, ~ glue(
    "F({.$DFn},{.$DFd})={num2str(.$F, 2)}, p={prop2str(.$p, minPrefix = '<')}"
  )))

# 3-way interaction
m <- df %>% 
  group_by(Advisor, Correct, Decision) %>% 
  summarise(conf = mean(Confidence), .groups = 'drop') %>%
  pivot_wider(names_from = Decision, values_from = conf) %>%
  mutate(Difference = Final - Initial)

r <- familiarization %>% 
  group_by(pid) %>% 
  summarise(
    initialAccuracy = mean(initialAnswerCorrect),
    finalAccuracy = mean(finalAnswerCorrect),
    initialConfidence = mean(initialConfidence),
    finalConfidence = mean(finalConfidence)
  )

out$conf_r_i <- correlationBF(r$initialAccuracy, r$initialConfidence, paired = T)
out$conf_r_f <- correlationBF(r$finalAccuracy, r$finalConfidence, paired = T)

```

Basic behavioural performance was similar to that observed with the same Dots task in Experiment 1A§\@ref(ac-acc-dots-r-performance). 
Initial decision accuracy converged on the target 71%, and participants may have benefited from advice in terms of their final decisions being more accurate than their initial decisions (`r out$acc_t`; but note $\text{BF}_{10}= $`r bf2str(exp(bf@bayesFactor$bf))`; Figure \@ref(fig:ac-agr-dots-r-performance)A).
There was no evidence of a difference in this tendency between advisors, as indicated by an ANOVA of Advisor x Time, in which a main effect of Time (`r out$acc_aov$s[2]`) was significant, but not the main effect of Advisor (`r out$acc_aov$s[1]`) or the interaction (`r out$acc_aov$s[3]`).

Figure \@ref(fig:ac-agr-dots-r-performance)B and ANOVA indicated that participants were more confident in their correct answers than their incorrect ones (`r out$conf_aov$s[3]`), and less confident in their final decisions than their initial estimates (`r out$conf_aov$s[2]`), and that these two factors interacted (`r out$conf_aov$s[6]`).
The advisor also mattered, with a main effect (`r out$conf_aov$s[1]`) and interaction with Time (`r out$conf_aov$s[4]`).
There was also a three-way interaction (`r out$conf_aov$s[7]`) caused by confidence decreasing for incorrect answers and increasing for correct answers with the Low agreement advisor, and increasing regardless of correctness following advice from the High agreement advisor.

There was no correlation between initial estimate accuracy and confidence (`r bf2str(exp(out$conf_r_i@bayesFactor$bf))`), and no evidence for a correlation between final decision accuracy and confidence (`r bf2str(exp(out$conf_r_f@bayesFactor$bf))`).

Neither advisor appeared to be more influential than the other (Figure \@ref(fig:ac-agr-dots-r-performance)C).

##### Advisor performance

The advice is generated probabilistically from the rules described previously in Table \@ref(tab:ac-agr-dots-m-profiles).
It is thus important to get a sense of the actual advice experienced by the participants.

```{r ac-agr-dots-r-advice-agr}

tmp <- familiarization %>% 
  mutate(Advisor = advisor_profile_name(adviceType)) %>%
  filter(!is.na(Advisor)) %>%
  group_by(pid, Advisor) %>%
  summarise(`Agreement rate` = mean(advisorAgrees), .groups = 'drop') %>%
  pivot_wider(names_from = Advisor, values_from = `Agreement rate`) %>%
  mutate(
    `Participant experience` = if_else(`Low agreement` > `High agreement`,
                                       'Anomalous', 'As planned'),
    `Participant experience` = factor(
      `Participant experience`, 
      levels = c('As planned', 'Anomalous')
    )
  )
n_ap <- sum(tmp$`Participant experience` == "As planned")

tmp <- familiarization %>% 
  mutate(Advisor = advisor_profile_name(adviceType)) %>%
  filter(!is.na(Advisor)) %>%
  group_by(pid, Advisor, initialAnswerCorrect) %>%
  summarise(`Agreement rate` = mean(advisorAgrees), .groups = 'drop') %>%
  group_by(Advisor, initialAnswerCorrect) %>%
  summarise(`Agreement rate` = mean(`Agreement rate`), .groups = 'drop') %>%
  mutate(`Agreement rate` = prop2str(`Agreement rate`)) %>%
  pivot_wider(
    names_from = initialAnswerCorrect, 
    values_from = `Agreement rate`
  ) %>%
  rename(`Actual|correct` = `TRUE`, `Actual|incorrect` = `FALSE`)

agr.table %>%
  select(
    Advisor, 
    `Target|correct` = `Participant correct`,
    `Target|incorrect` = `Participant incorrect`
  ) %>%
  left_join(tmp, by = "Advisor") %>%
  select(
    Advisor,
    `Target|correct`,
    `Actual|correct`,
    `Target|incorrect`,
    `Actual|incorrect`
  ) %>%
  kable(label = "\\label{tab:ac-agr-dots-r-advice-agr}Advisor agreement for Dots task Agreement experiment")

```

```{r ac-agr-dots-r-advice-acc}

tmp <- familiarization %>% 
  group_by(pid, Advisor) %>%
  summarise(Accuracy = mean(adviceCorrect), .groups = 'drop') %>%
  group_by(Advisor) %>%
  summarise(`Mean accuracy` = mean(Accuracy), .groups = 'drop')

# Note: agr.table defined in the Advice profile section
agr.table %>% 
  select(Advisor, `Target accuracy` = `Overall accuracy`) %>%
  left_join(tmp, by = "Advisor") %>%
  mutate(`Mean accuracy` = prop2str(`Mean accuracy`)) %>%
  kable(label = "\\label{tab:ac-acc-dots-r-advice-acc}Advisor accuracy for Dots task Agreement experiment")

```

The advisors agreed with the participants' initial estimates at close to target rates (Table \@ref(tab:ac-agr-dots-r-advice-agr)), and were as accurate on average as expected (Table \@ref(tab:ac-agr-dots-r-advice-acc)). 
Nevertheless, some participants experienced in practice 10-20% differences in advisor accuracy (although neither advisor was systematically more accurate across participants). 
All participants experienced the intended relationship wherein the High agreement advisor agreed with them more than the Low agreement advisor.

##### \OpenScience{prereg} Hypothesis test {#ac-agr-r-h}

```{r ac-agr-dots-r-graph, fig.caption="Dot task advisor choice for high/low agreement advisors.  Participants' pick rate for the advisors in the Choice phase of the experiment. The violin area shows a density plot of the individual participants' pick rates, shown by dots. The chance pick rate is shown by a dashed line.", fig.height=6, fig.width=5}

test <- trials %>% 
  filter(hasChoice) %>%
  mutate(Advisor = advisor_profile_name(adviceType),
         Advisor = factor(Advisor)) %>%
  order_factors()

tmp <- test %>%
  group_by(pid) %>%
  summarise(pChooseHigh = sum(adviceType == 7) / sum(adviceType %in% c(7,8)),
            .groups = 'drop') %>%
  mutate(`Feedback condition` = 'No feedback')

bf <- ttestBF(pull(tmp, pChooseHigh), mu = .5)

ggplot(tmp, aes(x = '', y = pChooseHigh)) +
  geom_hline(yintercept = .5, linetype = 'dashed') +
  geom_violindot(size_dots = .4) +
  geom_violinhalf(aes(fill = `Feedback condition`, colour = `Feedback condition`)) +
  annotate(geom = 'label', label = paste0('BF vs chance\n', bf2str(exp(bf@bayesFactor$bf))),
           x = 1, y = 1.05) +
  scale_y_continuous(limits = c(0, 1.1), breaks = seq(0, 1, length.out = 5)) +
  labs(y = 'p(Choose High agreement advisor)', x = '') +
  theme(axis.ticks.x = element_blank(), axis.line.x = element_blank())

.T <- tmp %>%
  pull(pChooseHigh) %>%
  md.ttest(y = .5)

```

Our key analysis concerned whether participants would have a systematic preference for choosing the High agreement advisor when they were given a choice of advisor. 
Consistent with the key prediction of this experiment, advisor choice varied significantly as a function of advisor agreement rate (Figure \@ref(fig:ac-agr-dots-r-graph)): The High agreement advisor was preferred at a rate greater than that expected by chance (`r .T`).
The modal preference remained at chance, but almost all participants who manifested a preference preferred the High agreement advisor. 

##### Follow-up tests

```{r ac-agr-dots-r-choice-by-exp, fig.caption="Advisor choice by experience in the Dots task with dis/agreeing advisors.  Each dot is a participant's proportions. The difference in accuracy rates is calculated as the proportion of correct answers seen from the High accuracy advisor minus the proportion of correct answers seen from the Low accuracy advisor, and the difference in agreement rates similarly for agreement. The participants did not receive feedback on the correct answers"}

tmp <- left_join(
  left_join(
    familiarization %>% 
      group_by(pid, Advisor) %>%
      summarise(acc = mean(adviceCorrect), .groups = 'drop') %>%
      pivot_wider(names_from = Advisor, values_from = acc) %>%
      transmute(
        pid, 
        Accuracy = `High agreement` - `Low agreement`
      ),
    familiarization %>% 
      group_by(pid, Advisor) %>%
      summarise(agr = mean(advisorAgrees), .groups = 'drop') %>%
      pivot_wider(names_from = Advisor, values_from = agr) %>%
      transmute(
        pid, 
        Agreement = `High agreement` - `Low agreement`
      ),
    by = "pid"
  ),
  test %>%
    group_by(pid) %>%
    summarise(pPickHigh = mean(Advisor == "High agreement")),
  by = "pid"
)

m_acc <- lm(pPickHigh ~ Accuracy, data = tmp) %>%
  tidy()
m_agr <- lm(pPickHigh ~ Agreement, data = tmp) %>%
  tidy()
s <- tribble(
  ~ Dimension, ~ Label,
  "Accuracy",
  glue(
    "y = {a}{num2str(x)}{a}x + {b}{num2str(i)}{b}",
    i = m_acc$estimate[1],
    x = m_acc$estimate[2], 
    b = ifelse(m_acc$p.value[1] < .05, "**", ""),
    a = ifelse(m_acc$p.value[2] < .05, "**", "")
  ),
  "Agreement",
  glue(
    "y = {a}{num2str(x)}{a}x + {b}{num2str(i)}{b}",
    i = m_agr$estimate[1],
    x = m_agr$estimate[2], 
    b = ifelse(m_agr$p.value[1] < .05, "**", ""),
    a = ifelse(m_agr$p.value[2] < .05, "**", "")
  )
)

r_acc <- correlationBF(tmp$pPickHigh, tmp$Accuracy, paired = T)
r_agr <- correlationBF(tmp$pPickHigh, tmp$Agreement, paired = T)

tmp <- tmp %>%
  pivot_longer(
    c(Accuracy, Agreement),
    names_to = "Dimension",
    values_to = "Difference"
  )

ggplot(tmp, aes(x = Difference, y = pPickHigh)) +
  geom_vline(xintercept = 0, linetype = 'dashed') +
  geom_smooth(method = 'lm', formula = y ~ x) +
  geom_point(alpha = .25) +
  # coord_fixed() +
  scale_y_continuous(limits = 0:1) +
  geom_richtext(
    aes(label = Label), y = 1, x = mean(tmp$Difference), fill = NA, data = s
  ) +
  facet_wrap(~Dimension) +
  labs(y = "p(Pick High agreement)")

```
As noted above, the stochastic nature of the advisors' advice meant that there was some variation in the participants' experience of the advisors.
This allowed us to investigate whether either objective accuracy or agreement rate differences were predictive of pick rates.
This did not appear to be the case: there was no evidence of a relationship between participants' advisor preference and their experience of either advisor accuracy ($BF_{10}=$ `r bf2str(exp(r_acc@bayesFactor$bf))`) or advisor agreement ($BF_{10}=$ `r bf2str(exp(r_agr@bayesFactor$bf))`). 

We would not expect a relationship to accuracy here, because we hypothesise that the work done by accuracy differences in the previous experiment was actually driven by agreement, which we manipulated in this experiment.
We might have expected a correlation between experienced agreement rates and preference strength, but these are between-participant differences and we suspect there is a great deal of noise in participant preferences that would mask any differences over the rather limited agreement rate difference range.

```{r}
tmp <- test %>%
  select(pid, initialConfidence, Advisor) %>%
  nest(d = -pid) %>%
  mutate(
    d = map(
      d, 
      ~ mutate(
        ., 
        initialConfidence = initialConfidence >= median(.$initialConfidence)
      )
    )
  ) %>%
  unnest(cols = d) %>%
  group_by(pid, initialConfidence) %>%
  summarise(pickRate = mean(Advisor == "High agreement"), .groups = 'drop') %>%
  pivot_wider(names_from = initialConfidence, values_from = pickRate) %>%
  rename(lowConf = `FALSE`, highConf = `TRUE`)
  
bf <- ttestBF(tmp$lowConf, tmp$highConf, paired = T)
tmp <- tmp %>%
  summarise(across(-pid, mean))

```

We might also expect advisor preference to vary as a function of initial confidence.
Following the logic in the previous experiment (Experiment 1A1A§\@ref(ac-acc-dots-r-follow-up)), participants may have a strong preference for the High agreement advisor but only exercise that preference where they are unsure about the answer themselves (i.e. where advice is most valuable to them).
This appeared not to be the case: we split participants' trials into high and low confidence based on their idiosyncratic median confidence, and conducted a paired t-test of the pick rates for the High accuracy advisor in each confidence category.
The Bayes factor for this t-test indicated good evidence of no difference in pick rates ($\text{BF}_{10}=$ `r bf2str(exp(bf@bayesFactor$bf))`).

##### Summary/Discussion

Participants who had a preference for one of the two advisors almost universally preferred the High agreement advisor. 
These results are in line with the effects of advisor accuracy in the same task as found in Experiment 1A§\@ref(ac-acc-dots). 
They are also consistent with our hypothesis that agreement is used as a proxy for feedback when objective feedback is unavailable.
We next explored whether this pattern would also be apparent in the Dates task.

### Experiment 2B: Advisor agreement effects in the Dates Task {#ac-agr-dates}


```{r ac-agr-dates-load, include = F}

rm(list = ls()); source('scripts_and_filters/general_setup.R')

# Load the study data
select_experiment(
  project = 'datequiz',
  function(x) filter(x, study == 'agreementDates', manipulationOK)
)


.dropEnv <- new.env()
tada('datequiz', package = 'esmData', envir = .dropEnv)
.dropEnv$datequiz <- .dropEnv$datequiz %>% 
  filter(study == 'agreementDates', !manipulationOK)

.dropEnv$DROP_V <- paste0(unique(.dropEnv$datequiz$version), collapse = ', ')
.dropEnv$DROP_P <- sum(.dropEnv$datequiz %>% 
                         filter(table == 'AdvisedTrial') %>% 
                         pull(N))

AdvisedTrial <- annotate_responses(AdvisedTrial)

```

#### Open scholarship practices

This experiment was preregistered at `r unique(datequiz$preregistration)`.
The experiment data are available in the `esmData::` package for R from \mccorrect{!TODO[Zenodo esmData]}, and also directly from \mccorrect{!TODO[OSFify Dates task data]}.
A snapshot of the state of the code for running the experiment at the time the experiment was run can be obtained from https://github.com/oxacclab/ExploringSocialMetacognition/blob/master/ACBin/acc.html.

#### Method {#ac-agr-dates-m}

This study used the binary version of the Dates Task (§\@ref(m-p-dates-b)).

##### Advice profiles

The High agreement and Low agreement advisor profiles issued binary advice (endorsing either the 'before' or 'after' column) probabilistically based on which column the participant had selected in their initial estimate and whether that was the correct answer. 

\mccorrect{NICK: Different to the Table above -- I guess the missing columns reflect the fact we don't know participant accuracy. But did we have a target/average accuracy in mind, so that we could estimate agreement rates (and also overall advisor accuracy)? Make explicit if so, and also remind the reader why it's difficult to control advisor features well in the task (vs. the Dots task).}

```{r ac-agr-dates-m-profiles-r} 

agr <- matrix(c(.9, .65, .75, .35), 2, 2)

agr.table <- tribble(
  ~`Advisor`, ~`Participant correct`, ~`Participant incorrect`,
  "High agreement", agr[1, 1], agr[2, 1],
  "Low agreement", agr[1, 2], agr[2, 2],
) %>% 
  prop2str()

kable(agr.table, caption = "\\label{tab:ac-agr-dates-m-profiles}Advisor advice profiles for Dates task Agreement experiment") %>%
  kable_styling() %>%
  column_spec(1, bold = T) %>%
  row_spec(0, bold = F) %>%
  collapse_rows(columns = 1, valign = "top") %>%
  add_header_above(c(" ", 
                     "Probability of agreement (%)" = 2))

```

\mccorrect{NICK: Summarise here how well the manipulation worked (i.e., move up and condense the relevant Results section below). MATT: Leave where it is but summarise as suggested.}

#### Results {#ac-agr-dates-r}

##### Exclusions

```{r ac-agr-dates-r-clean}
maxTrialRT <- 60000   # trials take < 1 minute
minTrials <- 11       # at least 11 trials completed
minChangeRate <- .1   # some advice taken on 10%+ of trials
minKeyTrials <- 10    # exactly 10 key trials

AdvisedTrial <- AdvisedTrial %>% filter(timeEnd <= maxTrialRT)

exclusions <- AdvisedTrial %>% 
  nest(d = -pid) %>%
  mutate(
    `Too few trials` = map_lgl(d, ~ nrow(.) < minTrials),
    `Insufficient advice taking` = 
      map_lgl(d, ~ (mutate(
        ., 
        x = responseAnswerSide != responseAnswerSideFinal |
          responseConfidence != responseConfidenceFinal) %>%
          pull(x) %>% mean()) < minChangeRate),
    `Too few choice trials` = map_lgl(d, ~ sum(!is.na(.$advisorChoice)) < minKeyTrials)
  ) %>% 
  select(-d)

do_exclusions(exclusions)


exclusions$`Total excluded` <- exclusions %>% select(-pid) %>% apply(1, any)
n <- ncol(exclusions)
exclusions %>% 
  summarise(across(where(is.logical), sum)) %>%
  mutate(`Total remaining` = length(unique(AdvisedTrial$pid))) %>% 
  pivot_longer(everything(), names_to = "Reason", values_to = "Participants excluded") %>%
  kable(caption = "\\label{tab:ac-agr-dates-exclusions}Participant exclusions for Dates task Agreement experiment") %>%
  row_spec((n - 1):n, bold = T)

```

Individual trials were screened to remove those that took longer than `r maxTrialRT/1000`s to complete. Participants were then excluded for having fewer than `r minTrials` trials remaining, fewer than `r minKeyTrials` trials on which they had a choice of advisor, or for giving the same initial and final response on more than `r (1 - minChangeRate) * 100`% of trials. 
Overall, `r sum(pull(exclusions, "Total excluded"))` participants were excluded, with the details shown in Table \@ref(tab:ac-agr-dates-exclusions).

##### Task performance

```{r ac-agr-dates-r-performance}

Familiarization <- AdvisedTrial %>%
  filter(is.na(advisorChoice) | !advisorChoice) %>%
  mutate(Advisor = advisor_description_name(advisor0idDescription),
         Advisor = factor(Advisor)) %>%
  order_factors()

```

Before exploring the interaction between the participants' responses and the advisors' advice, and the participants' advisor selection behaviour, it is useful to verify that participants interacted with the task in a sensible way, and that the task manipulations worked as expected.
In this section, task performance is explored during the Familiarization phase of the experiment where participants received advice from a pre-specified advisor on each trial. 
There were an equal number of these trials for each participant for each advisor.

###### Response times

Participants made two decisions during each trial. 
Neither of these decisions had a maximum response time. 
Each participant's response times for both initial and final decisions can be seen in Figure \@ref(fig:ac-agr-dates-r-response-times).
As with the Accuracy experiment, when the Dates task response times are compared to the Dots task response times (\@ref(fig:ac-agr-dots-r-response-times)), they are not only longer, but they are also much more varied within participants.

```{r ac-agr-dates-r-response-times, fig.caption="Response times for the Dates task with High/Low agreement advisors.  Each point shows a response relative to the start of the trial. Each row indicates a single participant's trials. The ridges show the distribution of the underlying points, with initial estimates and final decisions shown in different colours. The grey numbers on the right show the number of trials whose response times were more than 3 standard deviations away from the mean of all final response times (rounded to the next 10s)."}

tmp <- Familiarization %>% 
  transmute(
    pid = factor(pid),
    `Initial estimate` = responseTimeEstimate,
    `Final decision` = responseTimeEstimateFinal
  ) %>%
  pivot_longer(c(`Initial estimate`, `Final decision`),
               names_to = "Event", 
               values_to = "Time") %>%
  filter(!is.na(Event) & !is.na(Time)) %>%
  rename(Participant = pid)

max_rt <- tmp %>% 
  filter(Event == 'Final decision') %>%
  mutate(zTime = scale(Time)) %>%
  filter(zTime > 3) %>%
  filter(zTime == min(zTime)) %>% 
  pull(Time) %>% 
  .[1]
# round to 10s
max_rt <- ceiling(max_rt / 10000) * 10000
  

# Replace out-of-scale values with a count of dropped values
dropped <- tmp %>%
  group_by(Participant) %>%
  filter(Time > max_rt) %>%
  transmute(n = n())

tmp <- tmp %>%
  filter(Time <= max_rt) %>% 
  mutate(
    Participant = fct_reorder(Participant, Time, .desc = T),
    Event = factor(Event)
  )

tmp %>% 
  order_factors() %>%
  ggplot(aes(y = Participant, x = Time, fill = Event, colour = Event)) +
  geom_density_ridges(alpha = .25, colour = NA) +
  geom_point(alpha = .25, size = .25) +
  geom_text(aes(label = paste0('+', dropped$n), y = Participant),
            inherit.aes = F, x = max_rt, colour = 'grey', hjust = 1, 
            data = dropped) +
  scale_x_continuous(limits = c(0, max_rt), expand = c(0, 0)) +
  labs(x = 'Time since trial start') +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = 'top',
    plot.margin = 
  ) +
  coord_fixed(max_rt/length(unique(tmp$Participant)))

```

###### Accuracy

Unlike in the Dots version of the task, participant accuracy is not controlled.
Participants managed to improve their performance from their initial estimates to their final decisions with both advisors (Figure \@ref(fig:ac-agr-dates-r-accuracy)). 
This is likely because the advisors themselves were more accurate than the participants, so following their advice was generally a good strategy, and the difficulty of the task meant that participants were very willing to be influenced by advice.

```{r ac-agr-dates-r-accuracy, fig.caption="Response accuracy for the Dates task with High/Low agreement advisors.  Faint lines show individual participant means, for which the violin and box plots show the distributions. The dashed line indicates chance performance. Dotted violin outlines show the distribution of actual advisor accuracy.  Because there were relatively few trials, the proportion of correct trials for a participant generally falls on one of a few specific values. This produces the lattice-like effect seen in the graph. Some participants had individual trials excluded for over-long response times, meaning that the denominator in the accuracy calculations is different, and thus producing accuracy values which are slightly offset from others'."}
dw <- .2

tmp <- Familiarization %>% 
  group_by(Advisor, pid) %>%
  summarise(
    `Initial estimate` = mean(responseAnswerSideCorrect),
    `Final decision` = mean(responseAnswerSideCorrectFinal),
    .groups = 'drop'
  ) %>%
  pivot_longer(cols = c(`Initial estimate`, `Final decision`), 
               names_to = 'Response', values_to = 'Accuracy') %>%
  mutate(Advisor = factor(paste0(Advisor, '\n')))

adv <- Familiarization %>%
  group_by(Advisor, pid) %>%
  summarise(
    Response = 'Advice',
    Accuracy = mean(advisor0adviceSideCorrect),
    .groups = 'drop'
  ) %>%
  mutate(Advisor = factor(paste0(Advisor, '\n')))

bf <- tmp %>% 
  nest(d = -Advisor) %>%
  mutate(d = map(d, as.data.frame),
    bf = map(d, ~ ttestBF(x = .$Accuracy[.$Response == 'Initial estimate'],
                          y = .$Accuracy[.$Response == 'Final decision'], 
                          data = ., paired = T)),
         bf = map_chr(bf, ~ .@bayesFactor %>% .$bf %>% exp() %>% bf2str())) %>%
  select(-d)

tmp %>%
  mutate(Response = factor(Response)) %>%
  order_factors() %>%
  ggplot(aes(x = Response, y = Accuracy, colour = Advisor)) +
  scale_y_continuous(limits = c(NA, 1), expand = c(0, 0)) +
  scale_x_discrete() +
  coord_cartesian(clip = F) +
  geom_hline(yintercept = .5, linetype = 'dashed') +
  geom_line(aes(group = pid), alpha = .25) +
  geom_split_violin(aes(x = nudge(Response, dw), 
                        group = Response, fill = Advisor), 
                    width = .9, colour = NA) +
  geom_split_violin(aes(x = 2 + dw), 
                    group = 2, fill = NA, colour = 'black', linetype = 'dotted', 
                    data = adv) +
  geom_boxplot(aes(x = nudge(Response, dw), group = Response),
               outlier.shape = NA, size = 1, width = dw/2, colour = 'black') +
  geom_segment(x = 1 - dw, xend = 2 + dw, y = 1.01, yend = 1.01, 
               colour = 'black') +
  geom_label(aes(label = paste0('BF = ', bf)), 
             x = 1.5, y = 1.01, colour = 'black', data = bf) +
  facet_wrap(~Advisor) +
  broken_axis_bottom

```

###### Confidence

Generally, we expect participants to be more confident on trials on which they are correct compared to trials on which they are incorrect.
Participants were systematically more confident on correct as compared to incorrect trials for both initial estimates and final decisions.

```{r ac-agr-dates-r-confidence, fig.caption="Confidence for the Dates task with High/Low agreement advisors.  Faint lines show individual participant means, for which the violin and box plots show the distributions."}

dw <- .2

tmp <- Familiarization %>% 
  mutate(`Initial answer accuracy` = 
           if_else(responseAnswerSideCorrect, 'Correct', 'Incorrect')) %>%
  group_by(`Initial answer accuracy`, pid) %>%
  summarise(
    `Initial estimate` = mean(responseConfidenceScore),
    `Final decision` = mean(responseConfidenceScoreFinal),
    .groups = 'drop'
  ) %>%
  pivot_longer(cols = c(`Initial estimate`, `Final decision`), 
               names_to = 'Response', values_to = 'Confidence') %>%
  mutate(response = factor(paste0(Response, '\n')),
         Response = factor(Response))

bf <- tmp %>% 
  nest(d = -response) %>%
  mutate(d = map(d, as.data.frame),
         bf = map(d, ~ ttestBF(
           x = .$Confidence[.$`Initial answer accuracy` == 'Correct'],
           y = .$Confidence[.$`Initial answer accuracy` == 'Incorrect'], 
           data = ., paired = T)
         ),
         bf = map_chr(bf, ~ .@bayesFactor %>% .$bf %>% exp() %>% bf2str())) %>%
  select(-d)

tmp %>%
  mutate(`Initial answer accuracy` = factor(`Initial answer accuracy`)) %>%
  order_factors() %>%
  ggplot(aes(x = `Initial answer accuracy`, y = Confidence, colour = Response)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
  scale_x_discrete() +
  coord_cartesian(clip = F) +
  geom_line(aes(group = pid), alpha = .25) +
  geom_split_violin(aes(x = nudge(`Initial answer accuracy`, dw), 
                        group = `Initial answer accuracy`, 
                        fill = Response), 
                    width = .9, colour = NA) +
  geom_boxplot(aes(x = nudge(`Initial answer accuracy`, dw), 
                   group = `Initial answer accuracy`),
               outlier.shape = NA, size = 1, width = dw/2, colour = 'black') +
  geom_segment(x = 1 - dw, xend = 2 + dw, y = 1.01, yend = 1.01, 
               colour = 'black') +
  geom_label(aes(label = paste0('BF = ', bf)), 
             x = 1.5, y = 1.01, colour = 'black', data = bf) +
  facet_wrap(~response)

```

###### Metacognitive ability

The participants' metacognitive abilities were highly variable, with several participants displaying below-chance metacognitive ability (Figure \@ref(fig:ac-agr-dates-r-roc)).
While this may appear concerning, recall that metacognitive sensitivity and bias vary substantially and cannot be reliably estimated using ROC curves where performance accuracy on the underlying task is highly variable, so it is not necessarily the case that these values give cause for alarm.
The correlation between performance on the underlying task and metacognitive ability (Figure \@ref(fig:ac-agr-dates-r-roc-cor)) shows that, as one might expect, participants with a greater ability to perform the Dates task have a greater insight into their performance on the Dates task.
This in turn suggests that, despite the low number of trials on the task, we are able to obtain meaningful insights into participants' metacognitive abilities, albeit without being able to precisely estimate the metacognitive sensitivity or bias for an individual participant.

```{r ac-agr-dates-r-roc, fig.caption="ROC curves for the Dates task with High/Low agreement advisors.  Faint lines show individual participant data, while points and solid lines show mean data for all participants. Each participant's data are split into initial estimates and final decisions. For correct and incorrect responses seperately, the probability of a confidence rating being above a response threshold is calculated, with the threshold set to every possible confidence value in turn. This produces a point for each participant in each response for each possible confidence value indicating the probability of confidence being at least that high given the answer was correct, and the equivalent probability given the answer was incorrect. These points are used to create the faint lines, and averaged to produce the solid lines. The dashed line shows chance performance where the increasing confidence threshold leads to no increase in discrimination between correct and incorrect answers."}

nQuantiles <- 100 # confidence range

tmp <- Familiarization %>% 
  transmute(
    pid, 
    Advisor,
    initialAnswerCorrect = responseAnswerSideCorrect,
    finalAnswerCorrect = responseAnswerSideCorrectFinal,
    initialConfidenceScore = responseConfidenceScore,
    finalConfidenceScore = responseConfidenceScoreFinal
  ) %>%
  pivot_longer(cols = c(starts_with('initial'), starts_with('final')),
               names_to = c('Response', '.value'),
               names_pattern = '(initial|final)(.*)') %>%
  # calculate p(confidence > q) for in/correct answers at each quantile q
  nest(d = c(-pid, -Response, -AnswerCorrect)) %>%
  mutate(
    d = map(d, ~ p_conf(., seq(0, 1, length.out = nQuantiles)))
  ) %>%
  unnest(cols = d) %>% 
  unnest(cols = d)

tmp <- tmp %>% 
  mutate(
    Response = if_else(Response == 'initial', 
                       'Initial estimate', 'Final decision'),
    response = factor(paste0(Response, '\n')),
    response = factor(response),
    Confidence = factor(Confidence),
    Confidence = fct_relabel(Confidence, ~prop2str(as.numeric(unique(.))))
  ) %>%
  pivot_wider(names_from = AnswerCorrect, 
              names_prefix = 'Correct', 
              values_from = pConf) 

auroc <- tmp %>% 
  nest(d = c(-pid, -response)) %>%
  mutate(
    d = map(d, ~arrange(., CorrectFALSE, rev(CorrectTRUE))),
    d = map(d, ~mutate(., area = CorrectTRUE * 
                         (CorrectFALSE - lag(CorrectFALSE)))),
    area = map_dbl(d, ~ sum(.$area, na.rm = T))
  ) %>%
  select(-d) 

auroc.gg <- auroc %>%
  nest(d = -response) %>%
  mutate(
    d = map(d, ~ mutate(., mean = mean(area))),
    gg = map(
      d, 
      ~ ggplot(., aes(y = area)) +
        geom_hline(yintercept = .5, linetype = 'dashed') +
        geom_density(fill = 'black') +
        geom_hline(aes(yintercept = mean), data = unique(select(., mean))) +
        geom_label(aes(y = mean, x = nrow(.), 
                       label = paste0('Mean = ', prop2str(mean))), 
                   hjust = 1, data = unique(select(., mean))) +
        scale_y_continuous(limits = c(0, 1), expand = c(0, 0), 
                           breaks = c(0, .5, 1)) +
        scale_x_continuous(limits = c(0, nrow(.)), expand = c(0, 0),
                           position = 'top') +
        labs(x = "", y = "AUC") +
        theme(axis.ticks.x = element_blank(),
              axis.line.x = element_blank(),
              panel.grid.major.x = element_line(),
              plot.margin = unit(rep(0, 4), 'lines'))
    )
  )

tmp.avg <- tmp %>%
  group_by(Confidence, response) %>%
  summarise(across(where(is.numeric), mean), .groups = 'drop')

tmp.avg %>%
  order_factors() %>%
  ggplot(aes(x = CorrectFALSE, y = CorrectTRUE)) +
  geom_abline(slope = 1, intercept = 0, linetype = 'dashed') +
  geom_line(aes(group = pid), alpha = .2, colour = 'grey', data = tmp) +
  geom_line() +
  geom_point() +
  geom_plot(aes(label = gg), x = 1, y = .025, vp.width = 2/3, data = auroc.gg) +
  scale_x_continuous(limits = c(0, 1), expand = c(0, .01)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, .01)) +
  coord_fixed() +
  facet_wrap(~response) +
  theme(panel.spacing.x = unit(2, 'lines'),
        plot.margin = unit(c(0, 0, 4, 0), 'lines')) +
  labs(x = 'p( Confidence > threshold | Incorrect )', 
       y = 'p( Confidence > threshold | Correct )')

```

```{r ac-agr-dates-r-roc-cor, fig.caption="AUROC-accuracy correlation for the Dots task with High/Low agreement advisors.  Points show individual participant data for their area under the receiver operator characteristic (ROC) curve and their accuracy on initial estimates and final decisions. The blue lines and equation text show best-fit regression, and the shaded area gives its standard error. The equations give the regression equation plotted in blue, with bold coefficients being significant at p = .05."}

# Correlations between Type II AUROC and accuracy
acc <- left_join(
  auroc,
  Familiarization %>% 
    group_by(pid) %>% 
    summarise(initialAccuracy = mean(responseAnswerSideCorrect),
              finalAccuracy = mean(responseAnswerSideCorrectFinal),
              .groups = 'drop') %>%
    pivot_longer(-pid) %>%
    transmute(
      pid,
      response = factor(
        if_else(name == 'initialAccuracy', 
                'Initial estimate\n', 'Final decision\n')
      ),
      accuracy = value
    ),
  by = c('pid', 'response')
)

r = acc %>% 
  nest(d = -response) %>%
  mutate(
    d = map(d, ~ lm(area ~ accuracy, data = .)),
    d = map(d, tidy),
    d = map(d, ~ pivot_wider(., names_from = term, values_from = -term)),
    d = map_chr(d, ~paste0('y = ', 
                           if_else(.$`p.value_(Intercept)` < .05, '**', ''), 
                           round(.$`estimate_(Intercept)`, 2),
                           if_else(.$`p.value_(Intercept)` < .05, '**', ''), 
                           ' + ',
                           if_else(.$p.value_accuracy < .05, '**', ''),
                           round(.$estimate_accuracy, 2),
                           if_else(.$p.value_accuracy < .05, '**', ''), 
                           'x'))
  )

acc %>% 
  order_factors() %>%
  ggplot(aes(x = accuracy, y = area)) +
  geom_abline(slope = 1, intercept = 0, linetype = 'dashed') +
  geom_smooth(method = 'lm', formula = y ~ x) +
  geom_point(alpha = .2) +
  geom_richtext(x = .01, y = .99, hjust = 0, vjust = 1, fill = NA,
                aes(label = d), 
                data = r) +
  scale_x_continuous(limits = c(.0, 1), expand = c(0,0)) +
  scale_y_continuous(limits = c(.0, 1), expand = c(0,0)) +
  coord_fixed() +
  facet_wrap(~response) +
  labs(x = 'Accuracy', y = 'Area under ROC curve') +
  theme(panel.spacing.x = unit(2, 'lines'),
        plot.margin = unit(c(0, 0, 4, 0), 'lines'))

```

##### Experience with advisors

The advice is generated probabilistically from the rules described previously in Table \@ref(tab:ac-agr-dots-m-profiles).
It is thus important to get a sense of the actual advice experienced by the participants.

###### Advisor accuracy

As shown in Figure \@ref(fig:ac-agr-dates-r-advice-acc), the advisors were similarly accurate on average as expected. 
Nevertheless, there was a broad range of experiences between participants, both in the absolute accuracy of advisors and in their relative accuracies.
This variation is due to the relatively low number of trials on which advice was received from each advisor.

```{r ac-agr-dates-r-advice-acc, fig.caption="Advisor accuracy for Dots task with High/Low agreement advisors.  Coloured lines show the average accuracy of the advisors as experienced by an individual participant. Box plots and violins show the distribution of the participant means."}

dw <- .2

tmp <- Familiarization %>% 
  filter(!is.na(Advisor)) %>%
  group_by(pid, Advisor) %>%
  summarise(Accuracy = mean(advisor0adviceSideCorrect), .groups = 'drop')

tmp %>%
  ggplot(aes(x = Advisor, y = Accuracy)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
  scale_x_discrete() +
  geom_line(aes(group = pid), alpha = .2) +
  geom_split_violin(aes(x = nudge(Advisor, dw), group = Advisor), 
                    width = .9, colour = NA, fill = 'grey') +
  geom_boxplot(aes(x = nudge(Advisor, dw), group = Advisor),
               outlier.shape = NA, size = 1, width = dw/2, colour = 'black')

```

###### Advisor agreement

Figure \@ref(fig:ac-agr-dots-r-advice-agr) shows the agreement rates experienced by each participant. 
Most participants experienced a higher agreement rate from the High agreement advisor than from the Low agreement advisor, as per the manipulation in the experimental design.

\mccorrect{Should this break down agreement by initial in/correct as per the experiment design?}

```{r ac-agr-dates-r-advice-agr, fig.caption="Advisor agreement for Dots task with High/Low agreement advisors.  Faint lines show the average agreement rate of the advisors as experienced by an individual participant. The colour of the line indicates whether the higher agreement advisor agreed with the participant more often as per the experiment design. Box plots and violins show the distribution of the participant means."}

dw <- .2

tmp <- Familiarization %>% 
  filter(!is.na(Advisor)) %>%
  group_by(pid, Advisor) %>%
  summarise(`Agreement rate` = mean(advisor0adviceSide == responseAnswerSide), 
            .groups = 'drop') %>%
  # Calculate anomalous experiences
  pivot_wider(names_from = Advisor, values_from = `Agreement rate`) %>%
  mutate(`Participant experience` = if_else(`Low agreement` > `High agreement`,
                                            'Anomalous', 'As planned'),
         `Participant experience` = factor(
           `Participant experience`, 
           levels = c('As planned', 'Anomalous')
         )) %>%
  pivot_longer(cols = c(`High agreement`, `Low agreement`), 
               names_to = 'Advisor', values_to = 'Agreement rate') %>%
  mutate(Advisor = fct_rev(factor(Advisor)))

tmp %>%
  order_factors() %>%
  ggplot(aes(x = Advisor, y = `Agreement rate`, colour = `Participant experience`)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
  scale_x_discrete() +
  scale_colour_discrete(drop = F) +
  scale_alpha_manual(values = c(.5, .25), drop = F) +
  geom_line(aes(group = pid, alpha = `Participant experience`)) +
  geom_split_violin(aes(x = nudge(Advisor, dw), group = Advisor), 
                    width = .9, colour = NA, fill = 'grey') +
  geom_boxplot(aes(x = nudge(Advisor, dw), group = Advisor),
               outlier.shape = NA, size = 1, width = dw/2, colour = 'black')

```


##### Advisor influence

The Low agreement was systematically more influential for participants in both Feedback and No feedback conditions.
This is presumably due to the fact that disagreeing advice is generally more influential, in part due to the assymetry of the response scale once an initial estimate has been made.
Any influence effects in play during the Advisor choice phase may be more pronounced, since these data pertain to the Familiarization phase only, in which participants were still learning about the usefulness of their advisors.

```{r ac-agr-dates-r-influence-graph, fig.caption="Date task advisor influence for High/Low agreement advisors.  Participants' weight on the advice for advisors in the Familiarization phase of the experiment. The shaded area and boxplots indicate the distribution of the individual participants' mean influence of advice. Individual means for each participant are shown with lines in the centre of the graph. The theoretical range for influence values is [-2, 2]."}

tmp <- Familiarization %>%
  group_by(pid, Advisor, feedback) %>%
  select(c(matches('(influence|WOA)'), group_vars(.))) %>%
  summarise_all(mean)

# Add in feedback condition
tmp <- left_join(
  tmp,
  AdvisedTrial %>% 
    group_by(pid) %>% 
    summarise(feedbackCondition = case_when(any(feedback == 1) ~ 'Feedback', 
                                            T ~ 'No feedback'),
              .groups = 'drop'),
  by = 'pid'
) %>% 
  ungroup() %>%
  mutate_if(is.character, factor) %>%
  mutate(`Feedback condition` = feedbackCondition,
         Advisor = factor(Advisor)) %>%
  order_factors()

bf <- tmp %>% 
  nest(d = -c(feedbackCondition, `Feedback condition`)) %>%
  mutate(
    bf = map(d, ~ select(., pid, Advisor, advisor0Influence) %>%
               pivot_wider(names_from = Advisor, values_from = advisor0Influence) %>%
               filter_if(is.numeric, ~ !is.na(.)) %$%
               ttestBF(x = `High agreement`, y = `Low agreement`, data = ., paired = T))
  ) 

bf$BF <- sapply(1:nrow(bf), function(i) bf2str(exp(bf$bf[[i]]@bayesFactor$bf)))


dw <- .1

ggplot(tmp, aes(x = Advisor, y = advisor0Influence, 
                colour = `Feedback condition`, fill = `Feedback condition`)) +
  geom_hline(yintercept = 0, colour = 'lightgrey', size = 1) +
  geom_line(aes(group = pid), alpha = .25) +
  geom_split_violin(aes(x = nudge(Advisor, dw),
                        group = Advisor), width = 1,
               colour = NA) +
  geom_boxplot(outlier.shape = NA, size = 1, width = dw/2,
               aes(x = nudge(Advisor, dw), 
                   group = Advisor),
               colour = 'black') +
  geom_segment(x = 1, xend = 2, y = 1.55, yend = 1.55, colour = 'black') +
  geom_label(y = 1.55, x = 1.5, colour = 'black', fill = 'white', 
             aes(label = paste0('BF = ', BF)), data = bf) +
  scale_y_continuous(limits = c(-.50, 1.60), breaks = seq(-.50, 1.50, length.out = 6)) +
  scale_fill_hue(direction = -1, aesthetics = c('fill', 'colour')) +
  facet_grid(~`Feedback condition`) +
  labs(x = 'Advisor advice profile', y = 'Influence of advice') +
  broken_axis

```

##### \OpenScience{prereg} Hypothesis test

```{r ac-agr-dates-r-graph, fig.caption="Dates task advisor choice for High/Low agreement advisors.  Participants' pick rate for the advisors in the Choice phase of the experiment. The violin area shows a density plot of the individual participants' pick rates, shown by dots. The chance pick rate is shown by a dashed line. Participants in the Feedback condition received feedback during the Familiarization phase, but not during the Choice phase.", fig.height=6, fig.width=6}

tmp <- AdvisedTrial %>% 
  filter(advisorChoice == T) %>%
  group_by(pid) %>%
  summarise(pChooseHigh = mean(advisor0idDescription == 'highAgreement'),
            .groups = 'drop')

# Add in feedback condition
tmp <- left_join(
  tmp,
  AdvisedTrial %>% 
    group_by(pid) %>% 
    summarise(feedbackCondition = case_when(any(feedback == 1) ~ 'Feedback', 
                                            T ~ 'No feedback'),
              .groups = 'drop'),
  by = 'pid'
) %>% 
  mutate_if(is.character, factor) %>%
  mutate(`Feedback condition` = feedbackCondition) %>%
  order_factors()

bf <- tmp %>% 
  nest(d = -feedbackCondition) %>%
  mutate(bf = map(d, ~ pull(., pChooseHigh) %>% 
                        ttestBF(mu = .5))) 
bf$bf <- sapply(1:nrow(bf), function(i) num2str(exp(pull(bf, bf)[[i]]@bayesFactor$bf)))

bf.comp <- ttestBF(formula = pChooseHigh ~ feedbackCondition, data = tmp) %>%
  .@bayesFactor %>% .$bf %>% exp() %>% num2str()

ggplot(tmp, aes(x = feedbackCondition, y = pChooseHigh)) +
  geom_hline(yintercept = .5, linetype = 'dashed') +
  geom_violindot(size_dots = .4) +
  geom_violinhalf(aes(fill = `Feedback condition`, colour = `Feedback condition`)) +
  geom_label(aes(label = paste0('BF vs chance\n', bf)), y = 1.1, data = bf) +
  annotate(geom = 'segment', x = 1, xend = 2, y = 1.2, yend = 1.2) +
  annotate(geom = 'label', x = 1.5, y = 1.2, label = paste0('BF = ', bf.comp)) +
  scale_y_continuous(limits = c(0, 1.2), breaks = seq(0, 1, length.out = 5)) +
  scale_fill_hue(direction = -1, aesthetics = c('fill', 'colour')) +
  labs(y = 'p(Choose High agreement advisor)', x = '') +
  theme(axis.line.x = element_blank(), axis.ticks.x = element_blank())

.T.fb <- tmp %>%
  filter(feedbackCondition == 'Feedback') %>%
  pull(pChooseHigh) %>%
  md.ttest(y = .5, labels = c('*M*$_{Feedback}$'))

.T.Nfb <- tmp %>%
  filter(feedbackCondition != 'Feedback') %>%
  pull(pChooseHigh) %>%
  md.ttest(y = .5, labels = c('*M*$_{No feedback}$'))

```

Consistent with the result from the Dots task, in the No feedback condition participants' preferences for receiving advice from the High agreement advisor were greater than chance (`r .T.Nfb`).
\mccorrect{NICK: You're presenting in-line stats here, in a break from what you've done above where the stats also appear in a figure. In-line stats are fine to me (and, as I mentioned earlier when we met, your examiners might be picky about requiring this). Anyway, be consistent about your formatting/presentation of stats.}
The modal preference was to select the High agreement advisor on every Choice trial, and although some participants still showed a preference for hearing advice from the Low agreement advisor, preferences for the High agreement advisor were generally stronger and more frequent (Figure \@ref(fig:ac-agr-dates-r-graph)).

In the Feedback condition, the mean of the participants' selection rates was equivalent to random picking (`r .T.fb`).
This is consistent with a strategy which attempts to maximise the accuracy of final decisions, because neither advisor would help with this task systematically. 
The null result here does indicate, however, that there is no strong and clear preference for agreement over and above its accuracy benefits.
\mccorrect{NICK: This is true in one sense -> if we think about mean preference. However, individual participants do show clear preferences -- they're just not systematic across participants. Worth making this explicit, I think. E.g., you could calculate the binomial probability of generating pick rates as extreme as the ones you're seeing here in most partipants (i.e., give p(chooseA)=p(chooseB)=0.5 and N choices. Regardless, it's worth commenting explicitly on the variability in pick rate that you see.}

\mccorrect{NICK: Suggest editing in line with the suggestions above: Make explicit this is the key analysis. Present this analysis before the one on influence. Consider exploring whether differences are predicted by differing experience of advisor accuracy/agreement.}

\mccorrect{NICK: Comment also on the lack of significant interaction, which limits what you can conclude. I think the overall story here is that without feedback, people prefer agreement, but with feedback their behaviour is much more variable (as opposed to consistently picking at random).}

### Discussion {#ac-agr-d}

These two experiments investigated the impact of advisor agreement on choice of advice. 
In both Dots and Dates tasks, where feedback is not provided on advisors' performance, participants prefer high agreement advisors to low agreement advisors.
\mccorrect{NICK: Maybe need care in wording here. The feedback can be used to infer advisor performance, but strictly speaking the feedback is given in relation to what the participant decides.}

\mccorrect{At least in the Dates task the low agreement advice is probably more interesting - we already know what the high agreement advisor is going to say!}

\mccorrect{re: influence - 
An alternative explanation for the data is that the 'offbrand' advice selected for analysis was more surprising when coming from the advisor who usually agrees, and that this increased salience increased its influence rather than increased trust in the advisor.}
\mcorrect{NICK: Need explain what this is. But above in the corresponding Results section it seems like you're talking about influence of overall advice in the familiarisation phase. I'd forgotten this detail about "test" advice trials with offbrand advice. Remind the reader, even if the specifics are already explained in the general methods.
In general, your discussion ought to focus first on pick rates. E.g., what do you take-away from the finding of more picks for agreeing advice in both tasks (without feedback)? Then comment on what happens with feedback -- the bonus for agreeing advice is (overall) lost. But you still see wide preferences: These could be just random picks, but it could also be something systematic -- some people really like agreement, others like disagreement (as a preview of your modelling of advisor choices).
Any analysis of influence in this study (and in the series of experiments in general) has to be very tentative, given the designs really aren't optimised to measure it. I wouldn't put a lot of time into investigating influence differences.}
If that were the case then the same ought to be true for agreeing advice from a disagreeing advisor, and this is not the case \mccorrect{!TODO[Do we have/can we produce evidence for this? Perhaps look at our participants where advisors disagree with them by chance more than e.g. 70\% of the time and check for increased influence on agreement trials vs advisors who disagree less than 70\% of the time]}.
