
## Agreement {#ac-agr}

\mccorrect{!TODO[check Niccolo covered this]} 

Pescetelli and Yeung \mccorrect{!TODO[cite new paper]} demonstrated that advisors who agree \mccorrect{!TODO[somewhere we need to talk about what we mean by agreement, how Niccolo defined it, how we define it (varies between binary/continuous tasks), etc.]} more frequently are more influential (regardless of the presence of feedback) in a lab-based perceptual decision-making task.

There were differences in how participants selected the advisors between the Dots task (which has no feedback) and the No feedback condition of the Dates task for High versus Low accuracy advisors.
We may expect more pronounced effects in the absence of feedback when contrasting High versus Low agreement advisors, because we expect that agreement is the driving force behind the accuracy differences where feedback is not provided.

### Dots Task {#ac-agr-dots}

```{r include = F}

rm(list = ls()); source('scripts_and_filters/general_setup.R')

select_experiment(
  project = 'dotstask',
  function(x) filter(x, study == 'Agreement')
)

trials <- annotate_responses(trials)

```

#### Open scholarship practices

\indent\indent\OpenScience{prereg} `r unique(dotstask$preregistration)`

\OpenScience{data} \mccorrect{!TODO[OSFify data for these studies]}

\OpenScience{materials} https://github.com/oxacclab/ExploringSocialMetacognition/blob/9932543c62b00bd96ef7ddb3439e6c2d5bdb99ce/AdvisorChoice/index.html

##### Unanalysed data

There were no unanalysed data for this experiment.

#### Method {#ac-agr-dots-m}

\mccorrect{!TODO[clarify any methodological differences from the main methods chapter]}

##### Advice profiles

```{r ac-agr-dots-m-profiles-setup} 

pCor <- .71
agr <- matrix(c(.84, .61, .66, .17), 2, 2)


agr.table <- tribble(
  ~`Advisor`, ~`Participant correct`, ~`Participant incorrect`, ~`Overall`, ~`Overall accuracy`,
  "High agreement", agr[1, 1], agr[2, 1], sum(agr[,1] * c(pCor, 1 - pCor)), sum(agr[1,1] * pCor, (1 - agr[2,1]) * (1 - pCor)),
  "Low agreement", agr[1, 2], agr[2, 2], sum(agr[,2] * c(pCor, 1 - pCor)), sum(agr[1,2] * pCor, (1 - agr[2,2]) * (1 - pCor))
) %>% 
  prop2str()

tmp <- sapply(1:ncol(agr), function(i) sum(agr[, i] * c(pCor, 1 - pCor)))

```

The two advisor profiles (Table \@ref(tab:ac-agr-dots-m-profiles)) used in the experiment were High agreement and Low agreement
The High agreement advisor gave advice that endorsed the same answer side as the participant's initial estimate `r round(tmp[1] * 100, 1)`% of the time while the Low agreement advisor agreed with the participant `r round(tmp[2] * 100, 1)`% of the time.
The advisor profiles were balanced for overall accuracy rates.

```{r ac-agr-dots-m-profiles-r} 

kable(agr.table, caption = "\\label{tab:ac-agr-dots-m-profiles}Advisor advice profiles for Dots task Agreement experiment") %>%
  kable_styling() %>%
  column_spec(1, bold = T) %>%
  row_spec(0, bold = F) %>%
  collapse_rows(columns = 1, valign = "top") %>%
  add_header_above(c(" ", 
                     "Probability of agreement" = 3,
                     " "))

```

#### Results {#ac-agr-dots-r}

##### Exclusions

```{r}
nMaxOutliers <- 2
zThresh <- 3
accuracyRange <- c(.6, .85)
minTrialsPerCategory <- 12
preRegParticipants <- 50

tmp <- trials %>% 
  nest(d = -pid) %>%
  mutate(d = map_dbl(d, ~ mean(.$initialAnswerCorrect)))

exclusions <- tibble(pid = unique(trials$pid)) %>%
  mutate(
    `Accuracy too low` = pid %in% filter(tmp, d < accuracyRange[1])$pid,
    `Accuracy too high` = pid %in% filter(tmp, d > accuracyRange[2])$pid
  )

tmp <- trials %>% 
  filter(!practice) %>%
  nest(d = c(-pid, -confidenceCategory)) %>%
  mutate(n = map_int(d, nrow)) %>%
  select(-d) %>%
  pivot_wider(names_from = confidenceCategory, 
              names_prefix = "cc", 
              values_from = n) %>%
  mutate(
    anyNA = is.na(cc0) | is.na(cc1) | is.na(cc2),
    lowest = pmin(cc0, cc1, cc2, na.rm = T)
  )

exclusions <- exclusions %>% 
  mutate(
    `Missing confidence categories` = pid %in% filter(tmp, anyNA)$pid,
    `Skewed confidence categories` = pid %in% filter(tmp, lowest < minTrialsPerCategory)$pid
  )
  
do_exclusions(exclusions)

tmp <- trials %>% nest(d = -pid) %>% rowid_to_column() %>% filter(rowid > preRegParticipants)

exclusions <- exclusions %>% mutate(`Too many participants` = pid %in% tmp$pid)

do_exclusions(exclusions, backup = F)


exclusions$`Total excluded` <- exclusions %>% select(-pid) %>% apply(1, any)
n <- ncol(exclusions)
exclusions %>% 
  summarise(across(where(is.logical), sum)) %>%
  mutate(`Total remaining` = length(unique(trials$pid))) %>% 
  pivot_longer(everything(), names_to = "Reason", values_to = "Participants excluded") %>%
  kable(caption = "\\label{tab:ac-agr-dots-exclusions}Participant exclusions for Dots task Agreement experiment") %>%
  row_spec((n - 1):n, bold = T)

```

Participants' data could be excluded from analysis where they have an average accuracy below `r accuracyRange[1]` or above `r accuracyRange[2]`, do not have trials in all confidence categories, have fewer than `r minTrialsPerCategory` trials in each confidence category, or finish the experiment after `r preRegParticipants` participants have already submitted data which passed the other exclusion tests. 
Overall, `r sum(pull(exclusions, "Total excluded"))` participants were excluded, with the details shown in Table \@ref(tab:ac-agr-dots-exclusions).

##### Task performance

```{r}

familiarization <- trials %>%
  filter(typeName == "force", adviceType %in% c(7,8)) %>%
  mutate(Advisor = advisor_profile_name(adviceType),
         Advisor = factor(Advisor)) %>%
  order_factors()

```

Before exploring the interaction between the participants' responses and the advisors' advice, and the participants' advisor selection behaviour, it is useful to verify that participants interacted with the task in a sensible way, and that the task manipulations worked as expected.
In this section, task performance is explored during the Familiarization phase of the experiment where participants received advice from a pre-specified advisor on each trial. 
There were an equal number of these trials for each participant for each advisor.

###### Response times

Participants made two decisions during each trial. 
Neither of these decisions had a maximum response time. 
Each participant's response times for both initial and final decisions can be seen in Figure \@ref(fig:ac-agr-dots-r-response-times).

```{r ac-agr-dots-r-response-times, fig.caption="Response times for the Dots task with in/accurate advisors.  Each point shows a response relative to the start of the trial. Each row indicates a single participant's trials. The ridges show the distribution of the underlying points, with initial estimates and final decisions shown in different colours. The grey numbers on the right show the number of trials whose response times were more than 3 standard deviations away from the mean of all final response times (rounded to the next 10s)."}

tmp <- familiarization %>% 
  transmute(
    pid = factor(pid),
    `Initial estimate` = timeInitialResponse - timeInitialStart,
    `Final decision` = timeFinalResponse - timeInitialStart
  ) %>%
  pivot_longer(c(`Initial estimate`, `Final decision`),
               names_to = "Event", 
               values_to = "Time") %>%
  filter(!is.na(Event) & !is.na(Time)) %>%
  rename(Participant = pid)

max_rt <- tmp %>% 
  filter(Event == 'Final decision') %>%
  mutate(zTime = scale(Time)) %>%
  filter(zTime > 3) %>%
  filter(zTime == min(zTime)) %>% 
  pull(Time) %>% 
  .[1]
# round to 10s
max_rt <- ceiling(max_rt / 10000) * 10000
  

# Replace out-of-scale values with a count of dropped values
dropped <- tmp %>%
  group_by(Participant) %>%
  filter(Time > max_rt) %>%
  transmute(n = n())

tmp <- tmp %>% 
  filter(Time <= max_rt) %>% 
  mutate(
    Participant = fct_reorder(Participant, Time, .desc = T),
    Event = factor(Event)
  ) %>%
  order_factors()

ggplot(tmp, aes(y = Participant, x = Time, fill = Event, colour = Event)) +
  geom_density_ridges(alpha = .25, colour = NA) +
  geom_point(alpha = .25, size = .25) +
  geom_text(aes(label = paste0('+', dropped$n), y = Participant),
            inherit.aes = F, x = max_rt, colour = 'grey', hjust = 1, 
            data = dropped) +
  scale_x_continuous(limits = c(0, max_rt), expand = c(0, 0)) +
  labs(x = 'Time since trial start') +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = 'top',
    plot.margin = 
  ) +
  coord_fixed(max_rt/length(unique(tmp$Participant)))

```

All participants had similar patterns: initial and final responses were approximately normally distributed, with final responses having a higher variance due to incorporating the initial responses within them.
Most participants show some trials on which initial or final responses took substantially longer than usual.

###### Accuracy

Accuracy of initial decisions was controlled by a staircasing procedure which aimed to pin accuracy to 71%.
The accuracy of final decisions was free to vary according to the ability of the participant to take advantage of the advice on offer.
As Figure \@ref(fig:ac-agr-dots-r-accuracy) shows, participants' accuracy scores for initial decisions were close to the target values.
Participants did not tend to improve the accuracy of their responses following advice from High agreement advisors, while the evidence was unclear as to whether there was any difference in response accuracy with Low agreement advice.
The distribution of initial estimate accuracy for trials with the High agreement advisor is slightly unusual, with an almost-bimodal structure and a median somewhat higher than the target value. 
There is no obvious reason why this should be the case.

```{r ac-agr-dots-r-accuracy, fig.caption="Response accuracy for the Dots task with in/accurate advisors.  Faint lines show individual participant means, for which the violin and box plots show the distributions. The half-width horizontal dashed lines show the level of accuracy which the staircasing procedure targeted, while the full width dashed line indicates chance performance. Dotted violin outlines show the distribution of actual advisor accuracy."}

dw <- .2

tmp <- familiarization %>% 
  group_by(Advisor, pid) %>%
  summarise(
    `Initial estimate` = mean(initialAnswerCorrect),
    `Final decision` = mean(finalAnswerCorrect),
    .groups = 'drop'
  ) %>%
  pivot_longer(cols = c(`Initial estimate`, `Final decision`), 
               names_to = 'Response', values_to = 'Accuracy') %>%
  mutate(Advisor = factor(paste0(Advisor, '\n')),
         Response = factor(Response))

adv <- familiarization %>%
  group_by(Advisor, pid) %>%
  summarise(
    Response = 'Advice',
    Accuracy = mean(adviceCorrect),
    .groups = 'drop'
  ) %>%
  mutate(Advisor = factor(paste0(Advisor, '\n'))) %>%
  order_factors()

stair <- tribble(
  ~Response, ~Accuracy,
  'Initial estimate', .71
) %>%
  crossing(tibble(Advisor = unique(tmp$Advisor))) %>%
  filter(!is.na(Advisor))

# Should this be a paired t-test?
bf <- tmp %>% 
  nest(d = -Advisor) %>%
  mutate(d = map(d, as.data.frame),
    bf = map(d, ~ ttestBF(x = .$Accuracy[.$Response == 'Initial estimate'],
                          y = .$Accuracy[.$Response == 'Final decision'], 
                          data = ., paired = T)),
         bf = map_chr(bf, ~ .@bayesFactor %>% .$bf %>% exp() %>% bf2str())) %>%
  select(-d)

tmp %>%
  mutate(advisor = str_replace(Advisor, '\\n', ''),
         advisor = factor(advisor)) %>%
  order_factors() %>%
  ggplot(aes(x = Response, y = Accuracy, colour = advisor)) +
  scale_y_continuous(limits = c(NA, 1), expand = c(0, 0)) +
  scale_x_discrete() +
  scale_colour_discrete(name = 'Advisor', aesthetics = c('fill', 'colour')) +
  coord_cartesian(clip = F) +
  geom_hline(yintercept = .5, linetype = 'dashed') +
  geom_segment(aes(y = Accuracy, yend = Accuracy, x = 0, xend = 1.5), 
               linetype = 'dashed', colour = 'black', data = stair) +
  geom_line(aes(group = pid), alpha = .25) +
  geom_split_violin(aes(x = nudge(Response, dw), 
                        group = Response, fill = advisor), 
                    width = .9, colour = NA) +
  geom_split_violin(aes(x = 2 + dw), 
                    group = 2, fill = NA, colour = 'black', linetype = 'dotted', 
                    data = adv) +
  geom_boxplot(aes(x = nudge(Response, dw), group = Response),
               outlier.shape = NA, size = 1, width = dw/2, colour = 'black') +
  geom_segment(x = 1 - dw, xend = 2 + dw, y = 1, yend = 1, colour = 'black') +
  geom_label(x = 1.5, y = 1, aes(label = paste0('BF = ', bf)), colour = 'black', 
             data = bf) +
  facet_wrap(~Advisor) +
  broken_axis_bottom

```

###### Confidence

Generally, we expect participants to be more confident on trials on which they are correct compared to trials on which they are incorrect.
Participants were systematically more confident on correct as compared to incorrect trials for both initial estimates and final decisions.

```{r ac-agr-dots-r-confidence, fig.caption="Confidence for the Dots task with in/accurate advisors.  Faint lines show individual participant means, for which the violin and box plots show the distributions."}

dw <- .2

tmp <- familiarization %>% 
  mutate(`Initial answer accuracy` = 
           if_else(initialAnswerCorrect, 'Correct', 'Incorrect')) %>%
  group_by(`Initial answer accuracy`, pid) %>%
  summarise(
    `Initial estimate` = mean(initialConfidenceScore),
    `Final decision` = mean(finalConfidenceScore),
    .groups = 'drop'
  ) %>%
  pivot_longer(cols = c(`Initial estimate`, `Final decision`), 
               names_to = 'Response', values_to = 'Confidence') %>%
  mutate(response = factor(paste0(Response, '\n')),
         Response = factor(Response),
         `Initial answer accuracy` = factor(`Initial answer accuracy`))

bf <- tmp %>% 
  nest(d = -response) %>%
  mutate(d = map(d, as.data.frame),
         bf = map(d, ~ ttestBF(
           x = .$Confidence[.$`Initial answer accuracy` == 'Correct'],
           y = .$Confidence[.$`Initial answer accuracy` == 'Incorrect'], 
           data = ., paired = T)
         ),
         bf = map_chr(bf, ~ .@bayesFactor %>% .$bf %>% exp() %>% bf2str())) %>%
  select(-d)

tmp %>%
  order_factors() %>%
  ggplot(aes(x = `Initial answer accuracy`, y = Confidence, colour = Response)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
  scale_x_discrete() +
  coord_cartesian(clip = F) +
  geom_line(aes(group = pid), alpha = .25) +
  geom_split_violin(aes(x = nudge(`Initial answer accuracy`, dw), 
                        group = `Initial answer accuracy`, 
                        fill = Response), 
                    width = .9, colour = NA) +
  geom_boxplot(aes(x = nudge(`Initial answer accuracy`, dw), 
                   group = `Initial answer accuracy`),
               outlier.shape = NA, size = 1, width = dw/2, colour = 'black') +
  geom_segment(x = 1 - dw, xend = 2 + dw, y = 1, yend = 1, 
               colour = 'black') +
  geom_label(aes(label = paste0('BF = ', bf)), 
             x = 1.5, y = 1, colour = 'black', data = bf) +
  facet_wrap(~response)

```

###### Metacognitive ability

As shown by Figure \@ref(fig:ac-agr-dots-r-roc), almost all participants showed above-chance metacognitive sensitivity for both initial estimates and final decisions.
Participants generally showed higher metacognitive sensitivity for final decisions, although this may be an artefact of a change in metacognitive bias.
Participants' metacognitive sensitivity was not particularly high \mccorrect{!TODO[What are typical values we might expect in the dots task and similar tasks? Is there a useful mapping between meta-d' and Type II ROC to compare with e.g. Roualt's stuff?]}.
There was no evidence of participants' metacognitive sensitivity being correlated with their task performance (Figure \@ref(fig:ac-agr-dots-r-roc-cor)). 
This is expected when task performance is tightly controlled, because under these conditions variation in task performance reflects variation within a participant rather than between participants. 

```{r ac-agr-dots-r-roc, fig.caption="ROC curves for the Dots task with in/accurate advisors.  Faint lines show individual participant data, while points and solid lines show mean data for all participants. Each participant's data are split into initial estimates and final decisions. For correct and incorrect responses seperately, the probability of a confidence rating being above a response threshold is calculated, with the threshold set to every possible confidence value in turn. This produces a point for each participant in each response for each possible confidence value indicating the probability of confidence being at least that high given the answer was correct, and the equivalent probability given the answer was incorrect. These points are used to create the faint lines, and averaged to produce the solid lines. The dashed line shows chance performance where the increasing confidence threshold leads to no increase in discrimination between correct and incorrect answers."}

nQuantiles <- 50 # confidence range

tmp <- familiarization %>% 
  pivot_longer(cols = c(starts_with('initial'), starts_with('final')),
               names_to = c('Response', '.value'),
               names_pattern = '(initial|final)(.*)') %>%
  # calculate p(confidence > q) for in/correct answers at each quantile q
  nest(d = c(-pid, -Response, -AnswerCorrect)) %>%
  mutate(
    d = map(d, ~ p_conf(., seq(0, 1, length.out = nQuantiles)))
  ) %>%
  unnest(cols = d) %>% 
  unnest(cols = d)

tmp <- tmp %>% 
  mutate(
    Response = factor(if_else(Response == 'initial', 
                              'Initial estimate', 'Final decision')),
    Confidence = factor(Confidence),
    Confidence = fct_relabel(Confidence, ~prop2str(as.numeric(.)))
  ) %>%
  pivot_wider(names_from = AnswerCorrect, 
              names_prefix = 'Correct', 
              values_from = pConf) 

auroc <- tmp %>% 
  nest(d = c(-pid, -Response)) %>%
  mutate(
    d = map(d, ~arrange(., CorrectFALSE, rev(CorrectTRUE))),
    d = map(d, ~mutate(., area = CorrectTRUE * 
                         (CorrectFALSE - lag(CorrectFALSE)))),
    area = map_dbl(d, ~ sum(.$area, na.rm = T))
  ) %>%
  select(-d) 

auroc.gg <- auroc %>%
  nest(d = -Response) %>%
  mutate(
    d = map(d, ~ mutate(., mean = mean(area))),
    gg = map(
      d, 
      ~ ggplot(., aes(y = area)) +
        geom_hline(yintercept = .5, linetype = 'dashed') +
        geom_density(fill = 'black') +
        geom_hline(aes(yintercept = mean), data = unique(select(., mean))) +
        geom_label(aes(y = mean, x = nrow(.), 
                       label = paste0('Mean = ', prop2str(mean))), 
                   hjust = 1, data = unique(select(., mean))) +
        scale_y_continuous(limits = c(0, 1), expand = c(0, 0), 
                           breaks = c(0, .5, 1)) +
        scale_x_continuous(limits = c(0, nrow(.)), expand = c(0, 0),
                           position = 'top') +
        labs(x = "", y = "AUC") +
        theme(axis.ticks.x = element_blank(),
              axis.line.x = element_blank(),
              panel.grid.major.x = element_line(),
              plot.margin = unit(rep(0, 4), 'lines'))
    )
  )

tmp.avg <- tmp %>%
  group_by(Confidence, Response) %>%
  summarise(across(where(is.numeric), mean), .groups = 'drop')

tmp.avg %>%
  order_factors() %>%
  ggplot(aes(x = CorrectFALSE, y = CorrectTRUE)) +
  geom_abline(slope = 1, intercept = 0, linetype = 'dashed') +
  geom_line(aes(group = pid), alpha = .2, colour = 'grey', data = tmp) +
  geom_line() +
  geom_point() +
  geom_plot(aes(label = gg), x = 1, y = .025, vp.width = 2/3, data = auroc.gg) +
  scale_x_continuous(limits = c(0, 1), expand = c(0, .01)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, .01)) +
  coord_fixed() +
  facet_wrap(~Response) +
  theme(panel.spacing.x = unit(2, 'lines'),
        plot.margin = unit(c(0, 0, 4, 0), 'lines')) +
  labs(x = 'p( Confidence > threshold | Incorrect )', 
       y = 'p( Confidence > threshold | Correct )')

```

```{r ac-agr-dots-r-roc-cor, fig.caption="AUROC-accuracy correlation for the Dots task with in/accurate advisors.  Points show individual participant data for their area under the receiver operator characteristic (ROC) curve and their accuracy on initial estimates and final decisions. The blue lines and equation text show best-fit regression, and the shaded area gives its standard error. The equations give the regression equation plotted in blue, with bold coefficients being significant at p = .05."}

# Correlations between Type II AUROC and accuracy
acc <- left_join(
  auroc,
  familiarization %>% 
    group_by(pid) %>% 
    summarise(initialAccuracy = mean(initialAnswerCorrect),
              finalAccuracy = mean(finalAnswerCorrect),
              .groups = 'drop') %>%
    pivot_longer(-pid) %>%
    transmute(
      pid,
      Response = factor(
        if_else(name == 'initialAccuracy', 
                'Initial estimate', 'Final decision')
      ),
      accuracy = value
    ),
  by = c('pid', 'Response')
)

r = acc %>% 
  nest(d = -Response) %>%
  mutate(
    d = map(d, ~ lm(area ~ accuracy, data = .)),
    d = map(d, tidy),
    d = map(d, ~ pivot_wider(., names_from = term, values_from = -term)),
    d = map_chr(d, ~paste0('y = ', 
                           if_else(.$`p.value_(Intercept)` < .05, '**', ''), 
                           round(.$`estimate_(Intercept)`, 2),
                           if_else(.$`p.value_(Intercept)` < .05, '**', ''), 
                           ' + ',
                           if_else(.$p.value_accuracy < .05, '**', ''),
                           round(.$estimate_accuracy, 2),
                           if_else(.$p.value_accuracy < .05, '**', ''), 
                           'x'))
  )

acc %>%
  order_factors() %>%
  ggplot(aes(x = accuracy, y = area)) +
  geom_abline(slope = 1, intercept = 0, linetype = 'dashed') +
  geom_smooth(method = 'lm', formula = y ~ x) +
  geom_point(alpha = .2) +
  geom_richtext(x = .51, y = .99, hjust = 0, vjust = 1, fill = NA,
                aes(label = d), 
                data = r) +
  scale_x_continuous(limits = c(.45, 1), expand = c(0,0)) +
  scale_y_continuous(limits = c(.45, 1), expand = c(0,0)) +
  coord_fixed() +
  facet_wrap(~Response) +
  labs(x = 'Accuracy', y = 'Area under ROC curve') +
  broken_axis_bottom +
  theme(panel.spacing.x = unit(2, 'lines'),
        plot.margin = unit(c(0, 0, 4, 0), 'lines'))

```

##### Confidence change

```{r ac-agr-dots-r-confidence-change, fig.caption="Confidence change on the Dots task with in/accurate advisors.  Each point shows the initial and final confidence on a single trial. Final confidence is coded relative to initial confidence so that increasing confidence in the opposite decision (i.e. confidence on trials where the participant changed their mind) is increasingly negative. Points above the dashed y = x line represent increased confidence, while those below it give decreased confidence. Points close to the y = x line indicate relatively little change, while points further away indicate relatively greater change. The shaded grey area shows the zone outside which influence is capped (by moving vertically towards the grey zone boundary) when using the capped influence measure. Agreement and disagreement trials are plotted seperately, with trials coloured according to whether the initial decision was correct."}

# These polygon points define a triangle marking the limits for the capped influence
df.poly <- data.frame(    
  x = c(Inf, 0, 0),
  y = c(Inf, Inf, -Inf)
)

familiarization %>%
  mutate(
    Agree = factor(if_else(advisorAgrees, 'Agree', 'Disagree')),
    `Initial decision correct` = factor(if_else(initialCorrect, 
                                                'Correct', 'Incorrect')),
    `Initial confidence` = abs(initialConfidenceScore),
    `Final confidence` = if_else(initialAnswer == finalAnswer, 
                                 abs(finalConfidenceScore), 
                                 abs(finalConfidenceScore) * -1)
  ) %>%
  order_factors() %>%
  ggplot(aes(x = `Initial confidence`, y = `Final confidence`)) +
  geom_polygon(data = df.poly, aes(x,y), fill = 'grey', alpha = 0.2) +
  geom_point(alpha = 0.1, aes(colour = `Initial decision correct`)) +
  geom_abline(slope = 1, intercept = 0, linetype = 'dashed', size = 1, color = 'black') +
  scale_x_continuous(limits = c(0,1), expand = c(0,.01)) +
  scale_y_continuous(limits = c(-1,1), expand = c(0,.01)) +
  theme(panel.spacing = unit(2, 'lines'), 
        legend.position = 'bottom',
        plot.margin = unit(c(0, 0, 1, 0), 'lines')) +
  coord_fixed() +
  facet_grid(~Agree)

```

As with the High vs Low accuracy experiment (ยง\@ref(ac-dots-r-confidence-change)), there was an evident off-diagonal pattern in the disagreement trials, indicating a tendency for some participants to change their minds while preserving their confidence. 

As before, inspection of individual participant plots for disagreement trials where participants changed their minds (Figure \@ref(fig:ac-agr-dots-r-confidence-change-p)), this pattern is more likely due to aggregation than a behaviour of any particular individual. 
There were, however, more participants who showed off-diagonal-like patterns than with the Accuracy experiment.

```{r ac-agr-dots-r-confidence-change-p, fig.caption="Change-of-mind confidence updating on the Dots task.  Each facet shows data from a single participant for trials where they changed their mind on the categorical decision between the initial estimate and the final decision. Participants who never changed their mind are not included. Each point shows the initial and final confidence on a single trial. All final confidence scores are negative because they are coded relative to initial confidence; increasing confidence in the final decision is increasingly negative.  Lines show the best fit for a linear prediction of final from initial confidence, with solid lines indicating that the slope is significantly different from zero at alpha = .05. Points are coloured according to the value of the slope parameter. The grey line is the y = x - 1 line that shows the expected fit line according to the intuitive model of confidence updating.", fig.width = 7, fig.height = 7}

# Take trials where decision switches
crossers <- familiarization %>% 
  filter(initialAnswer != finalAnswer) %>%
  mutate(initialConfidenceScore = abs(initialConfidenceScore),
         finalConfidenceScore = -abs(finalConfidenceScore)) %>%
  # How good a predictor is initial confidence of final confidence by participant?
  nest(d = -pid) %>%
  filter(map_int(d, nrow) > 2) %>%
  mutate(
    m = map(d, ~ lm(finalConfidenceScore ~ initialConfidenceScore, data = .)),
    m = map(m, broom::tidy),
    m = map(m, ~ pivot_wider(., names_from = term, values_from = -term) %>%
              transmute(intercept = `estimate_(Intercept)`, 
                        slope = estimate_initialConfidenceScore, 
                        `p<.05` = p.value_initialConfidenceScore < .05))
  ) %>%
  unnest(cols = m) %>%
  arrange(desc(slope)) %>%
  mutate(p = paste0('p', pid),
         p = factor(p),
         p = fct_reorder(p, desc(slope)),
         `p<.05` = if_else(`p<.05`, 'p < .05', 'p >= .05'),
         Beta = cut(slope, 
                      breaks = c(-Inf, -1/3, 0, 1/3, Inf),
                      labels = c('< -1/3', '-1/3:0', '0:1/3', '> 1/3')))

crossers %>%
  unnest(cols = d) %>%
  ggplot(aes(initialConfidenceScore, finalConfidenceScore, colour = Beta)) +
  geom_abline(slope = 1, intercept = -1, colour = 'grey', size = 1) +
  geom_abline(aes(slope = slope, intercept = intercept, linetype = `p<.05`), 
              data = crossers) +
  geom_point(alpha = 1/3) +
  facet_wrap(~p) +
  coord_fixed() +
  scale_y_continuous(breaks = c(0, -.5, -1), expand = c(0,.05)) +
  scale_x_continuous(breaks = c(0, .5, 1), expand = c(0,.05)) +
  scale_linetype_manual(name = '', values = c('solid', 'dashed')) +
  theme(panel.spacing = unit(1, 'lines'), 
        legend.position = 'bottom',
        plot.margin = unit(c(0, 0, 1, 0), 'lines')) +
  labs(x = 'Initial confidence', y = 'Final confidence')

```

##### Experience with advisors

The advice is generated probabilistically from the rules described previously in Table \@ref(tab:ac-agr-dots-m-profiles).
It is thus important to get a sense of the actual advice experienced by the participants.

###### Advisor accuracy

As shown in Figure \@ref(fig:ac-agr-dots-r-advice-acc), the advisors were similarly accurate on average as expected. 
Nevertheless, some participants experienced in practice 10-20% differences in advisor accuracy (although neither advisor was systematically more accurate across participants). 

```{r ac-agr-dots-r-advice-acc, fig.caption="Advisor accuracy for Dots task with in/accurate advisors.  Coloured lines show the average accuracy of the advisors as experienced by an individual participant. Box plots and violins show the distribution of the participant means."}

dw <- .2

tmp <- familiarization %>% 
  filter(!is.na(Advisor)) %>%
  group_by(pid, Advisor) %>%
  summarise(Accuracy = mean(adviceCorrect), .groups = 'drop')

# Note: agr.table defined in the Advice profile section
tmp.adv <- agr.table %>% 
  mutate(
    Accuracy = as.numeric(`Overall accuracy`),
    Advisor = 
    factor(Advisor, levels = levels(tmp$Advisor))
  )


tmp %>%
  order_factors() %>%
  ggplot(aes(x = Advisor, y = Accuracy)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
  scale_x_discrete() +
  geom_line(aes(group = pid), alpha = .2) +
  geom_split_violin(aes(x = nudge(Advisor, dw), group = Advisor), 
                    width = .9, colour = NA, fill = 'grey') +
  geom_boxplot(aes(x = nudge(Advisor, dw), group = Advisor),
               outlier.shape = NA, size = 1, width = dw/2, colour = 'black')

```

###### Advisor agreement

Figure \@ref(fig:ac-agr-dots-r-advice-agr) shows the agreement rates experienced by each participant. 
All participants experienced a higher agreement rate from the High agreement advisor than from the Low agreement advisor.

\mccorrect{Should this break down agreement by initial in/correct as per the experiment design?}

```{r ac-agr-dots-r-advice-agr, fig.caption="Advisor agreement for Dots task with in/accurate advisors.  Faint lines show the average agreement rate of the advisors as experienced by an individual participant. The colour of the line indicates whether the higher agreement advisor agreed with the participant more often as per the experiment design. Box plots and violins show the distribution of the participant means, while the dashed lines indicate the agreement level for the advisors specified in their design."}

dw <- .2

tmp <- familiarization %>% 
  filter(!is.na(Advisor)) %>%
  group_by(pid, Advisor) %>%
  summarise(`Agreement rate` = mean(advisorAgrees), .groups = 'drop') %>%
  # Calculate anomalous experiences
  pivot_wider(names_from = Advisor, values_from = `Agreement rate`) %>%
  mutate(`Participant experience` = if_else(`Low agreement` > `High agreement`,
                                            'Anomalous', 'As planned'),
         `Participant experience` = factor(
           `Participant experience`, 
           levels = c('As planned', 'Anomalous')
         )) %>%
  pivot_longer(cols = c(`High agreement`, `Low agreement`), 
               names_to = 'Advisor', values_to = 'Agreement rate') %>%
  mutate(Advisor = factor(Advisor)) %>%
  order_factors() 

# Note: agr.table defined in the Advice profile section
tmp.adv <- agr.table %>% 
  mutate(
    `Agreement rate` = as.numeric(`Overall`),
    Advisor = 
    factor(Advisor, levels = levels(tmp$Advisor))
  )

tmp %>%
  ggplot(aes(x = Advisor, y = `Agreement rate`, colour = `Participant experience`)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
  scale_x_discrete() +
  scale_colour_discrete(drop = F) +
  scale_alpha_manual(values = c(.5, .25), drop = F) +
  geom_line(aes(group = pid, alpha = `Participant experience`)) +
  geom_split_violin(aes(x = nudge(Advisor, dw), group = Advisor), 
                    width = .9, colour = NA, fill = 'grey') +
  geom_segment(aes(x = nudge(Advisor, .25 * dw), xend = nudge(Advisor, 1.75 * dw),
                   y = `Agreement rate`, yend = `Agreement rate`),
               linetype = 'dashed', colour = 'black', data = tmp.adv) +
  geom_boxplot(aes(x = nudge(Advisor, dw), group = Advisor),
               outlier.shape = NA, size = 1, width = dw/2, colour = 'black')

```

##### Advisor influence

There were no systematic differences in the influence of the two advisors during the Familiarization phase (Figure \@ref(fig:ac-agr-dots-r-influence-graph)).
Some participants were substantially more influenced by one or other advisor, but these extreme cases were also relatively evenly distributed between the advisors.

```{r ac-agr-dots-r-influence-graph, fig.caption="Dot task advisor influence for high/low agreement advisors.  Participants' weight on the advice for advisors in the Familiarization phase of the experiment. The shaded area and boxplots indicate the distribution of the individual participants' mean influence of advice. Individual means for each participant are shown with lines in the centre of the graph. The theoretical range for influence values is [-2, 2].", fig.width = 4, fig.height = 6}

tmp <- familiarization %>% 
  group_by(pid, adviceType) %>%
  select(c(matches('(adviceInfluence)'), group_vars(.))) %>%
  summarise_all(mean) %>%
  mutate(adviceTypeName = case_when(adviceType == 7 ~ 'High agreement',
                                    adviceType == 8 ~ 'Low agreement',
                                    T ~ NA_character_),
         `Feedback condition` = 'No feedback') %>%
  mutate(across(-matches('Influence'), factor),
         adviceTypeName = fct_rev(adviceTypeName))

bf <- tmp %>% 
  select(group_vars(.), adviceTypeName, adviceInfluence) %>%
  pivot_wider(names_from = adviceTypeName, values_from = adviceInfluence) %$%
  ttestBF(`High agreement`, `Low agreement`, paired = T) %>%
  .@bayesFactor %>%
  .$bf %>%
  exp() %>%
  bf2str()

dw <- .1

ggplot(tmp, aes(x = adviceTypeName, y = adviceInfluence, 
                colour = `Feedback condition`, fill = `Feedback condition`)) +
  geom_hline(yintercept = 0, colour = 'lightgrey', size = 1) +
  geom_line(aes(group = pid), alpha = .25) +
  geom_split_violin(aes(x = nudge(adviceTypeName, dw),
                        group = adviceTypeName), width = .9,
               colour = NA) +
  geom_boxplot(outlier.shape = NA, size = 1, width = dw/2,
               aes(x = nudge(adviceTypeName, dw), 
                   group = adviceTypeName),
               colour = 'black') +
  geom_segment(x = 1, xend = 2, y = 1.05, yend = 1.05, colour = 'black') +
  geom_label(y = 1.05, x = 1.5, colour = 'black', fill = 'white', 
             aes(label = paste0('BF = ', bf))) +
  scale_y_continuous(limits = c(-.50, 1.10), breaks = seq(-.50, 1.00, length.out = 6)) +
  facet_grid(~`Feedback condition`) +
  labs(x = 'Advisor advice profile', y = 'Influence of advice') +
  broken_axis

```

##### \OpenScience{prereg} Hypothesis test {##ac-agr-r-h}

```{r ac-agr-dots-r-graph, fig.caption="Dot task advisor choice for high/low agreement advisors.  Participants' pick rate for the advisors in the Choice phase of the experiment. The violin area shows a density plot of the individual participants' pick rates, shown by dots. The chance pick rate is shown by a dashed line.", fig.height=6, fig.width=5}

tmp <- trials %>% 
  filter(hasChoice) %>%
  group_by(pid) %>%
  summarise(pChooseHigh = sum(adviceType == 7) / sum(adviceType %in% c(7,8)),
            .groups = 'drop') %>%
  mutate(`Feedback condition` = 'No feedback')

bf <- ttestBF(pull(tmp, pChooseHigh), mu = .5)

ggplot(tmp, aes(x = '', y = pChooseHigh)) +
  geom_hline(yintercept = .5, linetype = 'dashed') +
  geom_violindot(size_dots = .4) +
  geom_violinhalf(aes(fill = `Feedback condition`, colour = `Feedback condition`)) +
  annotate(geom = 'label', label = paste0('BF vs chance\n', bf2str(exp(bf@bayesFactor$bf))),
           x = 1, y = 1.05) +
  scale_y_continuous(limits = c(0, 1.1), breaks = seq(0, 1, length.out = 5)) +
  labs(y = 'p(Choose High agreement advisor)', x = '') +
  theme(axis.ticks.x = element_blank(), axis.line.x = element_blank())

.T <- tmp %>%
  pull(pChooseHigh) %>%
  md.ttest(y = .5)

```

The results of the advisor choice (Figure \@ref(fig:ac-agr-dots-r-graph)) were the same as those for the Dots task with High versus Low accuracy advisors (ยง\@ref(ac-acc-r-h)).
The High agreement advisor was preferred at a rate greater than that expected by chance (`r .T`).
The modal preference remained at chance, although, as in the accuracy experiment, almost all participants who manifested a preference preferred the High agreement advisor.

### Dates Task {#ac-agr-dates}

```{r include = F}

rm(list = ls()); source('scripts_and_filters/general_setup.R')

# Load the study data
select_experiment(
  project = 'datequiz',
  function(x) filter(x, study == 'agreementDates', manipulationOK)
)


.dropEnv <- new.env()
tada('datequiz', package = 'esmData', envir = .dropEnv)
.dropEnv$datequiz <- .dropEnv$datequiz %>% 
  filter(study == 'agreementDates', !manipulationOK)

.dropEnv$DROP_V <- paste0(unique(.dropEnv$datequiz$version), collapse = ', ')
.dropEnv$DROP_P <- sum(.dropEnv$datequiz %>% 
                         filter(table == 'AdvisedTrial') %>% 
                         pull(N))

AdvisedTrial <- annotate_responses(AdvisedTrial)

```

#### Open scholarship practices

\indent\indent\OpenScience{prereg} `r unique(datequiz$preregistration)`

\OpenScience{data} \mccorrect{!TODO[OSFify data for these studies]}

\OpenScience{materials} https://github.com/oxacclab/ExploringSocialMetacognition/blob/master/ACBin/acc.html

##### Unanalysed data

Early versions of this experiment (`r paste0(.dropEnv$DROP_V, collapse = ', ')`) included a bug which prevented feedback from being shown during the familiarisation phase even to participants in the Feedback condition.
The `r .dropEnv$DROP_P` participants whose data was collected in these versions is not included in analysis.
These participants could theoretically be included in the No feedback condition regardless of their condition label in the data, but this is not done here.

#### Method {#ac-agr-dates-m}

This study used the binary version of the Dates Task (ยง\@ref(m-p-dates-b)).

##### Advice profiles

The High agreement and Low agreement advisor profiles issued binary advice (endorsing either the 'before' or 'after' column) probabilistically based on which column the participant had selected in their initial estimate and whether that was the correct answer. 

```{r ac-agr-dates-m-profiles-r} 

agr <- matrix(c(.9, .65, .75, .35), 2, 2)

agr.table <- tribble(
  ~`Advisor`, ~`Participant correct`, ~`Participant incorrect`,
  "High agreement", agr[1, 1], agr[2, 1],
  "Low agreement", agr[1, 2], agr[2, 2],
) %>% 
  prop2str()

kable(agr.table, caption = "\\label{tab:ac-agr-dates-m-profiles}Advisor advice profiles for Dates task Agreement experiment") %>%
  kable_styling() %>%
  column_spec(1, bold = T) %>%
  row_spec(0, bold = F) %>%
  collapse_rows(columns = 1, valign = "top") %>%
  add_header_above(c(" ", 
                     "Probability of agreement (%)" = 2))

```

#### Results {#ac-agr-dates-r}

##### Exclusions

```{r}
maxTrialRT <- 60000   # trials take < 1 minute
minTrials <- 11       # at least 11 trials completed
minChangeRate <- .1   # some advice taken on 10%+ of trials
minKeyTrials <- 10    # exactly 10 key trials

AdvisedTrial <- AdvisedTrial %>% filter(timeEnd <= maxTrialRT)

exclusions <- AdvisedTrial %>% 
  nest(d = -pid) %>%
  mutate(
    `Too few trials` = map_lgl(d, ~ nrow(.) < minTrials),
    `Insufficient advice taking` = 
      map_lgl(d, ~ (mutate(
        ., 
        x = responseAnswerSide != responseAnswerSideFinal |
          responseConfidence != responseConfidenceFinal) %>%
          pull(x) %>% mean()) < minChangeRate),
    `Too few choice trials` = map_lgl(d, ~ sum(!is.na(.$advisorChoice)) < minKeyTrials)
  ) %>% 
  select(-d)

do_exclusions(exclusions)


exclusions$`Total excluded` <- exclusions %>% select(-pid) %>% apply(1, any)
n <- ncol(exclusions)
exclusions %>% 
  summarise(across(where(is.logical), sum)) %>%
  mutate(`Total remaining` = length(unique(AdvisedTrial$pid))) %>% 
  pivot_longer(everything(), names_to = "Reason", values_to = "Participants excluded") %>%
  kable(caption = "\\label{tab:ac-agr-dates-exclusions}Participant exclusions for Dates task Agreement experiment") %>%
  row_spec((n - 1):n, bold = T)

```

Individual trials were screened to remove those that took longer than `r maxTrialRT/1000`s to complete. Participants were then excluded for having fewer than `r minTrials` trials remaining, fewer than `r minKeyTrials` trials on which they had a choice of advisor, or for giving the same initial and final response on more than `r (1 - minChangeRate) * 100`% of trials. 
Overall, `r sum(pull(exclusions, "Total excluded"))` participants were excluded, with the details shown in Table \@ref(tab:ac-agr-dates-exclusions).

##### Task performance

```{r}

Familiarization <- AdvisedTrial %>%
  filter(is.na(advisorChoice) | !advisorChoice) %>%
  mutate(Advisor = advisor_description_name(advisor0idDescription),
         Advisor = factor(Advisor)) %>%
  order_factors()

```

Before exploring the interaction between the participants' responses and the advisors' advice, and the participants' advisor selection behaviour, it is useful to verify that participants interacted with the task in a sensible way, and that the task manipulations worked as expected.
In this section, task performance is explored during the Familiarization phase of the experiment where participants received advice from a pre-specified advisor on each trial. 
There were an equal number of these trials for each participant for each advisor.

###### Response times

Participants made two decisions during each trial. 
Neither of these decisions had a maximum response time. 
Each participant's response times for both initial and final decisions can be seen in Figure \@ref(fig:ac-agr-dates-r-response-times).
As with the Accuracy experiment, when the Dates task response times are compared to the Dots task response times (\@ref(fig:ac-agr-dots-r-response-times)), they are not only longer, but they are also much more varied within participants.

```{r ac-agr-dates-r-response-times, fig.caption="Response times for the Dates task with High/Low agreement advisors.  Each point shows a response relative to the start of the trial. Each row indicates a single participant's trials. The ridges show the distribution of the underlying points, with initial estimates and final decisions shown in different colours. The grey numbers on the right show the number of trials whose response times were more than 3 standard deviations away from the mean of all final response times (rounded to the next 10s)."}

tmp <- Familiarization %>% 
  transmute(
    pid = factor(pid),
    `Initial estimate` = responseTimeEstimate,
    `Final decision` = responseTimeEstimateFinal
  ) %>%
  pivot_longer(c(`Initial estimate`, `Final decision`),
               names_to = "Event", 
               values_to = "Time") %>%
  filter(!is.na(Event) & !is.na(Time)) %>%
  rename(Participant = pid)

max_rt <- tmp %>% 
  filter(Event == 'Final decision') %>%
  mutate(zTime = scale(Time)) %>%
  filter(zTime > 3) %>%
  filter(zTime == min(zTime)) %>% 
  pull(Time) %>% 
  .[1]
# round to 10s
max_rt <- ceiling(max_rt / 10000) * 10000
  

# Replace out-of-scale values with a count of dropped values
dropped <- tmp %>%
  group_by(Participant) %>%
  filter(Time > max_rt) %>%
  transmute(n = n())

tmp <- tmp %>%
  filter(Time <= max_rt) %>% 
  mutate(
    Participant = fct_reorder(Participant, Time, .desc = T),
    Event = factor(Event)
  )

tmp %>% 
  order_factors() %>%
  ggplot(aes(y = Participant, x = Time, fill = Event, colour = Event)) +
  geom_density_ridges(alpha = .25, colour = NA) +
  geom_point(alpha = .25, size = .25) +
  geom_text(aes(label = paste0('+', dropped$n), y = Participant),
            inherit.aes = F, x = max_rt, colour = 'grey', hjust = 1, 
            data = dropped) +
  scale_x_continuous(limits = c(0, max_rt), expand = c(0, 0)) +
  labs(x = 'Time since trial start') +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = 'top',
    plot.margin = 
  ) +
  coord_fixed(max_rt/length(unique(tmp$Participant)))

```

###### Accuracy

Unlike in the Dots version of the task, participant accuracy is not controlled.
Participants managed to improve their performance from their initial estimates to their final decisions with both advisors (Figure \@ref(fig:ac-agr-dates-r-accuracy)). 
This is likely because the advisors themselves were more accurate than the participants, so following their advice was generally a good strategy, and the difficulty of the task meant that participants were very willing to be influenced by advice.

```{r ac-agr-dates-r-accuracy, fig.caption="Response accuracy for the Dates task with High/Low agreement advisors.  Faint lines show individual participant means, for which the violin and box plots show the distributions. The dashed line indicates chance performance. Dotted violin outlines show the distribution of actual advisor accuracy.  Because there were relatively few trials, the proportion of correct trials for a participant generally falls on one of a few specific values. This produces the lattice-like effect seen in the graph. Some participants had individual trials excluded for over-long response times, meaning that the denominator in the accuracy calculations is different, and thus producing accuracy values which are slightly offset from others'."}
dw <- .2

tmp <- Familiarization %>% 
  group_by(Advisor, pid) %>%
  summarise(
    `Initial estimate` = mean(responseAnswerSideCorrect),
    `Final decision` = mean(responseAnswerSideCorrectFinal),
    .groups = 'drop'
  ) %>%
  pivot_longer(cols = c(`Initial estimate`, `Final decision`), 
               names_to = 'Response', values_to = 'Accuracy') %>%
  mutate(Advisor = factor(paste0(Advisor, '\n')))

adv <- Familiarization %>%
  group_by(Advisor, pid) %>%
  summarise(
    Response = 'Advice',
    Accuracy = mean(advisor0adviceSideCorrect),
    .groups = 'drop'
  ) %>%
  mutate(Advisor = factor(paste0(Advisor, '\n')))

bf <- tmp %>% 
  nest(d = -Advisor) %>%
  mutate(d = map(d, as.data.frame),
    bf = map(d, ~ ttestBF(x = .$Accuracy[.$Response == 'Initial estimate'],
                          y = .$Accuracy[.$Response == 'Final decision'], 
                          data = ., paired = T)),
         bf = map_chr(bf, ~ .@bayesFactor %>% .$bf %>% exp() %>% bf2str())) %>%
  select(-d)

tmp %>%
  mutate(Response = factor(Response)) %>%
  order_factors() %>%
  ggplot(aes(x = Response, y = Accuracy, colour = Advisor)) +
  scale_y_continuous(limits = c(NA, 1), expand = c(0, 0)) +
  scale_x_discrete() +
  coord_cartesian(clip = F) +
  geom_hline(yintercept = .5, linetype = 'dashed') +
  geom_line(aes(group = pid), alpha = .25) +
  geom_split_violin(aes(x = nudge(Response, dw), 
                        group = Response, fill = Advisor), 
                    width = .9, colour = NA) +
  geom_split_violin(aes(x = 2 + dw), 
                    group = 2, fill = NA, colour = 'black', linetype = 'dotted', 
                    data = adv) +
  geom_boxplot(aes(x = nudge(Response, dw), group = Response),
               outlier.shape = NA, size = 1, width = dw/2, colour = 'black') +
  geom_segment(x = 1 - dw, xend = 2 + dw, y = 1.01, yend = 1.01, 
               colour = 'black') +
  geom_label(aes(label = paste0('BF = ', bf)), 
             x = 1.5, y = 1.01, colour = 'black', data = bf) +
  facet_wrap(~Advisor) +
  broken_axis_bottom

```

###### Confidence

Generally, we expect participants to be more confident on trials on which they are correct compared to trials on which they are incorrect.
Participants were systematically more confident on correct as compared to incorrect trials for both initial estimates and final decisions.

```{r ac-agr-dates-r-confidence, fig.caption="Confidence for the Dates task with High/Low agreement advisors.  Faint lines show individual participant means, for which the violin and box plots show the distributions."}

dw <- .2

tmp <- Familiarization %>% 
  mutate(`Initial answer accuracy` = 
           if_else(responseAnswerSideCorrect, 'Correct', 'Incorrect')) %>%
  group_by(`Initial answer accuracy`, pid) %>%
  summarise(
    `Initial estimate` = mean(responseConfidenceScore),
    `Final decision` = mean(responseConfidenceScoreFinal),
    .groups = 'drop'
  ) %>%
  pivot_longer(cols = c(`Initial estimate`, `Final decision`), 
               names_to = 'Response', values_to = 'Confidence') %>%
  mutate(response = factor(paste0(Response, '\n')),
         Response = factor(Response))

bf <- tmp %>% 
  nest(d = -response) %>%
  mutate(d = map(d, as.data.frame),
         bf = map(d, ~ ttestBF(
           x = .$Confidence[.$`Initial answer accuracy` == 'Correct'],
           y = .$Confidence[.$`Initial answer accuracy` == 'Incorrect'], 
           data = ., paired = T)
         ),
         bf = map_chr(bf, ~ .@bayesFactor %>% .$bf %>% exp() %>% bf2str())) %>%
  select(-d)

tmp %>%
  mutate(`Initial answer accuracy` = factor(`Initial answer accuracy`)) %>%
  order_factors() %>%
  ggplot(aes(x = `Initial answer accuracy`, y = Confidence, colour = Response)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
  scale_x_discrete() +
  coord_cartesian(clip = F) +
  geom_line(aes(group = pid), alpha = .25) +
  geom_split_violin(aes(x = nudge(`Initial answer accuracy`, dw), 
                        group = `Initial answer accuracy`, 
                        fill = Response), 
                    width = .9, colour = NA) +
  geom_boxplot(aes(x = nudge(`Initial answer accuracy`, dw), 
                   group = `Initial answer accuracy`),
               outlier.shape = NA, size = 1, width = dw/2, colour = 'black') +
  geom_segment(x = 1 - dw, xend = 2 + dw, y = 1.01, yend = 1.01, 
               colour = 'black') +
  geom_label(aes(label = paste0('BF = ', bf)), 
             x = 1.5, y = 1.01, colour = 'black', data = bf) +
  facet_wrap(~response)

```

###### Metacognitive ability

The participants' metacognitive abilities were highly variable, with several participants displaying below-chance metacognitive ability (Figure \@ref(fig:ac-agr-dates-r-roc)).
While this may appear concerning, recall that metacognitive sensitivity and bias vary substantially and cannot be reliably estimated using ROC curves where performance accuracy on the underlying task is highly variable, so it is not necessarily the case that these values give cause for alarm.
The correlation between performance on the underlying task and metacognitive ability (Figure \@ref(fig:ac-agr-dates-r-roc-cor)) shows that, as one might expect, participants with a greater ability to perform the Dates task have a greater insight into their performance on the Dates task.
This in turn suggests that, despite the low number of trials on the task, we are able to obtain meaningful insights into participants' metacognitive abilities, albeit without being able to precisely estimate the metacognitive sensitivity or bias for an individual participant.

```{r ac-agr-dates-r-roc, fig.caption="ROC curves for the Dates task with High/Low agreement advisors.  Faint lines show individual participant data, while points and solid lines show mean data for all participants. Each participant's data are split into initial estimates and final decisions. For correct and incorrect responses seperately, the probability of a confidence rating being above a response threshold is calculated, with the threshold set to every possible confidence value in turn. This produces a point for each participant in each response for each possible confidence value indicating the probability of confidence being at least that high given the answer was correct, and the equivalent probability given the answer was incorrect. These points are used to create the faint lines, and averaged to produce the solid lines. The dashed line shows chance performance where the increasing confidence threshold leads to no increase in discrimination between correct and incorrect answers."}

nQuantiles <- 100 # confidence range

tmp <- Familiarization %>% 
  transmute(
    pid, 
    Advisor,
    initialAnswerCorrect = responseAnswerSideCorrect,
    finalAnswerCorrect = responseAnswerSideCorrectFinal,
    initialConfidenceScore = responseConfidenceScore,
    finalConfidenceScore = responseConfidenceScoreFinal
  ) %>%
  pivot_longer(cols = c(starts_with('initial'), starts_with('final')),
               names_to = c('Response', '.value'),
               names_pattern = '(initial|final)(.*)') %>%
  # calculate p(confidence > q) for in/correct answers at each quantile q
  nest(d = c(-pid, -Response, -AnswerCorrect)) %>%
  mutate(
    d = map(d, ~ p_conf(., seq(0, 1, length.out = nQuantiles)))
  ) %>%
  unnest(cols = d) %>% 
  unnest(cols = d)

tmp <- tmp %>% 
  mutate(
    Response = if_else(Response == 'initial', 
                       'Initial estimate', 'Final decision'),
    response = factor(paste0(Response, '\n')),
    response = factor(response),
    Confidence = factor(Confidence),
    Confidence = fct_relabel(Confidence, ~prop2str(as.numeric(unique(.))))
  ) %>%
  pivot_wider(names_from = AnswerCorrect, 
              names_prefix = 'Correct', 
              values_from = pConf) 

auroc <- tmp %>% 
  nest(d = c(-pid, -response)) %>%
  mutate(
    d = map(d, ~arrange(., CorrectFALSE, rev(CorrectTRUE))),
    d = map(d, ~mutate(., area = CorrectTRUE * 
                         (CorrectFALSE - lag(CorrectFALSE)))),
    area = map_dbl(d, ~ sum(.$area, na.rm = T))
  ) %>%
  select(-d) 

auroc.gg <- auroc %>%
  nest(d = -response) %>%
  mutate(
    d = map(d, ~ mutate(., mean = mean(area))),
    gg = map(
      d, 
      ~ ggplot(., aes(y = area)) +
        geom_hline(yintercept = .5, linetype = 'dashed') +
        geom_density(fill = 'black') +
        geom_hline(aes(yintercept = mean), data = unique(select(., mean))) +
        geom_label(aes(y = mean, x = nrow(.), 
                       label = paste0('Mean = ', prop2str(mean))), 
                   hjust = 1, data = unique(select(., mean))) +
        scale_y_continuous(limits = c(0, 1), expand = c(0, 0), 
                           breaks = c(0, .5, 1)) +
        scale_x_continuous(limits = c(0, nrow(.)), expand = c(0, 0),
                           position = 'top') +
        labs(x = "", y = "AUC") +
        theme(axis.ticks.x = element_blank(),
              axis.line.x = element_blank(),
              panel.grid.major.x = element_line(),
              plot.margin = unit(rep(0, 4), 'lines'))
    )
  )

tmp.avg <- tmp %>%
  group_by(Confidence, response) %>%
  summarise(across(where(is.numeric), mean), .groups = 'drop')

tmp.avg %>%
  order_factors() %>%
  ggplot(aes(x = CorrectFALSE, y = CorrectTRUE)) +
  geom_abline(slope = 1, intercept = 0, linetype = 'dashed') +
  geom_line(aes(group = pid), alpha = .2, colour = 'grey', data = tmp) +
  geom_line() +
  geom_point() +
  geom_plot(aes(label = gg), x = 1, y = .025, vp.width = 2/3, data = auroc.gg) +
  scale_x_continuous(limits = c(0, 1), expand = c(0, .01)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, .01)) +
  coord_fixed() +
  facet_wrap(~response) +
  theme(panel.spacing.x = unit(2, 'lines'),
        plot.margin = unit(c(0, 0, 4, 0), 'lines')) +
  labs(x = 'p( Confidence > threshold | Incorrect )', 
       y = 'p( Confidence > threshold | Correct )')

```

```{r ac-agr-dates-r-roc-cor, fig.caption="AUROC-accuracy correlation for the Dots task with High/Low agreement advisors.  Points show individual participant data for their area under the receiver operator characteristic (ROC) curve and their accuracy on initial estimates and final decisions. The blue lines and equation text show best-fit regression, and the shaded area gives its standard error. The equations give the regression equation plotted in blue, with bold coefficients being significant at p = .05."}

# Correlations between Type II AUROC and accuracy
acc <- left_join(
  auroc,
  Familiarization %>% 
    group_by(pid) %>% 
    summarise(initialAccuracy = mean(responseAnswerSideCorrect),
              finalAccuracy = mean(responseAnswerSideCorrectFinal),
              .groups = 'drop') %>%
    pivot_longer(-pid) %>%
    transmute(
      pid,
      response = factor(
        if_else(name == 'initialAccuracy', 
                'Initial estimate\n', 'Final decision\n')
      ),
      accuracy = value
    ),
  by = c('pid', 'response')
)

r = acc %>% 
  nest(d = -response) %>%
  mutate(
    d = map(d, ~ lm(area ~ accuracy, data = .)),
    d = map(d, tidy),
    d = map(d, ~ pivot_wider(., names_from = term, values_from = -term)),
    d = map_chr(d, ~paste0('y = ', 
                           if_else(.$`p.value_(Intercept)` < .05, '**', ''), 
                           round(.$`estimate_(Intercept)`, 2),
                           if_else(.$`p.value_(Intercept)` < .05, '**', ''), 
                           ' + ',
                           if_else(.$p.value_accuracy < .05, '**', ''),
                           round(.$estimate_accuracy, 2),
                           if_else(.$p.value_accuracy < .05, '**', ''), 
                           'x'))
  )

acc %>% 
  order_factors() %>%
  ggplot(aes(x = accuracy, y = area)) +
  geom_abline(slope = 1, intercept = 0, linetype = 'dashed') +
  geom_smooth(method = 'lm', formula = y ~ x) +
  geom_point(alpha = .2) +
  geom_richtext(x = .01, y = .99, hjust = 0, vjust = 1, fill = NA,
                aes(label = d), 
                data = r) +
  scale_x_continuous(limits = c(.0, 1), expand = c(0,0)) +
  scale_y_continuous(limits = c(.0, 1), expand = c(0,0)) +
  coord_fixed() +
  facet_wrap(~response) +
  labs(x = 'Accuracy', y = 'Area under ROC curve') +
  theme(panel.spacing.x = unit(2, 'lines'),
        plot.margin = unit(c(0, 0, 4, 0), 'lines'))

```

##### Experience with advisors

The advice is generated probabilistically from the rules described previously in Table \@ref(tab:ac-agr-dots-m-profiles).
It is thus important to get a sense of the actual advice experienced by the participants.

###### Advisor accuracy

As shown in Figure \@ref(fig:ac-agr-dates-r-advice-acc), the advisors were similarly accurate on average as expected. 
Nevertheless, there was a broad range of experiences between participants, both in the absolute accuracy of advisors and in their relative accuracies.
This variation is due to the relatively low number of trials on which advice was received from each advisor.

```{r ac-agr-dates-r-advice-acc, fig.caption="Advisor accuracy for Dots task with High/Low agreement advisors.  Coloured lines show the average accuracy of the advisors as experienced by an individual participant. Box plots and violins show the distribution of the participant means."}

dw <- .2

tmp <- Familiarization %>% 
  filter(!is.na(Advisor)) %>%
  group_by(pid, Advisor) %>%
  summarise(Accuracy = mean(advisor0adviceSideCorrect), .groups = 'drop')

tmp %>%
  ggplot(aes(x = Advisor, y = Accuracy)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
  scale_x_discrete() +
  geom_line(aes(group = pid), alpha = .2) +
  geom_split_violin(aes(x = nudge(Advisor, dw), group = Advisor), 
                    width = .9, colour = NA, fill = 'grey') +
  geom_boxplot(aes(x = nudge(Advisor, dw), group = Advisor),
               outlier.shape = NA, size = 1, width = dw/2, colour = 'black')

```

###### Advisor agreement

Figure \@ref(fig:ac-agr-dots-r-advice-agr) shows the agreement rates experienced by each participant. 
Most participants experienced a higher agreement rate from the High agreement advisor than from the Low agreement advisor, as per the manipulation in the experimental design.

\mccorrect{Should this break down agreement by initial in/correct as per the experiment design?}

```{r ac-agr-dates-r-advice-agr, fig.caption="Advisor agreement for Dots task with High/Low agreement advisors.  Faint lines show the average agreement rate of the advisors as experienced by an individual participant. The colour of the line indicates whether the higher agreement advisor agreed with the participant more often as per the experiment design. Box plots and violins show the distribution of the participant means."}

dw <- .2

tmp <- Familiarization %>% 
  filter(!is.na(Advisor)) %>%
  group_by(pid, Advisor) %>%
  summarise(`Agreement rate` = mean(advisor0adviceSide == responseAnswerSide), 
            .groups = 'drop') %>%
  # Calculate anomalous experiences
  pivot_wider(names_from = Advisor, values_from = `Agreement rate`) %>%
  mutate(`Participant experience` = if_else(`Low agreement` > `High agreement`,
                                            'Anomalous', 'As planned'),
         `Participant experience` = factor(
           `Participant experience`, 
           levels = c('As planned', 'Anomalous')
         )) %>%
  pivot_longer(cols = c(`High agreement`, `Low agreement`), 
               names_to = 'Advisor', values_to = 'Agreement rate') %>%
  mutate(Advisor = fct_rev(factor(Advisor)))

tmp %>%
  order_factors() %>%
  ggplot(aes(x = Advisor, y = `Agreement rate`, colour = `Participant experience`)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
  scale_x_discrete() +
  scale_colour_discrete(drop = F) +
  scale_alpha_manual(values = c(.5, .25), drop = F) +
  geom_line(aes(group = pid, alpha = `Participant experience`)) +
  geom_split_violin(aes(x = nudge(Advisor, dw), group = Advisor), 
                    width = .9, colour = NA, fill = 'grey') +
  geom_boxplot(aes(x = nudge(Advisor, dw), group = Advisor),
               outlier.shape = NA, size = 1, width = dw/2, colour = 'black')

```


##### Advisor influence

The Low agreement was systematically more influential for participants in both Feedback and No feedback conditions.
This is presumably due to the fact that disagreeing advice is generally more influential, in part due to the assymetry of the response scale once an initial estimate has been made.
Any influence effects in play during the Advisor choice phase may be more pronounced, since these data pertain to the Familiarization phase only, in which participants were still learning about the usefulness of their advisors.

```{r ac-agr-dates-r-influence-graph, fig.caption="Date task advisor influence for High/Low agreement advisors.  Participants' weight on the advice for advisors in the Familiarization phase of the experiment. The shaded area and boxplots indicate the distribution of the individual participants' mean influence of advice. Individual means for each participant are shown with lines in the centre of the graph. The theoretical range for influence values is [-2, 2]."}

tmp <- Familiarization %>%
  group_by(pid, Advisor, feedback) %>%
  select(c(matches('(influence|WOA)'), group_vars(.))) %>%
  summarise_all(mean)

# Add in feedback condition
tmp <- left_join(
  tmp,
  AdvisedTrial %>% 
    group_by(pid) %>% 
    summarise(feedbackCondition = case_when(any(feedback == 1) ~ 'Feedback', 
                                            T ~ 'No feedback'),
              .groups = 'drop'),
  by = 'pid'
) %>% 
  ungroup() %>%
  mutate_if(is.character, factor) %>%
  mutate(`Feedback condition` = feedbackCondition,
         Advisor = factor(Advisor)) %>%
  order_factors()

bf <- tmp %>% 
  nest(d = -c(feedbackCondition, `Feedback condition`)) %>%
  mutate(
    bf = map(d, ~ select(., pid, Advisor, advisor0Influence) %>%
               pivot_wider(names_from = Advisor, values_from = advisor0Influence) %>%
               filter_if(is.numeric, ~ !is.na(.)) %$%
               ttestBF(x = `High agreement`, y = `Low agreement`, data = ., paired = T))
  ) 

bf$BF <- sapply(1:nrow(bf), function(i) bf2str(exp(bf$bf[[i]]@bayesFactor$bf)))


dw <- .1

ggplot(tmp, aes(x = Advisor, y = advisor0Influence, 
                colour = `Feedback condition`, fill = `Feedback condition`)) +
  geom_hline(yintercept = 0, colour = 'lightgrey', size = 1) +
  geom_line(aes(group = pid), alpha = .25) +
  geom_split_violin(aes(x = nudge(Advisor, dw),
                        group = Advisor), width = 1,
               colour = NA) +
  geom_boxplot(outlier.shape = NA, size = 1, width = dw/2,
               aes(x = nudge(Advisor, dw), 
                   group = Advisor),
               colour = 'black') +
  geom_segment(x = 1, xend = 2, y = 1.55, yend = 1.55, colour = 'black') +
  geom_label(y = 1.55, x = 1.5, colour = 'black', fill = 'white', 
             aes(label = paste0('BF = ', BF)), data = bf) +
  scale_y_continuous(limits = c(-.50, 1.60), breaks = seq(-.50, 1.50, length.out = 6)) +
  scale_fill_hue(direction = -1, aesthetics = c('fill', 'colour')) +
  facet_grid(~`Feedback condition`) +
  labs(x = 'Advisor advice profile', y = 'Influence of advice') +
  broken_axis

```

##### \OpenScience{prereg} Hypothesis test

```{r ac-agr-dates-r-graph, fig.caption="Dates task advisor choice for High/Low agreement advisors.  Participants' pick rate for the advisors in the Choice phase of the experiment. The violin area shows a density plot of the individual participants' pick rates, shown by dots. The chance pick rate is shown by a dashed line. Participants in the Feedback condition received feedback during the Familiarization phase, but not during the Choice phase.", fig.height=6, fig.width=6}

tmp <- AdvisedTrial %>% 
  filter(advisorChoice == T) %>%
  group_by(pid) %>%
  summarise(pChooseHigh = mean(advisor0idDescription == 'highAgreement'),
            .groups = 'drop')

# Add in feedback condition
tmp <- left_join(
  tmp,
  AdvisedTrial %>% 
    group_by(pid) %>% 
    summarise(feedbackCondition = case_when(any(feedback == 1) ~ 'Feedback', 
                                            T ~ 'No feedback'),
              .groups = 'drop'),
  by = 'pid'
) %>% 
  mutate_if(is.character, factor) %>%
  mutate(`Feedback condition` = feedbackCondition) %>%
  order_factors()

bf <- tmp %>% 
  nest(d = -feedbackCondition) %>%
  mutate(bf = map(d, ~ pull(., pChooseHigh) %>% 
                        ttestBF(mu = .5))) 
bf$bf <- sapply(1:nrow(bf), function(i) num2str(exp(pull(bf, bf)[[i]]@bayesFactor$bf)))

bf.comp <- ttestBF(formula = pChooseHigh ~ feedbackCondition, data = tmp) %>%
  .@bayesFactor %>% .$bf %>% exp() %>% num2str()

ggplot(tmp, aes(x = feedbackCondition, y = pChooseHigh)) +
  geom_hline(yintercept = .5, linetype = 'dashed') +
  geom_violindot(size_dots = .4) +
  geom_violinhalf(aes(fill = `Feedback condition`, colour = `Feedback condition`)) +
  geom_label(aes(label = paste0('BF vs chance\n', bf)), y = 1.1, data = bf) +
  annotate(geom = 'segment', x = 1, xend = 2, y = 1.2, yend = 1.2) +
  annotate(geom = 'label', x = 1.5, y = 1.2, label = paste0('BF = ', bf.comp)) +
  scale_y_continuous(limits = c(0, 1.2), breaks = seq(0, 1, length.out = 5)) +
  scale_fill_hue(direction = -1, aesthetics = c('fill', 'colour')) +
  labs(y = 'p(Choose High agreement advisor)', x = '') +
  theme(axis.line.x = element_blank(), axis.ticks.x = element_blank())

.T.fb <- tmp %>%
  filter(feedbackCondition == 'Feedback') %>%
  pull(pChooseHigh) %>%
  md.ttest(y = .5, labels = c('*M*$_{Feedback}$'))

.T.Nfb <- tmp %>%
  filter(feedbackCondition != 'Feedback') %>%
  pull(pChooseHigh) %>%
  md.ttest(y = .5, labels = c('*M*$_{No feedback}$'))

```

Consistent with the result from the Dots task, in the No feedback condition participants' preferences for receiving advice from the High agreement advisor were greater than chance (`r .T.Nfb`).
The modal preference was to select the High agreement advisor on every Choice trial, and although some participants still showed a preference for hearing advice from the Low agreement advisor, preferences for the High agreement advisor were generally stronger and more frequent (Figure \@ref(fig:ac-agr-dates-r-graph)).

In the Feedback condition, the mean of the participants' selection rates was equivalent to random picking (`r .T.fb`).
This is consistent with a strategy which attempts to maximise the accuracy of final decisions, because neither advisor would help with this task systematically. 
The null result here does indicate, however, that there is no strong and clear preference for agreement over and above its accuracy benefits.

### Discussion {#ac-agr-d}

Where feedback is provided on advisors' performance, participants prefer high agreement advisors to low agreement advisors.

\mccorrect{At least in the Dates task the low agreement advice is probably more interesting - we already know what the high agreement advisor is going to say!}

\mccorrect{re: influence - 
An alternative explanation for the data is that the 'offbrand' advice selected for analysis was more surprising when coming from the advisor who usually agrees, and that this increased salience increased its influence rather than increased trust in the advisor.}
If that were the case then the same ought to be true for agreeing advice from a disagreeing advisor, and this is not the case \mccorrect{!TODO[Do we have/can we produce evidence for this? Perhaps look at our participants where advisors disagree with them by chance more than e.g. 70\% of the time and check for increased influence on agreement trials vs advisors who disagree less than 70\% of the time]}.
